---
title: "Generic interpretation"
output: html_notebook
---

```{r}
library(tidyverse)
library(tidyboot)
library(ggpirate)
library(knitr)
library(viridis)
```

```{r}
readData = function(proj){
  read_csv(
    paste("../../data/interpretation/",proj,"/",
          proj,"-trials.csv", sep = "")
    )
}

readCatchInfo = function(proj){
  read_csv(
    paste("../../data/interpretation/",proj,"/",
          proj,"-catch_trials.csv", sep = "")
    )
}

readSubjInfo = function(proj){
  read_csv(
    paste("../../data/interpretation/",proj,"/",
          proj,"-subject_information.csv", sep = "")
    )
}
```


```{r}
df.1 <- read_csv("data/asymmetry/asymmetry-1-trials.csv")

df.1.bs <- df.1 %>%
  filter(trial_type == 'implied_prevalence') %>%
  mutate(response = as.numeric(response)) %>%
  group_by(stim_property) %>%
  tidyboot_mean(column = response)
```


```{r}
df.1.bs %>%
  mutate(stim_property = factor(stim_property, levels =  stim_property[order(mean)])) %>%
  ggplot(aes( x= stim_property, y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_linerange()+
  geom_point()+
  coord_flip()+
  ylim(0, 100)
```


# Interpretation-1

```{r}
df.int.1 <- readData("interpretation-1") %>%
  group_by(workerid) %>%
  mutate(normalizedResponse = (response - mean(response)) / sd(response))
 
df.int.1.subj <- readSubjInfo("interpretation-1")
df.int.1.subj %>%
  select(problems, comments) %>%
  kable()
```

### by item histogram

```{r fig.width = 10, fig.height = 4}
df.int.1 %>%
  ggplot(., aes(x = response ))+
  geom_histogram()+
  facet_wrap(~property)
```
```{r fig.height = 4}
df.int.1.bs <- df.int.1 %>%
  group_by(property) %>%
  tidyboot_mean(column = response)

df.int.1.bs %>%
  mutate(property = factor(property, levels =  property[order(mean)])) %>%
  ggplot(aes( x= property, y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_linerange()+
  geom_point()+
  coord_flip()+
  ylim(0, 1)

#ggsave("figs/interpretation-1-n18-95ci.pdf", height = 4)
```
```{r fig.height = 4}
df.int.1 %>%
  mutate(property = factor(property, 
                           levels =  with(df.int.1.bs, property[order(mean)]))) %>%
  ggplot(., aes( x = property, y = response, color = property))+
  geom_pirate(bars = F, violins = F, width_points = 0.2)+
  coord_flip()+
  scale_color_viridis(discrete = T)+
  ylim(0, 1)

#ggsave("figs/interpretation-1-n18-pirates.pdf", height = 7)
```


### by subject hists

```{r fig.width = 10, fig.height = 4}
df.int.1 %>%
  ggplot(., aes(x = response ))+
  geom_histogram()+
  facet_wrap(~workerid)
```


```{r}
df.int.norm.bs.1 <- df.int.1 %>%
 group_by(property) %>%
  tidyboot_mean(column = normalizedResponse)

df.int.1 %>%
  mutate(property = factor(property, 
                           levels =  with(df.int.norm.bs.1, property[order(mean)]))) %>%
  ggplot(., aes( x = property, y = normalizedResponse, color = property))+
  geom_pirate(bars = F, violins = F, width_points = 0.2)+
  coord_flip()+
  scale_color_viridis(discrete = T)

#ggsave("figs/interpretation-1-normalized-n18-pirates.pdf", height = 7)
```


# Interpretation-2

```{r}
df.int.2.catch <- readCatchInfo("interpretation-2")

df.int.2.catch.summary <- df.int.2.catch %>%
  group_by(workerid, tested_on) %>%
  summarize(totalCorrect = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, totalCorrect) %>%
  rename(correct_rejection = `0`, 
         hit = `1`) %>%
  mutate(pass = ifelse(hit >= 4 & correct_rejection >= 4, 1, 0),
         totalCorrect = correct_rejection + hit)

df.int.2.catch.summary %>%
  select(`0`, `1`) %>%
  table()

df.int.2.catch.summary %>%
  select(pass) %>%
  table()
```

```{r}
df.int.2 <- readData("interpretation-2") %>%
  group_by(workerid) %>%
  mutate(normalizedResponse = (response - mean(response)) / sd(response))

df.int.2 <- left_join(df.int.2, df.int.2.catch.summary %>%
                         select(workerid, totalCorrect, pass))

df.int.2.filtered <- df.int.2 %>% filter(pass == 1)
  
df.int.2.subj <- readSubjInfo("interpretation-2")

df.int.2.subj %>%
  select(problems, comments) %>%
  kable()
```




### by item histogram

by item counts
```{r}
with(df.int.2, table(property))

# filtered data
with(df.int.2.filtered, table(property))
```

```{r fig.width = 10, fig.height = 4}
df.int.2 %>%
  ggplot(., aes(x = response ))+
  geom_histogram()+
  facet_wrap(~property)
```



```{r fig.height = 4}
df.int.2.bs <- df.int.2 %>%
  group_by(property) %>%
  tidyboot_mean(column = response)

df.int.2 %>%
  mutate(property = factor(property, 
                           levels =  with(df.int.2.bs, property[order(mean)]))) %>%
  ggplot(., aes( x = property, y = response, color = property))+
  geom_pirate(bars = F, violins = F, width_points = 0.2)+
  coord_flip()+
  scale_color_viridis(discrete = T)+
  ylim(0, 1)

#ggsave("figs/interpretation-1-n18-pirates.pdf", height = 7)
```


```{r fig.height = 4}
df.int.2.filtered.bs <- df.int.2.filtered %>%
  group_by(property) %>%
  tidyboot_mean(column = response)

df.int.2.filtered %>%
  mutate(property = factor(property, 
                           levels =  with(df.int.2.filtered.bs, property[order(mean)]))) %>%
  ggplot(., aes( x = property, y = response, color = property))+
  geom_pirate(bars = F, violins = F, width_points = 0.2)+
  coord_flip()+
  scale_color_viridis(discrete = T)+
  ylim(0, 1)

ggsave("figs/interpretation-2-n36filterd-pirates.pdf", height = 9)
```



### by subject hists

```{r fig.width = 10, fig.height = 4}
df.int.2 %>%
  ggplot(., aes(x = response, fill= factor(pass )))+
  geom_histogram()+
  facet_wrap(~workerid)#+
  #scale_x_continuous(breaks = c(0, 0.5, 1), limits = c(-0.1, 1.1))+
  #scale_fill_viridis(discrete = T)

#ggsave("figs/interpretation-2-bySubj-hists.pdf", height = 6, width = 11)
```


```{r}
df.int.norm.bs.1 <- df.int.1 %>%
 group_by(property) %>%
  tidyboot_mean(column = normalizedResponse)

df.int.1 %>%
  mutate(property = factor(property, 
                           levels =  with(df.int.norm.bs.1, property[order(mean)]))) %>%
  ggplot(., aes( x = property, y = normalizedResponse, color = property))+
  geom_pirate(bars = F, violins = F, width_points = 0.2)+
  coord_flip()+
  scale_color_viridis(discrete = T)

#ggsave("figs/interpretation-1-normalized-n18-pirates.pdf", height = 7)
```


# Interpretation-3

72 items. follow-up question for responses < 0.25

```{r}
df.int.3.catch <- readCatchInfo("interpretation-3")

df.int.3.catch.summary <- df.int.3.catch %>%
  group_by(workerid, tested_on) %>%
  summarize(totalCorrect = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, totalCorrect) %>%
  rename(correct_rejection = `0`, 
         hit = `1`) %>%
  mutate(pass = ifelse(hit >= 4 & correct_rejection >= 4, 1, 0),
         totalCorrect = correct_rejection + hit)

df.int.3.catch.summary %>%
  select(pass) %>%
  table()
```

```{r}
df.int.3 <- readData("interpretation-3") %>%
  group_by(workerid) %>%
  mutate(normalizedResponse = (response - mean(response)) / sd(response))

df.int.3 <- left_join(df.int.3, df.int.3.catch.summary %>%
                         select(workerid, totalCorrect, pass))

df.int.3.filtered <- df.int.3 %>% filter(pass == 1)
  
df.int.3.subj <- readSubjInfo("interpretation-3")

df.int.3.subj %>%
  select(problems, comments) %>%
  kable()
```

### by item histogram

by item counts
```{r}
with(df.int.3, table(property))

# filtered data
with(df.int.3.filtered, table(property))
```

```{r fig.width = 10, fig.height = 4}
df.int.3 %>%
  ggplot(., aes(x = response ))+
  geom_histogram()+
  facet_wrap(~property)
```



```{r fig.height = 4}
df.int.3.bs <- df.int.3 %>%
  group_by(property) %>%
  tidyboot_mean(column = response)

df.int.3 %>%
  mutate(property = factor(property, 
                           levels =  with(df.int.3.bs, property[order(mean)]))) %>%
  ggplot(., aes( x = property, y = response, color = property))+
  geom_pirate(bars = F, violins = F, width_points = 0.2)+
  coord_flip()+
  scale_color_viridis(discrete = T)+
  ylim(0, 1)

#ggsave("figs/interpretation-3-n18-pirates.pdf", height = 7)
```


```{r fig.height = 4}
df.int.3.filtered.bs <- df.int.3.filtered %>%
  group_by(property) %>%
  tidyboot_mean(column = response)

df.int.3.filtered %>%
  mutate(property = factor(property, 
                           levels =  with(df.int.3.filtered.bs, property[order(mean)]))) %>%
  ggplot(., aes( x = property, y = response, color = property))+
  geom_pirate(bars = F, violins = F, width_points = 0.2)+
  coord_flip()+
  scale_color_viridis(discrete = T)+
  ylim(0, 1)

#ggsave("figs/interpretation-3-n36filterd-pirates.pdf", height = 9)
```



### by subject hists

```{r fig.width = 10, fig.height = 4}
df.int.3 %>%
  ggplot(., aes(x = response, fill= factor(pass )))+
  geom_histogram()+
  facet_wrap(~workerid)#+
  #scale_x_continuous(breaks = c(0, 0.5, 1), limits = c(-0.1, 1.1))+
  #scale_fill_viridis(discrete = T)

#ggsave("figs/interpretation-2-bySubj-hists.pdf", height = 6, width = 11)
```

### explanations of low prevalence interpretations

```{r}
df.int.3.expl <- df.int.3 %>%
  filter(!(explanation == "<NA>")) %>%
  select(property, response, explanation)

df.int.3.expl[order(df.int.3.expl$property),] %>%
  kable()
```




# Interpretation-4

74 items. follow-up question for responses < 0.5

```{r}
df.int.4.catch <- readCatchInfo("interpretation-4")

df.int.4.catch.summary <- df.int.4.catch %>%
  group_by(workerid, tested_on) %>%
  summarize(totalCorrect = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, totalCorrect) %>%
  rename(correct_rejection = `0`, 
         hit = `1`) %>%
  mutate(pass = ifelse(hit >= 4 & correct_rejection >= 4, 1, 0),
         totalCorrect = correct_rejection + hit)

df.int.4.catch.summary %>%
  select(pass) %>%
  table()
```

```{r}
df.int.4 <- readData("interpretation-4") %>%
  group_by(workerid) %>%
  mutate(normalizedResponse = (response - mean(response)) / sd(response))

df.int.4 <- left_join(df.int.4, df.int.4.catch.summary %>%
                         select(workerid, totalCorrect, pass))

df.int.4.filtered <- df.int.4 %>% filter(pass == 1)
  
df.int.4.subj <- readSubjInfo("interpretation-4")

df.int.4.subj %>%
  select(language)

df.int.4.subj %>%
  select(problems, comments) %>%
  kable()
```


### by item histogram

by item counts
```{r}
with(df.int.4, table(property))

# filtered data
data.frame(with(df.int.4.filtered, table(property))) %>%
  ggplot(., aes( x = Freq ))+
  geom_bar()
```

```{r fig.width = 18, fig.height = 8}
df.int.4 %>%
  ggplot(., aes(x = response ))+
  geom_histogram()+
  facet_wrap(~property)

ggsave("figs/interpretation-4-n36-hist.pdf", width = 20, height = 14)
```



```{r fig.height = 4}
df.int.4.bs <- df.int.4 %>%
  group_by(property) %>%
  tidyboot_mean(column = response)

df.int.4 %>%
  mutate(property = factor(property, 
                           levels =  with(df.int.4.bs, property[order(mean)]))) %>%
  ggplot(., aes( x = property, y = response, color = property))+
  geom_pirate(bars = F, violins = F, width_points = 0.2)+
  coord_flip()+
  scale_color_viridis(discrete = T)+
  ylim(0, 1)

ggsave("figs/interpretation-4-n36-pirates.pdf", height = 7)
```


```{r fig.height = 4}
df.int.4.filtered.bs <- df.int.4.filtered %>%
  group_by(property) %>%
  tidyboot_mean(column = response)

df.int.4.filtered %>%
  mutate(property = factor(property, 
                           levels =  with(df.int.4.filtered.bs, property[order(mean)]))) %>%
  ggplot(., aes( x = property, y = response, color = property))+
  geom_pirate(bars = F, violins = F, width_points = 0.2)+
  coord_flip()+
  scale_color_viridis(discrete = T)+
  ylim(0, 1)

#ggsave("figs/interpretation-3-n36filterd-pirates.pdf", height = 9)
```



```{r}
df.int.34.filtered.bs <- left_join(
  df.int.3.filtered.bs %>%
    rename(mean_3 = mean, ci_lower_3 = ci_lower, ci_upper_3 = ci_upper,
           n_3 = n, empirical_stat_3 = empirical_stat),
  df.int.4.filtered.bs %>%
    rename(mean_4 = mean, ci_lower_4 = ci_lower, ci_upper_4 = ci_upper,
           n_4 = n, empirical_stat_4 = empirical_stat)
)

print(with(df.int.34.filtered.bs, cor(mean_3, mean_4, use = "pairwise.complete.obs")))

ggplot(df.int.34.filtered.bs, aes ( x = mean_3, y = mean_4,
                  xmin = ci_lower_3, xmax = ci_upper_3,
                  ymin = ci_lower_4, ymax = ci_upper_4))+
  geom_point()+
  geom_errorbarh(alpha = 0.3)+geom_errorbar(alpha = 0.3)+
  xlim(0, 1)+
  ylim(0, 1)+
  coord_fixed()
  
  
```



### by subject hists

```{r fig.width = 10, fig.height = 4}
df.int.3 %>%
  ggplot(., aes(x = response, fill= factor(pass )))+
  geom_histogram()+
  facet_wrap(~workerid)#+
  #scale_x_continuous(breaks = c(0, 0.5, 1), limits = c(-0.1, 1.1))+
  #scale_fill_viridis(discrete = T)

#ggsave("figs/interpretation-2-bySubj-hists.pdf", height = 6, width = 11)
```

### explanations of low prevalence interpretations

```{r}
df.int.4.expl <- df.int.4 %>%
  filter(!(explanation == "<NA>")) %>%
  select(property, response, explanation) %>%
  mutate(explanation = gsub("&quotechar", "'", explanation))

df.int.4.expl[with(df.int.4.expl, order(property, response)),] %>%
  kable()
```




# Interpretation-5

74 items. follow-up question for responses < 0.5

```{r}
df.int.5.catch <- readCatchInfo("interpretation-5")

df.int.5.catch.summary <- df.int.5.catch %>%
  group_by(workerid, tested_on) %>%
  summarize(totalCorrect = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, totalCorrect) %>%
  rename(correct_rejection = `0`, 
         hit = `1`) %>%
#  mutate(pass = ifelse(hit > 4 & correct_rejection > 4, 1, 0),
  mutate(pass = ifelse(hit >= 4 & correct_rejection >= 4, 1, 0),
         totalCorrect = correct_rejection + hit)

df.int.5.catch.summary %>%
  select(pass) %>%
  table()
```

```{r}
df.int.5.subj <- readSubjInfo("interpretation-5")

df.int.5.subj %>%
  select(language)

df.int.5.subj %>%
  select(problems, comments) %>%
  kable()
```

Native english

```{r}
d.int.5.nativeEnglish <- df.int.5.subj %>% 
  select(workerid ,language) %>% 
  mutate(englishNative = grepl("eng", tolower(language)))

#save(d.full.nativeEnglish, file = "../cached_results/english_summary.RData")

table(d.int.5.nativeEnglish$englishNative)

# what do people report for native english that is not english?
d.int.5.nativeEnglish %>%
  filter(!englishNative) %>%
  select(language) %>%
  kable(.)
```

Load data

```{r}
df.int.5 <- readData("interpretation-5") %>%
  filter(trial_type == "implied_prevalence") %>%
  group_by(workerid) %>%
  mutate(normalizedResponse = (response - mean(response)) / sd(response))

## RTs
df.int.5.rt <- df.int.5 %>%
  group_by(workerid) %>%
  summarize(meanRT = mean(rt/ 1000),
            rt_lt_4 = meanRT < 4)

df.int.5.rt %>%
  ggplot(., aes(x = meanRT))+
  geom_histogram()+
  xlim(0, 10)
###


df.int.5 <- left_join(
  left_join(
  left_join(df.int.5, df.int.5.catch.summary %>%
                         select(workerid, totalCorrect, pass)),
  d.int.5.nativeEnglish),
  
                      df.int.5.rt)

df.int.5.filtered <- df.int.5 %>% 
  filter(pass == 1, englishNative)
```



### by item histogram

by item counts
```{r}
with(df.int.5.filtered, table(property))

# filtered data
data.frame(with(df.int.5.filtered, table(property))) %>%
  ggplot(., aes( x = Freq ))+
  geom_bar()
```

```{r fig.width = 18, fig.height = 8}
df.int.5.filtered %>%
  ggplot(., aes(x = response, fill = property_type))+
  geom_histogram(aes(
    y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]
    ),
    bins = 20, color = 'black')+  #scale_fill_viridis(discrete = T)+
  facet_wrap(~ property_type + property, scales = 'free')+
  scale_x_continuous(limits = c(-0.05, 1.05), breaks = c(0, 0.5, 1))
  

#ggsave("figs/interpretation-5-filtered-n140-hist.pdf", width = 20, height = 14)
```

```{r fig.width = 18, fig.height = 8}
df.int.5 %>%
  mutate(pass_rt = paste(pass, rt_lt_4)) %>%
  ggplot(., aes(x = response, fill = pass_rt))+
  geom_histogram()+
  facet_wrap(~workerid)

ggsave("figs/interpretation-5-subj-n140-hist.pdf", width = 20, height = 18)
```





```{r fig.height = 4}
df.int.5.bs <- df.int.5 %>%
  group_by(property) %>%
  tidyboot_mean(column = response)

df.int.5 %>%
  mutate(property = factor(property, 
                           levels =  with(df.int.5.bs, property[order(mean)]))) %>%
  ggplot(., aes( x = property, y = response, color = property))+
  geom_pirate(bars = F, violins = F, width_points = 0.2, alpha_points = 0.3)+
  coord_flip()+
  scale_color_viridis(discrete = T)+
  ylim(0, 1)

#ggsave("figs/interpretation-5-n140-pirates.pdf", height = 7)
```


```{r fig.height = 4}
df.int.5.filtered.bs <- df.int.5.filtered %>%
  group_by(property) %>%
  tidyboot_mean(column = response)

df.int.5.filtered %>%
  mutate(property = factor(property, 
                           levels =  with(df.int.5.filtered.bs, property[order(mean)]))) %>%
  ggplot(., aes( x = property, y = response, color = property_type))+
  geom_pirate(bars = F, violins = F, width_points = 0.2, alpha_points = 0.35)+
  coord_flip()+
  #scale_color_viridis(discrete = T)+
  ylim(0, 1)

#ggsave("figs/interpretation-5-n140filterd-pirates.pdf", height = 9)
```



```{r}
df.int.45.filtered.bs <- left_join(
  df.int.5.filtered.bs %>%
    rename(mean_5 = mean, ci_lower_5 = ci_lower, ci_upper_5 = ci_upper,
           n_5 = n, empirical_stat_5 = empirical_stat),
  df.int.4.filtered.bs %>%
    rename(mean_4 = mean, ci_lower_4 = ci_lower, ci_upper_4 = ci_upper,
           n_4 = n, empirical_stat_4 = empirical_stat)
)

print(with(df.int.45.filtered.bs, cor(mean_5, mean_4, use = "pairwise.complete.obs")))

ggplot(df.int.45.filtered.bs, aes ( x = mean_4, y = mean_5,
                  xmin = ci_lower_4, xmax = ci_upper_4,
                  ymin = ci_lower_5, ymax = ci_upper_5))+
  geom_point()+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_errorbarh(alpha = 0.3)+geom_errorbar(alpha = 0.3)+
  xlim(0, 1)+
  ylim(0, 1)+
  coord_fixed()
  
  
```



### explanations of low prevalence interpretations

```{r}
df.int.5.expl <- readData("interpretation-5") %>%
  filter(trial_type != "implied_prevalence")%>%
  select(property, original_response, response, explanation) %>%
  mutate(explanation = gsub("&quotechar", "'", explanation))


ggplot(df.int.5.expl, aes(x = original_response, y = response))+
  geom_point()+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  xlim(0, 1)+
  ylim(0, 1)+
  coord_fixed()

df.int.5.expl[with(df.int.5.expl, order(property, response)),] %>%
  kable()
```




# Interpretation-6

% question. 75 items. follow-up question for responses < 0.5

```{r}
df.int.6.catch <- readCatchInfo("interpretation-6")

df.int.6.catch.summary <- df.int.6.catch %>%
  group_by(workerid, tested_on) %>%
  summarize(totalCorrect = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, totalCorrect) %>%
  rename(correct_rejection = `0`, 
         hit = `1`) %>%
  #mutate(pass = ifelse(hit > 4 & correct_rejection > 4, 1, 0),
  mutate(pass = ifelse(hit >= 4 & correct_rejection >= 4, 1, 0),
         totalCorrect = correct_rejection + hit)

df.int.6.catch.summary %>%
  select(pass) %>%
  table()
```

```{r}
df.int.6.subj <- readSubjInfo("interpretation-6")

df.int.6.subj %>%
  select(language)

df.int.6.subj %>%
  select(problems, comments) %>%
  kable()
```

Native english

```{r}
d.int.6.nativeEnglish <- df.int.6.subj %>% 
  select(workerid ,language) %>% 
  mutate(englishNative = grepl("eng", tolower(language)))

#save(d.full.nativeEnglish, file = "../cached_results/english_summary.RData")

table(d.int.6.nativeEnglish$englishNative)

# what do people report for native english that is not english?
d.int.6.nativeEnglish %>%
  filter(!englishNative) %>%
  select(language) %>%
  kable(.)
```

Load data

```{r}
df.int.6 <- readData("interpretation-6") %>%
  filter(trial_type == "implied_prevalence") %>%
  group_by(workerid) %>%
  mutate(normalizedResponse = (response - mean(response)) / sd(response))

## RTs
df.int.6.rt <- df.int.6 %>%
  group_by(workerid) %>%
  summarize(meanRT = mean(rt/ 1000),
            rt_lt_4 = meanRT < 4)

df.int.6.rt %>%
  ggplot(., aes(x = meanRT))+
  geom_histogram()+
  xlim(0, 10)
###


df.int.6 <- left_join(
  left_join(
  left_join(df.int.6, df.int.6.catch.summary %>%
                         select(workerid, totalCorrect, pass)),
  d.int.6.nativeEnglish),
  
                      df.int.6.rt)

df.int.6.filtered <- df.int.6 %>% 
  filter(pass == 1, englishNative) %>%
  mutate(property = gsub("&quotechar", "", property))
```



### by item histogram

by item counts
```{r}
with(df.int.6.filtered, table(property)) %>% mean()

# filtered data
data.frame(with(df.int.6.filtered, table(property))) %>%
  ggplot(., aes( x = Freq ))+
  geom_bar()
```

```{r fig.width = 18, fig.height = 8}
df.int.6.filtered %>%
  ggplot(., aes(x = response, fill = property_type))+
  geom_histogram(aes(
    y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]
    ),
    bins = 20, color = 'black')+  #scale_fill_viridis(discrete = T)+
  facet_wrap(~ property_type + property, scales = 'free')+
  scale_x_continuous(limits = c(-0.05, 1.05), breaks = c(0, 0.5, 1))
  

#ggsave("figs/interpretation-5-filtered-n140-hist.pdf", width = 20, height = 14)
```

```{r fig.width = 18, fig.height = 8}
df.int.6 %>%
  mutate(pass_rt = paste(pass, rt_lt_4)) %>%
  ggplot(., aes(x = response, fill = pass_rt))+
  geom_histogram()+
  facet_wrap(~workerid)

#ggsave("figs/interpretation-6-subj-n140-hist.pdf", width = 20, height = 18)
```



```{r fig.height = 4}
df.int.6.bs <- df.int.6 %>%
  group_by(property) %>%
  tidyboot_mean(column = response)

df.int.6 %>%
  mutate(property = factor(property, 
                           levels =  with(df.int.6.bs, property[order(mean)]))) %>%
  ggplot(., aes( x = property, y = response, color = property))+
  geom_pirate(bars = F, violins = F, width_points = 0.2, alpha_points = 0.3)+
  coord_flip()+
  scale_color_viridis(discrete = T)+
  ylim(0, 1)

#ggsave("figs/interpretation-6-n200-pirates.pdf", height = 7)
```


```{r fig.height = 4}
df.int.6.filtered.bs <- df.int.6.filtered %>%
  group_by(property) %>%
  tidyboot_mean(column = response)

df.int.6.filtered %>%
  mutate(property = factor(property, 
                           levels =  with(df.int.6.filtered.bs, property[order(mean)]))) %>%
  ggplot(., aes( x = property, y = response, color = property))+
  geom_pirate(bars = F, violins = F, width_points = 0.2, alpha_points = 0.35)+
  coord_flip()+
  #scale_color_viridis(discrete = T)+
  ylim(0, 1)

#ggsave("figs/interpretation-6-n200filterd-pirates.pdf", height = 9)
```



```{r}
df.int.56.filtered.bs <- left_join(
  df.int.5.filtered.bs %>%
    rename(mean_5 = mean, ci_lower_5 = ci_lower, ci_upper_5 = ci_upper,
           n_5 = n, empirical_stat_5 = empirical_stat),
  df.int.6.filtered.bs %>%
    rename(mean_6 = mean, ci_lower_6 = ci_lower, ci_upper_6 = ci_upper,
           n_6 = n, empirical_stat_6 = empirical_stat)
)

print(with(df.int.56.filtered.bs, cor(mean_5, mean_6, use = "pairwise.complete.obs")))

print(with(df.int.56.filtered.bs, cor(mean_5, mean_6, use = "pairwise.complete.obs", method = "spearman")))

ggplot(df.int.56.filtered.bs, aes ( x = mean_5, y = mean_6,
                  xmin = ci_lower_5, xmax = ci_upper_5,
                  ymin = ci_lower_6, ymax = ci_upper_6))+
  geom_point()+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_errorbarh(alpha = 0.3)+geom_errorbar(alpha = 0.3)+
  xlim(0, 1)+
  ylim(0, 1)+
  coord_fixed()
```



### explanations of low prevalence interpretations

```{r}
df.int.6.expl <- readData("interpretation-6") %>%
  filter(trial_type != "implied_prevalence")%>%
  select(property, original_response, response, explanation) %>%
  mutate(explanation = gsub("&quotechar", "'", explanation))


ggplot(df.int.6.expl, aes(x = original_response, y = response))+
  geom_point()+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  xlim(0, 1)+
  ylim(0, 1)+
  coord_fixed()

df.int.6.expl[with(df.int.6.expl, order(property, response)),] %>%
  kable()
```


```{r}
df.int.6.expl %>%
  mutate(change = ifelse(
    original_response < response, -1, 
    ifelse(original_response > response, 1, 0))) %>%
  group_by(change) %>%
  summarize(n = n())
```


## select 25 items equally spaced on implied prevalence


```{r}
df.int.6.filtered.bs[with(df.int.6.filtered.bs, order(mean)),]
with(df.int.6.filtered.bs, order(mean))

df.int.6.filtered.bs[with(df.int.6.filtered.bs, order(mean))[c(seq(1, 75, 3), 75)],] %>%
  mutate(property = factor(property, 
                           levels =  with(df.int.6.filtered.bs, property[order(mean)[c(seq(1, 75, 3), 75)]])
                             
                             )) %>%
  ggplot(., aes( x = property, y = mean, ymin = ci_lower, ymax = ci_upper, fill = property))+
  #geom_pirate(bars = F, violins = F, width_points = 0.2, alpha_points = 0.3)+
  geom_col(position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  coord_flip()+
  scale_fill_viridis(discrete = T)+
  ylim(0, 1)+
  guides(fill = F)
```


```{r output 25 items to json}
left_join(
  df.int.6.filtered.bs[with(df.int.6.filtered.bs, order(mean)[c(seq(1, 75, 3), 75)]),], 
  df.int.6.filtered %>% ungroup() %>% distinct(property, property_type)
) %>%
  select(property, property_type) %>%
  jsonlite::toJSON(., pretty = T)
```

## bootstrap interpretation distributions


```{r bootstrap interpretation distributions}
 bootstrapInterpretationDistributions<- function(i){
  # within each property, you only have one rating per subject
  # hence, you can group by property, and sample rows (subjects)
  df.int.6.filtered.i <- df.int.6.filtered %>% 
    group_by(property) %>%
    sample_n(61, replace = TRUE) %>%
    rowwise() %>%
    mutate(binned_response = round_to_bin(response)) %>%
    group_by(property, binned_response) %>%
    count() %>%
    ungroup() %>%
    spread(binned_response, n)

  df.int.6.filtered.i[is.na(df.int.6.filtered.i)] <- 0

  df.int.6.filtered.i %>%
    gather(state, n, -property) %>%
    group_by(property) %>%
    mutate(prop = n / sum(n),
           prop = round(prop, 5),
           i = i)
 }

no_cores <- detectCores() - 1
cl <- makeCluster(no_cores, type="FORK")
start_time <- Sys.time()
df.int.6.filtered.dists.bs <- bind_rows(
  parLapply(cl, 1:1000, bootstrapInterpretationDistributions)
)

end_time <- Sys.time()
print(end_time - start_time) 
stopCluster(cl)
```

```{r bootstrap interpretation distributions (summarize), fig.width = 10, fig.height = 7}
df.int.6.filtered.dists.bs.summary <- df.int.6.filtered.dists.bs %>%
  mutate(state = as.numeric(state)) %>%
  group_by(property, state) %>%
  summarize(data_lower = quantile(prop, 0.025),
            data_mean = mean(prop),
            data_upper = quantile(prop, 0.975))

ggplot(df.int.6.filtered.dists.bs.summary, 
       aes( x = state, y = data_mean, ymin = data_lower, ymax = data_upper))+
  geom_col(position= position_dodge())+
  geom_errorbar(position = position_dodge())+
  facet_wrap(~property)
```

```{r read in (boostrapped) model predictions}
model.path <- "../../models/results/bootstrap/"
model.prefix <- "generics-bda-L0-btstrp-genint-results-prior3_chunk"

model.files <- list.files(
  path = model.path,
  pattern = model.prefix
)

m.preds <- bind_rows(lapply(model.files, function(modfile){
  read_csv(paste(model.path, modfile, sep = ""))
}))

m.preds.genint.zeroPadded <- left_join(
  expand.grid(
  model = unique(m.preds$model),
  property = unique(m.preds$property),
  iteration = unique(m.preds$iteration),
  state = unique(m.preds$state)
  ), m.preds)

m.preds.genint.zeroPadded[is.na(m.preds.genint.zeroPadded)] <- 0
summary(m.preds.genint.zeroPadded)
```

```{r model expvals, fig.width = 11}
m.preds.zeroPadded.genint.expectations <- m.preds.genint.zeroPadded %>%
  group_by(model, property, iteration) %>%
  summarize(expval = sum(prob*state))

m.pred.uncertain.expvals <- m.preds.zeroPadded.genint.expectations %>%
  filter(model == "uncertain") %>%
  group_by(property) %>%
  summarize(mean_expval = mean(expval))

property.order <- with(m.pred.uncertain.expvals, property[order(mean_expval)])

m.preds.zeroPadded.genint.expectations.summary <- m.preds.zeroPadded.genint.expectations %>%
  group_by(model, property) %>%
  summarize( lower = quantile(expval, 0.025),
             mean = mean(expval),
             upper = quantile(expval, 0.975)) %>%
  ungroup() %>%
  mutate(property = factor(property, levels = property.order))

ggplot(m.preds.zeroPadded.genint.expectations.summary, 
       aes( x = property, y = mean, ymin = lower, ymax = upper, fill = property))+
  geom_col(position= position_dodge(), color  = 'black', alpha = 0.8)+
  geom_errorbar(position = position_dodge())+
  scale_fill_viridis(discrete = T)+
  ylab("Mean implied prevalence")+
  facet_wrap(~model, nrow = 2)+
  theme(axis.text.x = element_blank())
```

```{r scatters expected values}
md.int6.binned.boostrapped <- left_join(m.preds.zeroPadded.genint.expectations %>%
    group_by(model, property) %>%
    summarize( model_lower = quantile(expval, 0.025),
               model_prediction = mean(expval),
               model_upper = quantile(expval, 0.975)),
  df.int.6.filtered.bs) %>%
  ungroup()

left_join(m.preds.zeroPadded.genint.expectations %>%
    group_by(model, property) %>%
    summarize( model_lower = quantile(expval, 0.025),
               model_prediction = mean(expval),
               model_upper = quantile(expval, 0.975)),
  df.int.6.filtered.bs) %>%
  ungroup() %>%   
  mutate(property = factor(property, levels = property.order)) %>%
  ggplot(., aes(x = model_prediction, xmin = model_lower, xmax = model_upper, ymin = ci_lower, y = mean, ymax = ci_upper, fill = property))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.8)+
  geom_errorbar(position = position_dodge(), alpha = 0.8)+
  geom_errorbarh(position = position_dodge(), alpha = 0.4)+
  geom_point(shape = 21, color = 'black')+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  coord_fixed()+
  facet_wrap(~model, nrow = 2)+
  guides(fill = F)

ggsave("figs/interpretation6-filtered-prior3-bootstrap-scatter-all.png", width = 10, height = 5)
```

```{r scatters 3 models}
md.int6.binned.boostrapped %>%
    filter(model %in% c("prior", "uncertain", "fixed_0.125")) %>%
  mutate(property = factor(property, levels = property.order)) %>%
  ggplot(., aes(x = model_prediction, xmin = model_lower, xmax = model_upper, ymin = ci_lower, y = mean, ymax = ci_upper, fill = property))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.8)+
  geom_errorbar(position = position_dodge(), alpha = 0.8)+
  geom_errorbarh(position = position_dodge(), alpha = 0.4)+
  geom_point(shape = 21, color = 'black')+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  coord_fixed()+
  facet_wrap(~model, nrow = 1)+
  guides(fill = F)

ggsave("figs/interpretation6-filtered-prior3-bootstrap-scatter.png", width = 10, height = 5)
md.int6.binned.boostrapped %>%
  group_by(model) %>%
  summarize(r2 = cor(model_prediction, mean)^2,
            mse = mean((model_prediction-mean)^2),
            n = n()) %>%
  kable(.)
```


### not yet used 

```{r model posteriors, fig.width = 20, fig.height = 8}
m.preds.zeroPadded.bins.boostrapped <- m.preds.zeroPadded %>%
  #filter(threshold %in% c("prior", "generic")) %>%
  group_by(model, distribution, state) %>%
  summarize( lower = quantile(prob, 0.025),
             mean = mean(prob),
             upper = quantile(prob, 0.975)) %>%
  ungroup()

m.preds.zeroPadded.bins.boostrapped %>%
  mutate(distribution = factor(distribution, levels = property.order)) %>%
  ggplot(., aes( x = state, y = mean, ymin = lower, ymax = upper, fill = distribution))+
  geom_col(position= position_dodge(), alpha = 0.8, color = 'black')+
  geom_errorbar(position = position_dodge(),  alpha = 1)+
  facet_grid(model~distribution, scales = 'free')+
  scale_x_continuous(breaks = c(0, 0.5 , 1))+
  scale_fill_viridis(discrete = T)+
  ylab("predicted probability")+
  xlab("prevalence")
```

```{r scatters binned_posteriors}
md.int3.binned.boostrapped <- left_join(m.preds.zeroPadded.bins.boostrapped %>%
    rename(model_mean = mean, model_lower = lower, model_upper = upper),
  df.int.6.filtered.dists.bs.summary)


ggplot(md.int3.binned.boostrapped, aes(fill = state,
                x = model_mean, xmin = model_lower, xmax = model_upper,
                y = data_mean, ymin = data_lower, ymax = data_upper))+
  facet_wrap(~model, nrow = 2)+
  geom_errorbar(alpha = 0.2)+
  geom_errorbarh(alpha = 0.2)+
  #coord_fixed()+
  geom_point(shape = 21, color = 'black')+
  #scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  #scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_fill_viridis()+
  theme(legend.position = 'bottom')
  
ggsave("figs/prior-manipulation-3-interpretation-filteredNo0s-n600-modelFits-scatter-distributions.pdf", width = 10, height = 5)
```
