---
title: "Prior elicitation"
output: html_notebook
---

```{r}
library(tidyverse)
library(tidyboot)
library(ggpirate)
library(knitr)
library(viridis)

readData = function(proj){
  read_csv(
    paste("../../data/prior/",proj,"/",
          proj,"-trials.csv", sep = "")
    )
}

readCatchInfo = function(proj){
  read_csv(
    paste("../../data/prior/",proj,"/",
          proj,"-catch_trials.csv", sep = "")
    )
}

readSubjInfo = function(proj){
  read_csv(
    paste("../../data/prior/",proj,"/",
          proj,"-subject_information.csv", sep = "")
    )
}
```

# Prior-1

## Subject information

```{r}
df.prior.1 <- readData("prior-1")
 
df.prior.1.subj <- readSubjInfo("prior-1")
df.prior.1.subj %>%
  select(problems, comments) %>%
  kable()
```

## Catch trials

```{r}
df.prior.1.catch <- readCatchInfo("prior-1")

df.prior.1.catch.summary <- df.prior.1.catch %>%
  group_by(workerid, tested_on) %>%
  summarize(totalCorrect = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, totalCorrect) %>%
  rename(correct_rejection = `0`, 
         hit = `1`) %>%
  mutate(pass = ifelse(hit >= 4 & correct_rejection >= 4, 1, 0),
         totalCorrect = correct_rejection + hit)

df.prior.1.catch.summary %>%
  select(pass) %>%
  table()
```

remove catch trial failures

```{r}
df.prior.1 <- left_join(df.prior.1, df.prior.1.catch.summary %>%
                         select(workerid, totalCorrect, pass))

df.prior.1.filtered <- df.prior.1 %>% filter(pass == 1)

```



## What categories do people produce?

```{r}
df.prior.categories.1 <- df.prior.1.filtered %>%
  filter(trial_type == "category_elicitation")

df.prior.categories.1 %>%
  group_by(response) %>%
  count() %>%
  kable()
```

## Prevalence priors

```{r}
df.prior.prevalence.1 <- df.prior.1.filtered %>%
  filter(trial_type == "prevalence_elicitation", !(is.na(response))) %>%
  mutate(response = as.numeric(response))
```


Histogram of number of responses per item

```{r}
df.prior.prevalence.1 %>%
  group_by(property) %>%
  count() %>%
  ggplot(., aes(x = n))+
  geom_bar()
```

Distribution of all responses (collapse item)

```{r}
df.prior.prevalence.1 %>%
  ggplot(., aes( x = response ))+
  geom_histogram()
```

Item distributions (prevalence priors)

```{r fig.width = 18, fig.height = 8}
df.prior.prevalence.1 %>%
  ggplot(., aes( x = response ))+
  geom_histogram( bins = 20)+
  facet_wrap(~property, scales = 'free') +
  scale_x_continuous(limits = c(-0.1, 1.1), breaks = c(0, 0.5, 1))
```

Distribution of expected values

```{r}
df.prior.1.ev <- df.prior.prevalence.1 %>%
  group_by(property) %>%
  tidyboot_mean(column = response)

ggplot(df.prior.1.ev, aes ( x = mean ))+
  geom_histogram(bins = 20)
```


Distribution of expected values conditional on non-zero prevalence

```{r}
df.prior.1.conditional.ev <- df.prior.prevalence.1 %>%
  filter(response > 0) %>%
  group_by(property) %>%
  tidyboot_mean(column = response)

ggplot(df.prior.1.conditional.ev, aes ( x = mean ))+
  geom_histogram(bins = 20)
```




Copy interpretation df over from `generic-interpretation-1.Rmd`

```{r}
df.prior.1.ev.wInt <- left_join(
  df.prior.1.ev,
  #df.prior.1.conditional.ev,
  df.int.3.filtered.bs %>%
    rename(int_mean = mean, int_upper = ci_upper, int_lower = ci_lower) %>%
    select(property, int_mean, int_upper, int_lower)
) %>%
  mutate(sq_err = (mean - int_mean)^2)

ggplot(df.prior.1.ev.wInt, aes (x = mean, xmin = ci_lower, xmax = ci_upper,
                     y = int_mean, ymin = int_lower, ymax = int_upper))+
  geom_point()+
  geom_errorbar(alpha = 0.2)+
  geom_errorbarh(alpha = 0.2)+
  scale_x_continuous(limits = c(0, 1.1), breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(0, 1.1), breaks = c(0, 0.5, 1))+
  coord_fixed()
```


