---
title: "Prior manipulation pilots and full sample"
output: github_document
---

### author: MH Tessler

### date: April 21, 2019

```{r}
library(tidyverse)
library(tidyboot)
#library(ggpirate)
library(knitr)
library(viridis)
#library(tidytext)
#library(rwebppl)
library(lme4)
library(brms)
#library(jsonlite)
#library(parallel)

# lower_bins <- c(0, 0.01, seq(0.05, 0.95, 0.05), 0.99)
# upper_bins <- c(0.01, seq(0.05, 0.95, 0.05), 0.99, 1)
lower_bins <-seq(0, 0.95, 0.05)
upper_bins <- seq(0.05, 1, 0.05)
mid_bins <- (upper_bins - lower_bins)/2 + lower_bins

round_to_bin <- function(x){
  index <- if (x==0){ 1 } else if (x ==1){ length(mid_bins)} else{
    x <= upper_bins & x > lower_bins
  }
  #if (sum(index) > 1) { print (x) }
  return (mid_bins[index])
}

knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, sanitize = T)

```

# Prior manipulation 3


```{r}
df.pm.prior <- read_csv("../data/paper_data/expt2/expt2a-prior-trials.csv")
df.pm.prior.catch <- read_csv("../data/paper_data/expt2/expt2a-prior-catch_trials.csv")
df.pm.prior.subj <- read_csv("../data/paper_data/expt2/expt2a-prior-subject_information.csv")
```

full data collection

```{r}
df.pm.prior.catch %>%
  select(pass_both) %>%
  table()
```

```{r}
df.pm.prior.subj %>%
  select(problems, comments) %>%
  kable()
```

Native english

```{r}
df.pm.subj.nativeEng <- df.pm.prior.subj %>% 
  select(workerid ,language) %>% 
  mutate(englishNative = grepl("eng", tolower(language)))

#save(d.full.nativeEnglish, file = "../cached_results/english_summary.RData")

table(df.pm.subj.nativeEng$englishNative)

# what do people report for native english that is not english?
df.pm.subj.nativeEng %>%
  filter(!englishNative) %>%
  select(language) %>%
  kable(.)
```

```{r}
df.pm.prior %>%
  distinct(workerid, rt)  %>%
  ggplot(., aes(x = rt / 60000))+
  geom_histogram()+
  xlab("minutes")
  #xlim(0, 10)
###


df.pm.prior.filtered <- left_join(
  left_join(df.pm.prior, df.pm.prior.catch %>%
                         select(workerid, pass_both)),
  df.pm.subj.nativeEng)  %>% 
  filter(pass_both == 1, englishNative)

df.pm.prior.filtered %>%
  distinct(workerid) %>%
  count()
```



### by item histogram

by item counts
```{r}
with(df.pm.prior.filtered %>% distinct(workerid, distribution),
                table(distribution))  %>%
  kable()
```

```{r fig.width = 8}
df.pm.prior.filtered %>%
  ggplot(., aes(x = response))+
  geom_histogram(aes(
    y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]
    ),
    bins = 20, color = 'black', fill = 'grey')+  #scale_fill_viridis(discrete = T)+
  facet_wrap(~ distribution, scales = 'free')+
  scale_x_continuous(limits = c(-0.05, 1.05), breaks = c(0, 0.5, 1))


with(df.trials, table(distribution))
df.trials %>%
  ggplot(., aes(x = response))+
  geom_histogram( bins = 20, color = 'black', fill = 'grey')+#aes(
    #y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]
    #),
     #scale_fill_viridis(discrete = T)+
  facet_wrap(~ distribution, scales = 'free')+
  scale_x_continuous(limits = c(-0.05, 1.05), breaks = c(0, 0.5, 1))


#ggsave("figs/interpretation-5-filtered-n140-hist.pdf", width = 20, height = 14)
```



# Model predictions

```{r read in (boostrapped) model predictions}
model.path <- "../models/results/bootstrap/"

## all of the fixed threshold model predictions in the L1 file are erroneous
## because of a coding error, they are simply the prior
## use L0 file (above) for the fixed_threshold model predictions
#model.prefix.l1 <- "generics-bda-priormanip-L1unlifted-btstrp-results_chunk"
#model.prefix.l0 <- "generics-bda-L0-btstrp-results_chunk"
model.prefix.l1 <- "generics-bda-priormanip-L1unlifted-fixTheFixeds-btstrp-results_chunk"

L1.model.files <- list.files(
  path = model.path,
  pattern = model.prefix.l1
)

# L0.model.files <- list.files(
#   path = model.path,
#   pattern = model.prefix.l0
# )

# m.preds <- bind_rows(lapply(L0.model.files, function(modfile){
#   read_csv(paste(model.path, modfile, sep = ""))
# }))

m.preds <-  bind_rows(lapply(L1.model.files, function(modfile){
  read_csv(paste(model.path, modfile, sep = ""), 
           cols(
            model = col_character(),
            distribution = col_character(),
            iteration = col_integer(),
            state = col_double(),
            prob = col_double()
          ))
}))

# m.preds <- bind_rows(
#   m.preds.L1 %>% 
#     filter(model %in% c("literal", "prior", "pragmatic_unlifted")), 
#   m.preds %>%
#      filter(!(model %in% c("prior", "uncertain")))# %>%
#     # mutate(model = ifelse(model == "prior", "prior_1",
#                    # ifelse(model == "uncertain", "literal_1", model)))
# )

m.preds.zeroPadded <- left_join(
  expand.grid(
  model = unique(m.preds$model),
  distribution = unique(m.preds$distribution),
  iteration = unique(m.preds$iteration),
  state = unique(m.preds$state)
  ), m.preds)

m.preds.zeroPadded[is.na(m.preds.zeroPadded)] <- 0
summary(m.preds.zeroPadded)
```

```{r model expvals, fig.width = 11}
m.preds.zeroPadded.expectations <- m.preds.zeroPadded %>%
  group_by(model, distribution, iteration) %>%
  summarize(expval = sum(prob*state))

m.pred.uncertain.expvals <- m.preds.zeroPadded.expectations %>%
  #filter(model == "uncertain") %>%
  filter(model == "pragmatic_unlifted") %>%
  group_by(distribution) %>%
  summarize(mean_expval = mean(expval))

property.order <- with(m.pred.uncertain.expvals, distribution[order(mean_expval)])

m.preds.zeroPadded.expectations.summary <- m.preds.zeroPadded.expectations %>%
  group_by(model, distribution) %>%
  summarize( lower = quantile(expval, 0.025),
             mean = mean(expval),
             upper = quantile(expval, 0.975)) %>%
  ungroup() %>%
  mutate(distribution = factor(distribution, levels = property.order))

ggplot(m.preds.zeroPadded.expectations.summary, 
       aes( x = distribution, y = mean, ymin = lower, ymax = upper, fill = distribution))+
  geom_col(position= position_dodge(), color  = 'black', alpha = 0.8)+
  geom_errorbar(position = position_dodge())+
  scale_fill_viridis(discrete = T)+
  ylab("Mean implied prevalence")+
  facet_wrap(~model)
```
bootstrapped expectated values

```{r}
ggplot(m.preds.zeroPadded.expectations, aes(x = expval))+
  geom_histogram(bins = 20, fill = 'white', color = 'black')+
  facet_wrap(~model + distribution, scales = 'free')+
  scale_x_continuous(limits = c(-0.03, 1.03))
```


```{r model posteriors, fig.width = 20, fig.height = 8}
m.preds.zeroPadded.bins.boostrapped <- m.preds.zeroPadded %>%
  #filter(threshold %in% c("prior", "generic")) %>%
  group_by(model, distribution, state) %>%
  summarize( lower = quantile(prob, 0.025),
             mean = mean(prob),
             upper = quantile(prob, 0.975)) %>%
  ungroup()

m.preds.zeroPadded.bins.boostrapped %>%
  #mutate(distribution = factor(distribution, levels = property.order)) %>%
  ggplot(., aes( x = state, y = mean, ymin = lower, ymax = upper, fill = distribution))+
  geom_col(position= position_dodge(), alpha = 0.8, color = 'black')+
  geom_errorbar(position = position_dodge(),  alpha = 1)+
  facet_grid(model~distribution, scales = 'free')+
  scale_x_continuous(breaks = c(0, 0.5 , 1))+
  scale_fill_viridis(discrete = T)+
  ylab("predicted probability")+
  xlab("prevalence")
```

# Expt 2b: Interpretation data (prior manipulation)

```{r load catch data pm int}
df.pm.int <- read_csv("../data/paper_data/expt2/expt2b-interpretation-interpretation-trials.csv")
df.pm.int.catch <- read_csv("../data/paper_data/expt2/expt2b-interpretation-catch_trials.csv")
df.pm.int.subj <- read_csv("../data/paper_data/expt2/expt2b-interpretation-interpretation-subject_information.csv")

df.pm.int.catch %>%
  select(pass_both) %>%
  table()
```

```{r load subj info pm int}
df.pm.int.subj %>%
  select(problems, comments) %>%
  kable()
```

Native english

```{r native language pm int}
df.pm.int.subj.nativeEng <- df.pm.int.subj %>% 
  select(workerid ,language) %>% 
  mutate(englishNative = grepl("eng", tolower(language)))

#save(d.full.nativeEnglish, file = "../cached_results/english_summary.RData")

table(df.pm.int.subj.nativeEng$englishNative)

# what do people report for native english that is not english?
df.pm.int.subj.nativeEng %>%
  filter(!englishNative) %>%
  select(language) %>%
  kable(.)
```

Load data

```{r load data and filter pmint3}
df.pm.int %>%
  distinct(workerid, rt)  %>%
  mutate(rt_min = rt / 60000) %>%
  ggplot(., aes(x = rt_min))+
  geom_histogram()+
  xlab("minutes")
  #xlim(0, 10)
###


df.pm.int.filtered <- left_join(
  left_join(df.pm.int, df.pm.int.catch %>%
                         select(workerid, pass_both)),
  df.pm.int.subj.nativeEng) %>% 
  filter(pass_both == 1, englishNative)
#  filter(pass_both == 1, englishNative, response > 0) # the last condition is posthoc (see below about 0 responses)

df.pm.int.filtered %>%
  distinct(workerid) %>%
  count()
```


"0" responses

```{r 0 responses pm int3}
df.pm.int.filtered %>%
  filter(response == 0) %>% 
  group_by(distribution) %>%
  count() %>% 
  kable()

df.pm.int.filtered %>%
  filter(response == 0) %>%
  select(workerid, distribution, experimentResults, explanation) %>%
  kable()
```

- though one person cites that "animals dont have that ability", most of these responses are due to pattern detection. people got distributions that seemed to have a pattern in it. we suspect they ignored the language..

Explaining using the word "pattern"?

```{r explanations using pattern or partner}
df.pm.int %>%
  mutate(mention_pattern = grepl("pattern", tolower(explanation)),
         mention_partner = grepl("partner", tolower(explanation))) %>%
  filter(mention_partner) %>%
  group_by(distribution) %>%
  count()

```

### by item counts

```{r condition ns}
with(df.pm.int.filtered %>% distinct(workerid, distribution),
                table(distribution)) %>%
  kable()

df.prior_manip.int.filtered.n_subj_per_item <- df.pm.int.filtered %>%
  group_by(distribution) %>%
  count() %>% ungroup() %>% summarize(n_subj_per_item = mean(n),
                                      lb = min(n),
                                      ub = max(n))
```


```{r save meta data, eval =F}
expt3.int.catchFail <- sum(!df.pm.3.int.catch$pass_both)
expt3.int.nonEnglish <- sum(!df.pm.3.int.subj.nativeEng$englishNative)
expt3.int.n <- length(unique(df.pm.int.3$workerid))
expt3.int.n.passCatch.English <- length(unique(df.pm.int.3.filtered$workerid))
expt3.int.meanTime <- df.pm.int.3 %>%
  distinct(workerid, rt)  %>%
  summarize(mean_time = mean(rt / 60000))
save(expt3.int.catchFail,
     expt3.int.nonEnglish,
     expt3.int.n,
     expt3.int.n.passCatch.English,
     expt3.int.meanTime,
     df.prior_manip.int.filtered.n_subj_per_item,
  file = "../../paper/cached_results/priorManip_int_metaData.RData")
```


by item histogram

```{r data distributions, fig.width = 8}
df.pm.int.filtered %>%
  ggplot(., aes(x = response))+
  geom_histogram(aes(
    y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]
    ),
    bins = 20, color = 'black', fill = 'grey')+  #scale_fill_viridis(discrete = T)+
  facet_wrap(~ distribution, scales = 'free', nrow = 2)+
  scale_x_continuous(limits = c(-0.2, 1.2), breaks = c(0, 0.5, 1))

# ggsave("figs/prior-manipulation-3-interpretation-filteredNo0s-n600-hist.pdf", width = 12, height = 6)
```

#### what's happening with rare determinsitic

```{r}
df.pm.int.filtered %>%
  filter(distribution == "rare_deterministic",
         response < 0.1) %>%
  select(workerid, distribution, experimentResults, response, explanation) %>%
  kable(.)
```

### analyze expected values

```{r data 95cis}
df.pm.int.filtered.bs <- df.pm.int.filtered %>%
  group_by(distribution) %>%
  tidyboot_mean(column = response)

df.pm.int.filtered.bs %>% ungroup() %>%
  mutate(distribution = factor(distribution, levels = property.order)) %>%
  ggplot(., aes( x = distribution, y = mean, ymin = ci_lower, ymax = ci_upper, fill = distribution))+
  geom_col(position= position_dodge(), color  = 'black', alpha = 0.8)+
  geom_errorbar(position = position_dodge())+
  scale_fill_viridis(discrete = T)+
  ylab("Mean implied prevalence")+
  theme(axis.text.x = element_blank())
```

preregistered prediction ordering []s denote very small difference in predicted

 rare_weak, 
 [weak_or_half, rare_half], 
 [weak_or_strong, uniform], 
 rare_strong, 
 [weak_or_deterministic, half_or_deterministic],
 [strong_or_deterministic, rare_deterministic]
 
 
```{r data model expvals}
md.pm.int.filtered.expvals.bs.summary <- bind_rows(
  df.pm.int.filtered.bs %>% 
    select(-n, -empirical_stat) %>% 
    mutate(model = 'data'),
  m.preds.zeroPadded.expectations.summary %>%
    rename(ci_lower = lower, ci_upper = upper)
)


md.pm.int.filtered.expvals.bs.summary %>% 
  ungroup() %>%
  #filter(!(model %in% c("fixed_0.625", "fixed_0.875"))) %>%
  mutate(distribution = factor(distribution, levels = property.order),
         model = factor(model,
                        levels = c("prior", "literal","pragmatic_unlifted",
                                   "data",
                                   "fixed_0.05", "fixed_0.1",
                                   "fixed_0.3"))) %>%
  ggplot(., aes( x = distribution, y = mean, ymin = ci_lower, ymax = ci_upper, fill = distribution))+
  geom_col(position= position_dodge(), color  = 'black', alpha = 0.8)+
  geom_errorbar(position = position_dodge())+
  scale_fill_viridis(discrete = T)+
  ylab("Mean implied prevalence")+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+
  facet_wrap(~model)+ guides(fill = guide_legend(reverse=T))


# ggsave("figs/prior-manipulation-3-interpretation-filtered-n600-expvals-model-data.pdf", width = 7, height = 5)

```

```{r scatters expected values}
md.pm.int.filtered.expvals.bs.summary.wide <- left_join(m.preds.zeroPadded.expectations %>%
    group_by(model, distribution) %>%
    summarize( model_lower = quantile(expval, 0.025),
               model_prediction = mean(expval),
               model_upper = quantile(expval, 0.975)),
  df.pm.int.filtered.bs) %>%
  ungroup()

md.pm.int.filtered.expvals.bs.summary.wide %>%   
  mutate(distribution = factor(distribution, levels = property.order)) %>%
  ggplot(., aes(x = model_prediction, xmin = model_lower, xmax = model_upper, ymin = ci_lower, y = mean, ymax = ci_upper, fill = distribution))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.8)+
  geom_errorbar(position = position_dodge(), alpha = 0.8)+
  geom_errorbarh(position = position_dodge(), alpha = 0.4)+
  geom_point(shape = 21, color = 'black')+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  coord_fixed()+
  facet_wrap(~model, nrow = 2)+
  guides(fill = F)

#ggsave("figs/prior-manipulation-3-interpretation-filtered-n600-modelFits-scatter.png", width = 10, height = 5)

md.pm.int.filtered.expvals.bs.summary.wide %>%
  group_by(model) %>%
  summarize(r2 = cor(model_prediction, mean) ^2,
            mse = mean((model_prediction-mean)^2)) %>%
  kable(.)
```

### Regression analyses

#### Effect of prior mean?

```{r}
load(file = "../../paper/cached_results/gentInt_manipPriors_dists_expvals.RData")
# md.pm.int.3.filtered.expvals.bs.summary, md.pm.int.3.filtered.dists.bs.summary,
#      md.pm.int.3.filtered.dists.bs.summary.wide, md.pm.int.3.filtered.expvals.bs.summary.wide


df.pm.int.filtered.prior_mean <- left_join(
  df.pm.int.filtered,
  md.pm.int.filtered.expvals.bs.summary %>%
    filter(model == "prior") %>%
    select(distribution, mean) %>%
    rename(prior_mean = mean)
)


rs.lm.priorManip <- lm(data = df.pm.int.filtered.prior_mean,
     response ~ prior_mean)

#save(rs.lm.priorManip,
#     file = "../../paper/cached_results/gentInt_manipPriors_lm.RData")

summary(rs.lm.priorManip)
```


 rare_weak vs. [weak_or_half, rare_half]
 
```{r regression contrast 0}
contrast1.levels <- c("rare_weak", "weak_or_half", "rare_half")
rs.lm.priorManip.contrast1 <- lm(
  data = 
    df.pm.int.filtered.prior_mean %>%
    filter(
      distribution %in% contrast1.levels
      ) %>%
    mutate(distribution = factor(
      distribution, levels = contrast1.levels)
      ),
     response ~ distribution)

summary(rs.lm.priorManip.contrast1)
```


 rare_weak vs. [weak_or_half, rare_half]
 
  0/25, 
 [25/50, 0/50], 
 [25/75, uniform], 
 0/75, 
 [25/100, 50/100],
 [75/100, 0/100]
 
 
```{r regression contrast 1}
contrast1.levels <- c(
  "rare_weak", 
  "weak_or_half", "rare_half",
  "weak_or_strong", "uniform",
  "rare_strong", 
  "weak_or_deterministic","half_or_deterministic",
  "strong_or_deterministic", "rare_deterministic"
  )
rs.lm.priorManip.contrast1 <- lm(
  data = 
    df.pm.int.filtered.prior_mean %>%
    mutate(distribution = factor(
      distribution, levels = contrast1.levels)
      ),
     response ~ distribution)

df.pm.int.filtered.prior_mean$distribution <-  factor(df.pm.int.filtered.prior_mean$distribution,
                                                        levels = contrast1.levels)
custom_contrasts <- MASS::contr.sdif(10)
colnames(custom_contrasts) <- paste("a", seq(1, 9))
contrasts(df.pm.int.filtered.prior_mean$distribution) <- custom_contrasts




rs.lm.priorManip.sdif <- lm(response ~ d,
                            df.pm.int.filtered.prior_mean %>%
                              rename(d = distribution))


summary(rs.lm.priorManip.sdif)
```


 rare_weak, 
 [weak_or_half, rare_half], 
 [weak_or_strong, uniform], 
 rare_strong, 
 [weak_or_deterministic, half_or_deterministic],
 [strong_or_deterministic, rare_deterministic]
 
 
 
```{r}
df.pm.int.filtered.prior_mean$distribution <- factor(df.pm.int.filtered.prior_mean$distribution)

contrasts(df.pm.int.filtered.prior_mean$distribution) <- cbind(c1 = c(-2,1,1,0,0,0,0,0,0,0),
      c2 = c(0, -1, 1, 0,0,0,0,0,0,0),
      c3 = c(-2,-2,-2,3,3,0,0,0,0,0),
      c4 = c(0,0,0,-1,1,0,0,0,0,0),
      c5 = c(0,0,0,-1,-1,2,0,0,0,0),
      c6 = c(0,0,0,0,0,-2,1,1,0,0),
      c7 = c(0,0,0,0,0,0,-1,1,0,0),
      c8 = c(0,0,0,0,0,0,-1,-1,1,1),
      c9 = c(0,0,0,0,0,0,0,0,-1,1)
      )


rs.lm.priorManip.sdif <- lm(response ~ d,
                            df.pm.int.filtered.prior_mean %>%
                              rename(d = distribution))

rs.brm.priorManip.sdif <- brm(
  formula = response ~ d,
  data = df.pm.int.filtered.prior_mean %>% rename(d = distribution),
  family = "zero_one_inflated_beta",
  chains = 3, 
  cores = 3,
  iter = 2000
  )

# save(rs.brm.priorManip.sdif, file = "../../paper/cached_results/gentInt_manipPriors_brms_contrasts.RData")

summary(rs.brm.priorManip.sdif)

contrasts(df.pm.int.filtered.prior_mean$distribution)


tidy(rs.brm.priorManip.sdif) %>%
  mutate(estimate = paste(
    format(estimate, digits = 2),
    " [", format(lower, digits = 2), ", ",
    format(upper, digits = 2), "]", sep =""
  )) %>%
  select(term, estimate)

```




[weak_or_half, rare_half]

```{r regression contrast 2}
contrast2.levels <- c("weak_or_half", "rare_half")
rs.lm.priorManip.contrast2 <- lm(
  data = 
    df.pm.int.filtered.prior_mean %>%
    filter(
      distribution %in% contrast2.levels
      ) %>%
    mutate(distribution = factor(
      distribution, levels = contrast2.levels)
      ),
     response ~ distribution)

summary(rs.lm.priorManip.contrast2)
```

weak_or_half vs. [weak_or_strong, uniform]

```{r regression contrast 3}
contrast3.levels <- c("weak_or_half", "weak_or_strong", "uniform")
rs.lm.priorManip.contrast3 <- lm(
  data = 
    df.pm.int.filtered.prior_mean %>%
    filter(
      distribution %in% contrast3.levels
      ) %>%
    mutate(distribution = factor(
      distribution, levels = contrast3.levels)
      ),
     response ~ distribution)

summary(rs.lm.priorManip.contrast3)
```

 [n.s.] -- [weak_or_strong, uniform] vs.  rare_strong

```{r regression contrast 4}
contrast4.levels <- c("weak_or_strong", "rare_strong")
rs.lm.priorManip.contrast4 <- lm(
  data = 
    df.pm.int.filtered.prior_mean %>%
    filter(
      distribution %in% contrast4.levels
      ) %>%
    mutate(distribution = factor(
      distribution, levels = contrast4.levels)
      ),
     response ~ distribution)

summary(rs.lm.priorManip.contrast4)
```


rare_strong vs. [weak_or_deterministic, half_or_deterministic]

```{r regression contrast 5}
contrast5.levels <- c("rare_strong", "weak_or_deterministic", "half_or_deterministic")
rs.lm.priorManip.contrast5 <- lm(
  data = 
    df.pm.int.filtered.prior_mean %>%
    filter(
      distribution %in% contrast5.levels
      ) %>%
    mutate(distribution = factor(
      distribution, levels = contrast5.levels)
      ),
     response ~ distribution)

summary(rs.lm.priorManip.contrast5)
```

- [n.s.]

[weak_or_deterministic, half_or_deterministic]
vs.
 [strong_or_deterministic, rare_deterministic]
 
```{r regression contrast 6}
contrast6.levels <- c("half_or_deterministic", "rare_deterministic", "strong_or_deterministic")
rs.lm.priorManip.contrast6 <- lm(
  data = 
    df.pm.int.filtered.prior_mean %>%
    filter(
      distribution %in% contrast6.levels
      ) %>%
    mutate(distribution = factor(
      distribution, levels = contrast6.levels)
      ),
     response ~ distribution)

summary(rs.lm.priorManip.contrast6)
```

```{r}
# save(rs.lm.priorManip,
#   rs.lm.priorManip.contrast1,
#   rs.lm.priorManip.contrast2,
#   rs.lm.priorManip.contrast3,
#   rs.lm.priorManip.contrast4,
#   rs.lm.priorManip.contrast5,
#   rs.lm.priorManip.contrast6,
#   file = "../../paper/cached_results/gentInt_manipPriors_lm.RData")

summary(rs.lm.priorManip)
```






### analyze full distibutions

```{r bootstrap interpretation distributions}
 bootstrapInterpretationDistributions<- function(i){
  
  df.pm.3.intDist.filtered.i <- df.pm.int.3.filtered %>% 
    group_by(distribution) %>%
    sample_n(53, replace = TRUE) %>%
    rowwise() %>%
    mutate(binned_response = round_to_bin(response)) %>%
    group_by(distribution, binned_response) %>%
    count() %>%
    ungroup() %>%
    spread(binned_response, n)

  df.pm.3.intDist.filtered.i[is.na(df.pm.3.intDist.filtered.i)] <- 0

  df.pm.3.intDist.filtered.i %>%
    gather(state, n, -distribution) %>%
    group_by(distribution) %>%
    mutate(prop = n / sum(n),
           prop = round(prop, 5),
           i = i)
}

no_cores <- detectCores() - 1
cl <- makeCluster(no_cores, type="FORK")
start_time <- Sys.time()
df.pm.int.3.filtered.dists.bs <- bind_rows(
  parLapply(cl, 1:5000, bootstrapInterpretationDistributions)
)

end_time <- Sys.time()
print(end_time - start_time) 
stopCluster(cl)
```
 
```{r write bootstrap interpretation distributions}
df.pm.int.3.filtered.dists.bs %>% 
  select(-prop) %>%
  spread(state, n) %>%
  jsonlite::toJSON(., pretty = F) %>%
  write(., "../../models/generics-bda-L0-btstrp-interpretations-notPretty.json")




### non boostrapped

  df.pm.3.intDist.filtered.0 <- df.pm.int.3.filtered %>% 
    rowwise() %>%
    mutate(binned_response = round_to_bin(response)) %>%
    group_by(distribution, binned_response) %>%
    count() %>%
    ungroup() %>%
    spread(binned_response, n)

  df.pm.3.intDist.filtered.0[is.na(df.pm.3.intDist.filtered.0)] <- 0

  df.pm.3.intDist.filtered.0 %>%
    gather(state, n, -distribution) %>%
    group_by(distribution) %>%
    mutate(prop = (n+1) / sum(n + 1),
           prop = round(prop, 5)) %>%
  select(-prop) %>%
  spread(state, n) %>%
  jsonlite::toJSON(., pretty = T) %>%
  write(., "../../models/generics-bda-L0-interpretations-counts.json")
```

```{r bootstrap interpretation distributions (summarize)}

df.pm.int.3.filtered.dists.bs.summary <- df.pm.int.3.filtered.dists.bs %>%
  mutate(state = as.numeric(state)) %>%
  group_by(distribution, state) %>%
  summarize(data_lower = quantile(prop, 0.025),
            data_mean = mean(prop),
            data_upper = quantile(prop, 0.975))


md.pm.int.3.filtered.dists.bs.summary <-bind_rows(m.preds.zeroPadded.bins.boostrapped,
          df.pm.int.3.filtered.dists.bs.summary %>% rename(lower = data_lower, mean = data_mean,upper= data_upper) %>%
            mutate(model = 'data'))




ggplot(df.pm.int.3.filtered.dists.bs.summary, 
       aes( x = state, y = data_mean, ymin = data_lower, ymax = data_upper))+
  geom_col(position= position_dodge())+
  geom_errorbar(position = position_dodge())+
  facet_wrap(~distribution, nrow = 2)
```

```{r scatters binned_posteriors}
md.pm.int.3.filtered.dists.bs.summary.wide <- left_join(m.preds.zeroPadded.bins.boostrapped %>%
    rename(model_mean = mean, model_lower = lower, model_upper = upper),
  df.pm.int.3.filtered.dists.bs.summary)


ggplot(md.pm.int.3.filtered.dists.bs.summary.wide, aes(fill = state,
                x = model_mean, xmin = model_lower, xmax = model_upper,
                y = data_mean, ymin = data_lower, ymax = data_upper))+
  facet_wrap(~model, nrow = 2)+
  geom_errorbar(alpha = 0.2)+
  geom_errorbarh(alpha = 0.2)+
  #coord_fixed()+
  geom_point(shape = 21, color = 'black')+
  #scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  #scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_fill_viridis()+
  theme(legend.position = 'bottom')
  

save(md.pm.int.3.filtered.expvals.bs.summary, md.pm.int.3.filtered.dists.bs.summary,
     md.pm.int.3.filtered.dists.bs.summary.wide, md.pm.int.3.filtered.expvals.bs.summary.wide,
     file = "../../paper/cached_results/gentInt_manipPriors_dists_expvals2.RData")

ggsave("figs/prior-manipulation-3-interpretation-filteredNo0s-n600-modelFits-scatter-distributions.pdf", width = 10, height = 5)


md.pm.int.3.filtered.dists.bs.summary.wide %>%
  group_by(model) %>%
  summarize(r2 = cor(model_mean, data_mean) ^2,
            mse = mean((model_mean-data_mean)^2),
            n = n()) %>%
  kable(.)
```

```{r scatters binned_posteriors 3 models}
md.pm.int.3.filtered.dists.bs.summary.wide %>%
  filter(model %in% c("prior", "literal", "pragmatic_unlifted", "fixed_0.125"),
         data_mean < 0.25) %>%
ggplot(., aes(fill = state,
                x = model_mean, xmin = model_lower, xmax = model_upper,
                y = data_mean, ymin = data_lower, ymax = data_upper))+
  facet_wrap(~model)+
  geom_errorbar(alpha = 0.2)+
  geom_errorbarh(alpha = 0.2)+
  #coord_fixed()+
  geom_point(shape = 21, color = 'black')+
  #scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  #scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_fill_viridis()+
  theme(legend.position = 'bottom')

ggsave("figs/prior-manipulation-3-interpretation-filteredNo0s-focus-n600-modelFits-scatter-distributions.pdf", width = 10, height = 5)
```

```{r uncertain model residuals}
md.int3.binned.boostrapped %>%
  #filter(model %in% c("prior", "uncertain", "fixed_0.125")) %>%
  filter(model %in% c("uncertain"),
         model_mean < 0.1, data_mean > 0.1) %>%
  mutate(absErr = abs(model_mean-data_mean),
         sqErr = absErr^2) %>% 
  View()
```

rare weak and rare determinsitic at the lowest bin (0.025) are the only points where the CIs dont overlap. why is this?

```{r}
df.pm.int.3.filtered %>%
  filter(distribution %in% c("rare_deterministic", "rare_weak"),
         response < 0.1) %>% 
  select(workerid, rt, distribution, response, explanation, experimentResults) %>%
  kable(.)
```

explanations all had to do with pattern matching. some participants randomly got a distribution that had an especially deviant pattern to it.

Where does fixed0.125 go wrong?

- dont yet understand this.
```{r fixed model residual}
md.int3.binned.boostrapped %>%
  #filter(model %in% c("prior", "uncertain", "fixed_0.125")) %>%
  filter(model %in% c("fixed_0.125"),
         model_mean > 0.1, data_mean < 0.1) %>%
  mutate(absErr = abs(model_mean-data_mean),
         sqErr = absErr^2) %>% 
  View()
```


### Model likelhoods / model comparison

```{r load model likelihood results}
#model.likelihoods <- read_csv("../../models/results/bootstrap/generics-bda-L0-btstrpPriors-likelihood-results_sampleFromPriorProb0.01.csv")



model.path <- "../../models/results/bootstrap/"
model.prefix <- "generics-bda-L0-btstrpPriors-likelihood-results_sampleFromPriorProb"

sample_from_prior_probs <- c(0.0001,0.0005,0.001,
                             0.005, 0.01, 0.05, 0.1, 0.15)


m.ll <- data.frame()
for (sfpp in sample_from_prior_probs){
  
  model.files <- list.files(
    path = model.path,
    pattern = paste(model.prefix, sfpp, ".csv", sep = "")
  )

  for (modfile in model.files){
    m.item <- read_csv(paste(model.path , modfile, sep = ""))
  
    m.ll <- bind_rows(
      m.ll,
      m.item %>% mutate(noiseProb = sfpp)
    )
    
  }
}
```


```{r model likelihoods summarized}
model.likelihoods.summarized <- m.ll %>%
  # filter(distribution %in% c("rare_weak", "rare_strong",
  #                            "rare_half", "rare_deterministic")) %>%
  group_by(model, noiseProb, iteration) %>%
  summarize(sum_likelihood = sum(likelihood)) %>%
  group_by(model, noiseProb) %>%
  summarize(lower_likelihood = quantile(sum_likelihood, 0.025),
            mean_likelihood = mean(sum_likelihood),
            upper_likelihood = quantile(sum_likelihood, 0.975))



model.order <- with(filter(model.likelihoods.summarized, noiseProb == 0.01), model[order(mean_likelihood)])

model.likelihoods.summarized %>%
  ungroup() %>%
  mutate(model = factor(model, levels = model.order)) %>%
  ggplot(., aes( x = model, y = mean_likelihood, ymin = lower_likelihood, ymax = upper_likelihood, fill = model))+
  geom_col(position= position_dodge(), color  = 'black', alpha = 0.8)+
  geom_errorbar(position = position_dodge(), width = 0.3)+
  scale_fill_viridis(discrete = T)+
  ylab("log p (d | m)")+
  facet_wrap(~noiseProb)+
  theme(axis.text.x = element_blank())

#Wggsave("figs/prior-manipulation-3-model-likelihoods-facetNoiseProb.pdf", width = 8, height = 5)
```


```{r bayes factors}
model.likelihoodRatios.summarized <- m.ll %>%
  # filter(distribution %in% c("rare_weak", "rare_strong",
  #                            "rare_half", "rare_deterministic")) %>%
  group_by(model, noiseProb, iteration) %>%
  summarize(sum_likelihood = sum(likelihood)) %>%
  ungroup() %>%
  spread(model, sum_likelihood) %>%
  gather(alternative_model, alternative_model_sum_likelihood, 
         -iteration, -uncertain, -noiseProb) %>%
  mutate(log_bf_uncertain_alternative = uncertain - alternative_model_sum_likelihood) %>%
  group_by(alternative_model, noiseProb) %>%
  summarize(lower_log_bf = quantile(log_bf_uncertain_alternative, 0.025),
            expected_log_bf= mean(log_bf_uncertain_alternative),
            upper_log_bf = quantile(log_bf_uncertain_alternative, 0.975))


model.likelihoodRatios.summarized %>%
  # mutate(alternative_model = factor(alternative_model, levels = alternative_model[with(model.likelihoodRatios.summarized, order(expected_log_bf))])) %>%
  ggplot(., aes( x = alternative_model, y = expected_log_bf, ymin = lower_log_bf, ymax = upper_log_bf, fill = alternative_model))+
  geom_col(position= position_dodge(), color  = 'black', alpha = 0.8)+
  geom_errorbar(position = position_dodge(), width = 0.3)+
  scale_fill_viridis(discrete = T)+
  facet_wrap(~noiseProb)+
  ylim(0, 50)+
  ylab("log [ p (d | generics model) / p (d | alternative model) ]")+
  theme(axis.text.x = element_blank())


model.likelihoodRatios.summarized %>% kable(.)

#save(model.likelihoodRatios.summarized, file = "../../paper/cached_results/genint_manipPriors_bf.RData")
```

## bootstrap priors (then write, and read into webppl)
```{r eval = F}
bootstrapPriors <- function(i){
  
  df.pm.filtered.priors.i <- df.pm.prior.filtered %>% 
    spread(category, response) %>%
    group_by(distribution) %>%
    sample_n(40, replace = TRUE) %>%
    gather(category, response, K, L, M, N, O)  %>%
    rowwise() %>%
    mutate(binned_response = round_to_bin(response)) %>%
    group_by(distribution, binned_response) %>%
    count() %>%
    ungroup() %>%
    spread(binned_response, n)

  df.pm.3.filtered.priors.i[is.na(df.pm.3.filtered.priors.i)] <- 0


df.pm.3.filtered.priors.wpReady <- df.pm.3.filtered.priors.i %>%
  gather(state, n, -distribution) %>%
  group_by(distribution) %>%
  mutate(prop = (n+1) / sum(n + 1),
         prop = round(prop, 5),
         i = i)
df.pm.3.filtered.priors.wpReady
}

no_cores <- detectCores() - 1
cl <- makeCluster(no_cores, type="FORK")
start_time <- Sys.time()
df.pm.3.filtered.priors.bs <- bind_rows(
  parLapply(cl, 1:1000, bootstrapPriors)
)

end_time <- Sys.time()
print(end_time - start_time) 
stopCluster(cl)
```

```{r visualize bootstrapped priors, eval = F}
head(df.pm.3.filtered.priors.bs)

df.pm.3.filtered.priors.bs.summary <- df.pm.3.filtered.priors.bs %>%
  mutate(state = as.numeric(state)) %>%
  group_by(distribution, state) %>%
  summarize( lower = quantile(prop, 0.025),
             mean = mean(prop),
             upper = quantile(prop, 0.975))


df.pm.3.filtered.priors.bs.summary %>%
  ggplot(., aes( x = state, y = mean, ymin = lower, ymax = upper))+
  geom_col(position= position_dodge())+
  geom_errorbar(position = position_dodge())+
  facet_wrap(~distribution, nrow = 2)

```

```{r write bootstrapped priors, eval = F}
df.pm.3.filtered.priors.bs %>% 
  select(-n) %>%
  spread(state, prop) %>%
  jsonlite::toJSON(., pretty = F) %>%
  write(., "../../models/generics-bda-L0-btstrp-priors-notPretty.json")
```


## Explanations that don't use the word "pattern"

```{r}
df.pm.int %>%
  mutate(mention_pattern = grepl("pattern", tolower(explanation))) %>%
  filter(!mention_pattern) %>%
  select(workerid, distribution, experimentResults, response, explanation) %>%
  kable()
```

