---
title: "Analysis of Experiments 1: Prior elicitation and Generic interpretation"
output: github_document
---

### author: MH Tessler

### date: April 21, 2019

# libraries

```{r}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, cache=F, message=FALSE, sanitize = T)
```


```{r libraries}
library(tidyverse)
library(tidyboot)
library(tidytext)
#library(ggpirate)
library(knitr)
#library(viridis)
```

# Experiment 1a: Prior Elicitation

## Subject information

```{r load prior data}
df.prior <- read_csv("../data/paper_data/expt1/expt1a-prior-trials.csv")
df.prior.catch <- read_csv("../data/paper_data/expt1/expt1a-prior-catch_trials.csv")
df.prior.subj <- read_csv("../data/paper_data/expt1/expt1a-prior-subject_information.csv")
```


```{r prior english}

df.prior.english <- df.prior.subj %>% 
  select(workerid ,language) %>% 
  mutate(english = grepl("en", tolower(language)))

expt1a.prior.n <- length(unique(df.prior$workerid))

print("english native?")
table(df.prior.english$english)

print("what do people report for native language that is not english?")

df.prior.english %>%
  filter(!english) %>%
  select(language) %>%
  kable(.)
```

## Catch trials

```{r prior memory check trials}
df.prior.catch.summary <- df.prior.catch %>%
  group_by(workerid, tested_on) %>%
  summarize(totalCorrect = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, totalCorrect) %>%
  rename(correct_rejection = `0`, 
         hit = `1`) %>%
  mutate(pass = ifelse(hit >= 4 & correct_rejection >= 4, 1, 0),
         totalCorrect = correct_rejection + hit)


df.prior.catch.pass <- sum(!df.prior.catch.summary$pass)

print("pass memory check")

df.prior.catch.summary %>%
  select(pass) %>%
  table()
```

remove catch trial failures

```{r prior exclusion}
df.prior.filtered <- left_join(
  df.prior, 
  df.prior.catch.summary %>% select(workerid, totalCorrect, pass)
  ) %>% left_join(., 
  df.prior.english) %>%
  filter(pass == 1, english)

expt1a.prior.n.passCatch.English <- length(unique(df.prior.filtered$workerid))
expt1a.prior.n.passCatch.English
```


How long did the experiemnt take?

```{r prior expt length(time)}
df.prior.filtered.meanTime <- df.prior.filtered %>%
  distinct(workerid, rt, trial_num, trial_type) %>%
  group_by(workerid) %>%
  summarize(total_time = sum(rt / 1000)) %>%
  ungroup() %>%
  summarize(mean_time = mean(total_time) / 60)

df.prior.filtered.meanTime
```




## Prevalence priors

```{r prevalence prior results}
df.prior.filtered.prevalence <- df.prior.filtered %>%
  filter(trial_type == "prevalence_elicitation", !(is.na(response))) %>%
  mutate(response = as.numeric(response),
         property = gsub("&quotechar", "", property))
```


### Histogram of number of responses per item

```{r prior hist n_responses per item}

df.prior.filtered.prevalence.n_subj_per_item <- df.prior.filtered.prevalence %>%
  group_by(property) %>%
  count() %>% ungroup() %>% summarize(n_subj_per_item = mean(n / 5),
                                      lb = min(n / 5),
                                      ub = max(n / 5))

df.prior.filtered.prevalence %>%
  group_by(property) %>%
  count() %>%
  ggplot(., aes(x = n / 5))+
  geom_bar()+
  ylab("number of items")+
  xlab("number of participants that rated item")


# save(expt2.prior.n,
#      expt2.prior.nonEnglish,
#      expt2.prior.catchFail,
#      expt2.prior.n.passCatch.English,
#      df.prior.3.filtered.meanTime, 
#      df.prior.3.filtered.n_subj_per_item,
#      file = "../../paper/cached_results/genint_priors_metaData.RData")

```

### Distribution of all responses (collapse item)

```{r prior hist all responses}
df.prior.filtered.prevalence %>%
  ggplot(., aes( x = response ))+
  geom_histogram()
```

### Item distributions (prevalence priors)

```{r priors by item, fig.width = 18, fig.height = 12}
df.prior.filtered.prevalence %>%
  ggplot(., aes( x = response ))+
  geom_histogram( bins = 20,aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]
    ))+
  facet_wrap(~property, scales = 'free') +
  scale_x_continuous(limits = c(-0.1, 1.1), breaks = c(0, 0.5, 1))

#ggsave("figs/prior-3-prevpriors-n144.pdf", width = 20, height = 14)
```

### Item distributions conditional on > 0

```{r priors nonzero by item, fig.width = 18, fig.height = 12}
df.prior.filtered.prevalence %>%
  filter(response > 0) %>%
  ggplot(., aes( x = response ))+
  geom_histogram( bins = 20,aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]
    ))+
  facet_wrap(~property, scales = 'free') +
  scale_x_continuous(limits = c(-0.1, 1.1), breaks = c(0, 0.5, 1))

#ggsave("figs/prior-3-prevpriorsNonZero-n144.pdf", width = 20, height = 14)
```

### Distribution of expected values

```{r priors expected values}
df.prior.filtered.prevalence.ev <- df.prior.filtered.prevalence %>%
  group_by(property) %>%
  tidyboot_mean(column = response)

ggplot(df.prior.filtered.prevalence.ev, aes ( x = mean ))+
  geom_histogram(bins = 30)

#ggsave("figs/prior-3-expvals-n144.pdf", width = 4, height = 4)

```


### Distribution of expected values conditional on non-zero prevalence

```{r priors nonxero expected values}
df.prior.filtered.prevalence.nonzero.ev <- df.prior.filtered.prevalence %>%
  filter(response > 0) %>%
  group_by(property) %>%
  tidyboot_mean(column = response)

ggplot(df.prior.filtered.prevalence.nonzero.ev, aes ( x = mean ))+
  geom_histogram(bins = 20)

#ggsave("figs/prior-3-nonZeroExpvals-n144.pdf", width = 4, height = 4)

```

### Distribution of proportion of probability mass at 0

```{r priors is zero}
df.prior.prevalence.isZero <- df.prior.filtered.prevalence %>%
  mutate(isZero = ifelse(response == 0, 1, 0)) %>%
  group_by(property) %>%
  tidyboot_mean(column = isZero)

ggplot(df.prior.prevalence.isZero, aes ( x = mean ))+
  geom_histogram(bins = 20)

#ggsave("figs/prior-3-isZero-n144.pdf", width = 4, height = 4)
```

### Propoortion IS ZERO vs nonzero Expectation

```{r priors is zero vs nonzero expectation}

df.prior.conditional.ev <- df.prior.filtered.prevalence %>%
  filter(response > 0) %>%
  group_by(property) %>%
  tidyboot_mean(column = response)


df.prior.prevalence.isZero.conditionalEv <- left_join(
  df.prior.conditional.ev %>%
    select(-n, -empirical_stat) %>%
    rename(pwp_mean = mean, pwp_low = ci_lower, pwp_high = ci_upper),
  df.prior.prevalence.isZero %>%
    select(-n, -empirical_stat) %>%
    rename(isZero = mean, zero_low = ci_lower, zero_high = ci_upper)
)

ggplot(df.prior.prevalence.isZero.conditionalEv, 
       aes( x = 1-isZero, xmin = 1-zero_low, xmax = 1-zero_high,
            y = pwp_mean, ymin = pwp_low, ymax = pwp_high))+
  geom_errorbar(alpha = 0.3) + geom_errorbarh(alpha = 0.3) + 
  geom_point(shape = 21, size = 2.6, color = 'black', fill = 'black')+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  ylab("Prevalence when present")+
  xlab("P(feature is present)")
```


### Prevalence priors for sample items

```{r priors sample items, fig.width=6}
target.properties <- c("eat insects", 
                       "feed on the carcasses of dead animals",
                       "are afraid of loud noises",
                       "get in fights with other animals",
                       "live in urban areas",
                       "live in zoos",
                       #"drink alcohol left behind by tourists",
                       "chase their tails",
                       "have seizures")
var_width <- 20

# save(df.prior.prevalence.3.isZero.conditionalEv,
#      df.prior.prevalence.3,
#      file = "../../paper/cached_results/genInt_priors.RData"
#      )

df.prior.filtered.prevalence %>%
  filter(property %in% target.properties) %>%
  mutate(property = factor(property, levels = target.properties,
                           labels = stringr::str_wrap(target.properties, 
                                                      width = var_width))) %>%
  ggplot(., aes( x = response ))+
  geom_histogram( 
    bins = 20,
    aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
    color = 'black', fill= 'white')+
  facet_wrap(~property, scales = 'free', nrow = 2) +
  scale_x_continuous(limits = c(-0.1, 1.1), breaks = c(0, 0.5, 1))+
  ylab("Proportion of responses")+
  xlab("Prevalence")

```



# Experiment 1b: Generic Interpretation

```{r load data}
df.int <- read_csv("../data/paper_data/expt1/expt1b-interpretation-trials.csv")
df.int.subj <- read_csv("../data/paper_data/expt1/expt1b-interpretation-subject_information.csv")
df.int.catch <- read_csv("../data/paper_data/expt1/expt1b-interpretation-catch_trials.csv")
```

Native language of English

```{r native english}
df.int.subj.english <- df.int.subj %>%
  select(workerid, language) %>%
  mutate(english = str_detect(tolower(language), "en"),
         english = ifelse(is.na(english), F, english))

paste(sum(df.int.subj.english$english), " out of ", length(df.int.subj.english$english), " subjects self report native language of english", sep = "")
```


### Memory check trials

```{r exclusion criteria}
df.int.catch.summarized <- df.int.catch %>%
  group_by(workerid, tested_on) %>% 
  summarise(n_correct = sum(correct)) %>%
  ungroup() %>%
  mutate(tested_on = factor(tested_on, levels = c(0, 1), 
                            labels = c("correct rejections", "hits")))

df.int.catch.pass <- df.int.catch.summarized %>%
  spread(tested_on, n_correct) %>%
  group_by(workerid) %>%
  summarise(pass = (hits > 3) && (`correct rejections` > 3))

print(
  paste(
    sum(df.int.catch.pass$pass), " out of ", 
    length(df.int.catch.pass$pass), " participants pass memory check",
    sep = ""
  ))


df.int.catch.summarized %>%
  ggplot(., aes( x = n_correct ))+
  geom_bar()+
  facet_wrap(~tested_on)+
  ylab("Number of subjects")
```

Exclude subjects who do not get at least 4 / 5 correct on both correct rejections and false alarms, as well as non-English speakers. 

```{r exclude subjects}
df.int.filtered <- left_join(
  df.int,
  df.int.catch.pass
  ) %>% left_join(.,
    df.int.subj.english
  ) %>%
    filter(pass, english)

print(
  paste(
    length(unique(df.int.filtered$workerid)), " out of ", 
    length(df.int.catch.pass$pass), " participants pass exclusion criteria",
    sep = ""
  ))

```

## Bootstrap CIs for by-item plot

```{r bootstrap, fig.width=8, fig.height=10}
df.int.filtered.bs <- df.int.filtered %>%
  group_by(property) %>%
  tidyboot_mean(column = response)

df.int.filtered <- df.int.filtered %>% 
    mutate(property = factor(property, 
                           levels =  with(df.int.filtered.bs, property[order(mean)])))
  
df.int.filtered.bs %>%
  mutate(property = factor(property,
                           levels =  with(df.int.filtered.bs, property[order(mean)]))) %>%
  ggplot(., aes( x = property, y = mean))+
  #geom_hline(yintercept = 0.5, lty = 2, alpha = 0.5)+
  geom_point(shape = 73, size = 4)+
  geom_point(data = df.int.filtered, position = position_jitter(),
             inherit.aes = F, aes( x = property, y = response),
             alpha = 0.1)+
  # geom_col(position = position_dodge(0.8),
  #          aes(y = mean),
  #          width = 0.8, alpha = 0.3, color = 'black')+
    coord_flip()+
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),
                position = position_dodge(0.8), width = 0.3, size = 1)+
  ylab("Implied prevalence rating")+
  scale_y_continuous(limits = c(-0.03, 1.03), breaks = c(0, 0.5, 1))+
  #scale_fill_solarized()+
  #scale_color_solarized()+
  xlab("")
```



### by item histogram

```{r by item histogram, fig.width = 13, fig.height = 10}
df.int.filtered %>%
  ggplot(., aes(x = response ))+
  geom_histogram()+
  facet_wrap(~property, scales = 'free')+
  xlim(-0.03, 1.03)
```

### by subject hists

```{r by subject hist, fig.width = 14, fig.height = 11}
df.int.filtered %>%
  ggplot(., aes(x = response ))+
  geom_histogram()+
  facet_wrap(~workerid, scales = 'free')+
  xlim(-0.03, 1.03)
```



# Replication data set

```{r load replication data}
df.int.rep <- read_csv("../data/paper_data/expt1/expt1b-rep-interpretation-trials.csv")
df.int.rep.subj <- read_csv("../data/paper_data/expt1/expt1b-rep-interpretation-subject_information.csv")
df.int.rep.catch <- read_csv("../data/paper_data/expt1/expt1b-rep-interpretation-catch_trials.csv")
```



Native language of English

```{r rep native english}
df.int.rep.subj.english <- df.int.rep.subj %>%
  select(workerid, language) %>%
  mutate(english = str_detect(tolower(language), "en"),
         english = ifelse(is.na(english), F, english))

paste(sum(df.int.rep.subj.english$english), " out of ", length(df.int.rep.subj.english$english), " subjects self report native language of english", sep = "")
```


### Memory check

```{r rep exlcusion criteria}
df.int.rep.catch.summarized <- df.int.rep.catch %>%
  group_by(workerid, tested_on) %>% 
  summarise(n_correct = sum(correct)) %>%
  ungroup() %>%
  mutate(tested_on = factor(tested_on, levels = c(0, 1), 
                            labels = c("correct rejections", "hits")))

df.int.rep.catch.pass <- df.int.rep.catch.summarized %>%
  spread(tested_on, n_correct) %>%
  group_by(workerid) %>%
  summarise(pass = (hits > 3) && (`correct rejections` > 3))

print(
  paste(
    sum(df.int.rep.catch.pass$pass), " out of ", 
    length(df.int.rep.catch.pass$pass), " participants pass memory check",
    sep = ""
  ))


df.int.rep.catch.summarized %>%
  ggplot(., aes( x = n_correct ))+
  geom_bar()+
  facet_wrap(~tested_on)+
  ylab("Number of subjects")
```

Exclude subjects who do not get at least 4 / 5 correct on both correct rejections and false alarms, as well as non-English speakers. 

```{r rep exclude subjects}
df.int.rep.filtered <- left_join(
  df.int.rep,
  df.int.rep.catch.pass
  ) %>% left_join(.,
    df.int.rep.subj.english
  ) %>%
    filter(pass, english)

print(
  paste(
    length(unique(df.int.rep.filtered$workerid)), " out of ", 
    length(df.int.rep.catch.pass$pass), " participants pass exclusion criteria",
    sep = ""
  ))

```

## Bootstrap CIs for by-item plot

```{r rep bootstrap, fig.width=8, fig.height=10}
df.int.rep.filtered.bs <- df.int.rep.filtered %>%
  group_by(property) %>%
  tidyboot_mean(column = response)


df.int.rep.filtered <- df.int.rep.filtered %>% 
    mutate(property = factor(property, 
                           levels =  with(df.int.rep.filtered.bs, property[order(mean)])))
  
df.int.rep.filtered.bs %>%
  mutate(property = factor(property,
                           levels =  with(df.int.rep.filtered.bs, property[order(mean)]))) %>%
  ggplot(., aes( x = property, y = mean))+
  #geom_hline(yintercept = 0.5, lty = 2, alpha = 0.5)+
  geom_point(shape = 73, size = 4)+
  geom_point(data = df.int.rep.filtered, position = position_jitter(),
             inherit.aes = F, aes( x = property, y = response),
             alpha = 0.1)+
  # geom_col(position = position_dodge(0.8),
  #          aes(y = mean),
  #          width = 0.8, alpha = 0.3, color = 'black')+
    coord_flip()+
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),
                position = position_dodge(0.8), width = 0.3, size = 1)+
  ylab("Implied prevalence rating")+
  scale_y_continuous(limits = c(-0.03, 1.03), breaks = c(0, 0.5, 1))+
  #scale_fill_solarized()+
  #scale_color_solarized()+
  xlab("")
```


## Comparison of main experiment and replication


```{r comparison main and rep}
df.int.filtered.bs.main.rep <- left_join(
  df.int.filtered.bs,
  df.int.rep.filtered.bs %>%
    select(-empirical_stat, -n) %>%
    rename(rep_mean = mean, rep_ci_upper = ci_upper, rep_ci_lower = ci_lower)
)

print(paste("correlation of two data set means  = ", with(df.int.filtered.bs.main.rep, cor(mean, rep_mean, use = "pairwise.complete.obs"), sep = "")))

ggplot(df.int.filtered.bs.main.rep, aes( x = mean, y = rep_mean,
                                         xmin = ci_lower, xmax = ci_upper,
                                         ymin = rep_ci_lower, ymax = rep_ci_upper))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.4)+
  geom_point()+
  geom_linerange(alpha = 0.3)+
  geom_errorbarh(alpha = 0.3)+
  xlim(0, 1)+ylim(0, 1)+
  coord_fixed()
```


## Comparison of generic interpretation and the prevalence prior

```{r}
df.prior.ev.wInt <- left_join(
  df.prior.filtered.prevalence.ev,
  #df.prior.3.conditional.ev,
  df.int.filtered.bs %>%
    rename(int_mean = mean, int_upper = ci_upper, int_lower = ci_lower) %>%
    select(property, int_mean, int_upper, int_lower)
) %>%
  mutate(sq_err = (mean - int_mean)^2)

ggplot(df.prior.ev.wInt, aes (x = mean, xmin = ci_lower, xmax = ci_upper,
                     y = int_mean, ymin = int_lower, ymax = int_upper))+
  geom_point()+
  geom_errorbar(alpha = 0.2)+
  geom_errorbarh(alpha = 0.2)+
  scale_x_continuous(limits = c(0, 1.1), breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(0, 1.1), breaks = c(0, 0.5, 1))+
  coord_fixed()
```

## Comparison of generic interpretation and the conditional, non-zero prevalence prior


```{r}
df.prior.nonZeroev.wInt <- left_join(
  #df.prior.filtered.prevalence.ev,
  df.prior.filtered.prevalence.nonzero.ev,
  df.int.filtered.bs %>%
    rename(int_mean = mean, int_upper = ci_upper, int_lower = ci_lower) %>%
    select(property, int_mean, int_upper, int_lower)
) %>%
  mutate(sq_err = (mean - int_mean)^2)

ggplot(df.prior.nonZeroev.wInt, aes (x = mean, xmin = ci_lower, xmax = ci_upper,
                     y = int_mean, ymin = int_lower, ymax = int_upper))+
  geom_point()+
  geom_errorbar(alpha = 0.2)+
  geom_errorbarh(alpha = 0.2)+
  scale_x_continuous(limits = c(0, 1.1), breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(0, 1.1), breaks = c(0, 0.5, 1))+
  coord_fixed()
```


## What categories do people produce in the prevalence prior elicitation?

```{r prior free production categories}
df.prior.categories <- df.prior.filtered %>%
  filter(trial_type == "category_elicitation") %>%
  mutate(response = gsub("&quotechar", "", response)) %>%
  unnest_tokens(word, response) %>%
  anti_join(stop_words)

d.tidy.wordCounts <- df.prior.categories %>%
  count(animal_class,word)

d.tidy.wordCounts[with(d.tidy.wordCounts, order(animal_class, -n)),] %>%
  kable()
```

## Subject comments and information

#### Prior experiment 

```{r prior subj comments}
df.prior.subj %>%
  select(problems, comments) %>%
  kable()
```


#### Main experiment 

```{r subj comments}
df.int.subj %>%
  select(problems, comments) %>%
  kable()
```

#### Replication experiment 

```{r rep subj comments}
df.int.rep.subj %>%
  select(problems, comments) %>%
  kable()
```



