---
title             : "Generic statements have weak (and strong) implications"
shorttitle        : "Context-sensitive generic interpretations"

author: 
  - name          : "Michael Henry Tessler"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "450 Serra Mall, Bldg. 420, Rm. 316, Stanford, CA 94305"
    email         : "mhtessler@stanford.edu"
  - name          : "Noah D. Goodman"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Stanford University"
    
header-includes:
  - \usepackage{tabularx}
  - \usepackage{multicol}
  - \usepackage{wrapfig}
  - \usepackage{caption}
  - \usepackage{booktabs}
  - \usepackage{amsmath}
  - \usepackage{graphicx}
  - \usepackage{subcaption}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{xcolor}
  
author_note: >
  This manuscript is currently in prep. Comments or suggestions should be directed to MH Tessler.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["generics.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---
\newcommand{\denote}[1]{\mbox{ $[\![ #1 ]\!]$}}
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\definecolor{Red}{RGB}{255,0,0}
\definecolor{Green}{RGB}{10,200,100}
\definecolor{Blue}{RGB}{10,100,200}

\newcommand{\mht}[1]{{\textcolor{Blue}{[mht: #1]}}}
\newcommand{\ndg}[1]{{\textcolor{Green}{[ndg: #1]}}}
\newcommand{\red}[1]{{\textcolor{Red}{#1}}}


```{r load_packages, include = FALSE}
# install.packages(c("tidyverse", "cowplot", "ggthemes", "ggpirit", "viridis"))
# devtools::install_github("crsh/papaja")
library("papaja")
library(tidyverse)
library(cowplot)
library(ggthemes)
library(RColorBrewer)
library(ggpirate)
library(viridis)
library(brms)
theme_set(theme_few())
remove(list= ls())
```


```{r analysis_preferences}
# Seed for random number generation
set.seed(42)

knitr::opts_chunk$set(echo=FALSE, warning=FALSE, cache=T, message=FALSE, sanitize = T)
format_regression_effects <- function(brm_summary, fixed_effect_name, n_digits = 3){
   #print(fixed_effect_name)
   e1 <- brm_summary[["fixed"]][[fixed_effect_name, "Estimate"]]
   e_lower <- brm_summary[["fixed"]][[fixed_effect_name, "l-95% CI"]]
   e_upper <- brm_summary[["fixed"]][[fixed_effect_name, "u-95% CI"]]
   return(paste(
     format(e1, digits = n_digits), " [", 
     format(e_lower, digits = n_digits), ", ", 
     format(e_upper, digits = n_digits), "]", sep = ""))
}

compute_r2 <- function(df,v1, v2, sigfigs = 3){
  return(format(cor(df[[v1]], df[[v2]])^2, digits = sigfigs))
}

compute_mse <- function(df, v1, v2, sigfigs = 3){
  return(format(mean( (df[[v1]]-df[[v2]])^2), digits = sigfigs))
}


```

# Introduction


<!-- MH: Refer to the model as the "vague quantifier" or "vague threshold" account? Easier to discuss alternative models. -->

<!-- - is there a way to connect to the claims of Cimpian2009 about generics influencing feature-as-cause vs. feature-as-effect explanations? -->
  <!-- - perhaps not due to the generic vs. specific distiction, but to prior beliefs about the property? -->
  
<!-- - in generic endorsement: connect double generalizations ("Dogs bark") to so-called "non-generics" ("Dogs are on my front lawn"). Since "are on my front lawn" is a stative (?) property, there is only one generalizations about dogs which gets heavily restricted by the property? -->

<!-- Learning from others comes in many forms.  -->
<!-- An expert may tolerate onlookers, a demonstrator may slow down when completing a particularly challenging part of the task, and a teacher may actively provide pedagogical examples and describe them with language [@Kline2014; @Csibra2009].  -->
<!-- Informative demonstrations may be particularly useful for procedural learning (e.g., hunting seals, riding a bicycle).  -->

Much of what we learn about the world comes not from our own experience but by learning from others, often with language.
Using language, a teacher can go beyond direct experience, conveying information that is itself a generalization.
Generalizations about categories are conveyed using *generic language* [e.g., "Birds have hollow bones"; @Carlson1977], a clear case of abstract knowledge transmitted via language [@Gelman2009].
Generics are ubiquitous in everyday conversation and child-directed speech [@Gelman1998; @Gelman2008; @GelmanEtAl2004], and learning from generics is thought to be central to conceptual development [@Gelman2004; @Cimpian2009:explanations].
Understanding how beliefs are updated from generic language is thus an important question for cognitive science.

<!-- Generics provide information that is difficult to gain access to or dangerous to observe -->
<!-- Learning from language is uniquely powerful because language can convey abstract content that goes beyond direct experience. -->


<!-- that difficult to gain access to [e.g., birds have hollow bones] or dangerous to observe [e.g.,  certain plants are poisonous, staring at the sun causes blindness].  -->
<!-- The premier example of language's ability to transmit abstract knowledge comes in the form of statements that convey generalizations, otherwise known as *generic language*  -->
<!-- One of the most important roles for generic language is to provide learners with information about new or poorly understood categories. -->

<!-- But unlike statements about concrete events or exemplars  (e.g., "This bird flys"), generics convey information that is not directly observable and, in fact, resilient to counterexamples (e.g., penguins do not fly). -->
<!-- Here, we investigate how generic language is interpreted  -->

@Abelson1966 argued that generics, "...once accepted psychologically, [...] appear to be commonly taken in a rather strong sense, as though the qualifier *always* had implicitly crept into their interpretation" (p. 172).
Indeed, adults learning from generics about both familiar and novel animals (e.g., "Bears like to eat ants"; "Lorches have purple feathers") rate the *implied prevalence* of the feature (e.g., the percentage of bears that like to eat ants) as quite high [$\sim 85\%$; @Gelman2002; @Cimpian2010, Expt. 1]. 
The fact that generics seem to convey strong implications may explain why social stereotypes are propagated and maintained [@Rhodes2012].

Do all generics carry strong implications?
Philosophers and linguists have noted that statements like "Mosquitos carry malaria" seem only to have the quantificational force of an existential claim, meaning *some mosquitos carry malaria* or *mosquitos can carry malaria*.
@Cohen2004 argues for a panolply of conditions that give rise to existential interpretations (e.g., focus-sensitive additives, as in "Birds lay eggs. Mammals lay eggs too.").^[
 At least two mammals, Platypuses and echidnas, reproduce by laying eggs.
]
Some empirical evidence points to the existence of *weak generics*: @Cimpian2010 (Expt. 3) found lower implied prevalence from generics about features that could be construed as accidental [e.g., "Crullets have fungus-covered claws"; see also @Khemlani2009; @Khemlani2012 for evidence for weak inferences from generics].
In these previous studies, however, the actual implied prevalence from weak generics was still quite high [in @Cimpian2010 Expt. 3, mean implied prevalence $= 70\%$], leaving open the question of whether generics can receive genuinely weak interpretations (e.g., minority interpretations: $< 50\%$).

There are also open theoretical questions: property-specific generic interpretations (e.g., "Lorches have purple feathers" vs. "... fungus-covered claws") have been explained as differences in *theory-based expectations* [@Leslie2008; @Cimpian2010theory; @Prasada2013], but these notions have not been made sufficiently precise to provide a quantative, predictive account of how beliefs will be updated given a specific generic statement.
@TesslerLangGenUnderReview proposed a quantitative model of generic language as a kind of vague quantifier, combining tools from formal semantics and Bayesian modeling.
This model accounted for truth judgments or endorsements (e.g., is "Mosquitos carry malaria" true or false?) among a wide range of linguistic stimuli including generics about animals, habitual statements about actions (e.g., "John runs"), and causal sentences (e.g., "This herb makes animals sleepy").
Their endorsement model is cast as a speaker deciding whether or not to assert a generic statement to a listener, who updates their prior beliefs about the prevalence of the feature in the category from the generic statement.
The listener model used therein provides a mapping from a generic statement to implied prevalence---it is a quantitative account of how generics update beliefs.
This paper tests the predictions of this listener model directly.
In doing so, we also look for evidence for weak generics, which are predicted to exist and provide the strongest test of the uncertain threshold account. 

<!-- Interpreting a generic as *most* can also be too weak: "Triangles have three sides" is a statement about *all triangles*; if a shape does not have three sides, it is not a triangle.  -->
<!-- Indeed, the differences between quantified statements and generic statements are appreciated by children as young as three years [@Gelman2015genericsQuantifiers]. -->

<!-- Flexible interpretations of generic language may be in part attributed to beliefs about the property [@Nisbett1983]. -->
<!-- Properties that are biological in nature (e.g., "Wugs have wings") are interpreted as applying to most or all of the category [@Gelman2002; @Brandone2014], while features that could be construed as incidental (e.g., "Crullets have fungus-covered claws") are interpreted as applying to relatively fewer members of the category [@Cimpian2010]. -->

The paper is organized as follows.
First, we review @TesslerLangGenUnderReview's computational model of generic interpretation, describe alternative models, and overview our experimental and data analytic approach. 
In Expt. 1, we replicate and extend the findings of @Cimpian2010 that biological and accidental properties receive differential interpretations. 
In Expt. 2, we extend these findings using a larger and more diverse stimulus set better able to test the quantitative predictions of our model and explore the existence of weak generics.
In Expt. 3, we experimentally manipulate background knowledge and test the model-predicted effects on interpretations of novel generics.
In each experiment, we compare the uncertain threshold model's predictions to alternative models that have the same prior knowledge but which update their beliefs via different semantic mechanisms (e.g., fixed-thresholds); in each case, we find the vague threshold model is best able to account for property-specific generic interpretations. 
Together, these results provide strong evidence that generics update beliefs in a context-sensitive manner, well-modeled as a vague quantifier. 

<!-- First, we test whether or not weak interpretations of generics are possible by testing interpretations of generics about a wide range of properties (Expt. 1a).  -->
<!-- Then, we measure interlocutors' prior beliefs about the prevalence of the property (Expt. 1b) using the prior elicitation paradigm in @TesslerGenerics.  -->
<!-- We compare our interpretation model's predictions, which use the empirically measured priors, to the implied prevalence data and find that our model is able to predict, with high quantitative accuracy, the context-sensitive interpretations of generics.  -->
<!-- Finally, we show that, rather than being merely correlationa in nature, the prevalence prior is causally related to generic interpretation by manipulating the prevalence prior and measuring participants interpretaions of novel generics (Expt. 2).  -->


<!-- Despite these variable truth conditions, generic sentences are thought to have charasterically "strong implications" [@Gelman2002; @Cimpian2010; @Brandone2014]. -->
<!-- It is these strong interpretations that make generics lead to stereotypes [@Rhodes2012]. -->

<!-- We recently proposed that generics communicate in an underspecified way about the prevalence of the feature. -->
<!-- That is, our model predicted that "Mosquitos carry malaria" is a felicitious utterance because listeners expect *carrying malaria* to not be widespread within a category, even when it is present in some of the category.  -->

<!-- @Cimpian2010 too found that generics predicating biological properties of kinds carry strong interpretations.  -->
<!-- The properties used in those studies were all related to body parts of animals (e.g., "Lorches have purple feathers" $\rightarrow$ *almost all lorches have purple feathers*).  -->
<!-- Bare plural nouns predicated with *accidental* properties (e.g., "Lorches have broken legs") had significantly weaker interpretations in terms of how many of the kind were expected to have the property.  -->
<!-- However, these accidental properties do not lend themselves to generic interpretation and sound infelicitous.  -->
<!-- At the same time, the average implied prevalence for the *accidental property* generics was close to 70\%, leaving open the question as to whether or not generics can have truly weak (i.e., minority-based) interpretations. -->


# Computational model

Generic language conveys generalizations about categories [@Carlson1977; @Leslie2008].
Human generalization from observational data can be well described using the language of probability [@Shepard1987; @Tenenbaum2011], and so it makes sense that probability would be at the core of the meaning of generalizations conveyed in language. 
@TesslerLangGenUnderReview formalize such a hypothesis, positing that the semantics of generics are concerned with probability but in an underspecified, context-dependent manner.

Using the truth-functional tools of formal semantics [@Montague1973], the literal meaning of a generic statement can be modeled as a threshold function operating on the prevalence $r$ of the feature in the category (e.g., the proportion of mosquitos that carry malaria): $\denote{generic} = \{r > \theta\}$.^[
  The prevalence $r$ can be thought as a "prevalence in the mind", or a subjective degree of belief about the property in the category, which may not accurately track the empirical frequency.
]
The literal meaning of quantifiers can also be described by threshold functions (e.g., $\denote{some} = \{r > 0\}$, $\denote{most} = \{r > 0.5\}$, $\denote{all} = \{r = 1\}$).
@TesslerLangGenUnderReview posit that the corresponding threshold for the generic $\theta$ is *a priori* uncertain---formally, it is drawn from a context-invariant, uniform prior distribution on thresholds $P(\theta)$---and is resolved by context.
Of course, different threshold distributions could be learned over time for different properties.
The choice of a uniform distribution here is to explore how well context-sensitive generic interpretations  can be modeled by differences in corresponding prior beliefs about properties, without having to posit semantic differences between different generic sentences.

In order for a statement to update beliefs about prevalence in a given category, a listener must have prior beliefs about prevalence abstracted across categories.
To interpret a generic sentence, a listener draws upon her abstract knowledge about properties, formalized by a prior distribution over likely prevalence levels $P(r)$.
Though not the direct focus of this work, the prevalence prior distribution can be seen as a relatively minimal formalization of theory-based expectations. 
Different theory-based relationships between kinds and properties will give rise to different prior distributions over prevalence. 
The prevalence prior, thus, acts as a statistical layer between conceptual knowledge and natural language semantics. 
  
Thus the quantitative model for generic interpretation is given by:

\begin{eqnarray}
L(r, \theta \mid u) &\propto& {\delta_{\denote{u}(r, \theta)} \cdot P(r) \cdot P(\theta)} \label{eq:L0}
\end{eqnarray}

Formally, the truth-functional meaning is represented by the Kronecker delta function  $\delta_{\denote{u}(r, \theta)}$ that returns $1$ when the utterance is true (i.e., when $r > \theta$) and $0$ otherwise.

\begin{eqnarray}
\delta_{\denote{u_{gen}}(r, \theta)} &\propto  & \begin{cases}
1 & \text{if } r > \theta \\
0 & \text{otherwise}
\end{cases}\label{eq:delta}
\end{eqnarray}

The interpretation model computes a posterior distribution on prevalence by considering different possible thresholds $\theta$.
Given a particular value of $\theta$, the literal semantics rules out all prevalences $r$ below $\theta$.
Consider the model behavior when the prevalence prior is a uniform distribution---$P(r) = \text{Uniform}(0, 1)$ (Figure\ \@ref(fig:modelSimulations)A; top).
Given a particular value of $\theta$, the posterior on prevalence will be uniform over all prevalence levels above $\theta$ (Figure\ \@ref(fig:modelSimulations)B; top row);
thus, higher prevalence levels $r$ are consistent with more thresholds $\theta$.
Therefore, given a uniform prevalence prior, the generic interpretation model returns a non-uniform posterior that favors higher prevalence levels (Figure\ \@ref(fig:modelSimulations)B; top row, right-most column).
<!-- , which has uncertainty over the threshold and marginalizes over different possible thresholds,  -->
This behavior captures the intuition that, without strong background knowledge, generics probably imply that most or all of the category has the property.


## The influence and structure of prevalence priors

The generic interpretation model balances the prior probability of different prevalence levels $r$ with the overall preference for higher prevalence levels because they are consistent with more thresholds $\theta$ (as described above).
This updating mechanism results in interpretations that strongly depend on the prevalence prior $P(r)$.
The prevalence prior for familiar properties may display interesting structure reflecting domain-specific beliefs about the property.
Figure\ \@ref(fig:modelSimulations)A shows hypothetical prevalence priors for the features *fly* and *carry malaria* as well as an abstract property *Y* without structured background knowledge. 

Interpretations from the uncertain threshold model (Figure\ \@ref(fig:modelSimulations)B, right-most column) are similar to different quantified statements for different properties in question.
For the biological property prior, a generic ("Xs fly") is interpreted most similarly to "Most Xs fly".
This results from the prior distribution over a biological property like *fly* being bimodal with modes near 0\% and 100\%, reflecting the idea that for an arbitrary category, it is likely that 0\% of them fly (e.g., dogs, rabbits, etc...); however, among categories with at least some members who fly, we would expect all or nearly all of them to fly (hence, the second mode near 100\%).
For the accidental property prior, "Xs carry malaria" is most similar to "Some Xs carry malaria" because the property is expected to be rare both within- and across-categories.
If a listener knows the existence of the property depends upon the sex of the creature (e.g., *lays eggs*), the prevalence interpretation from a generic ("Xs lay eggs") should be roughly that 50% of the m lay eggs (only the females).
<!-- Similar to the *fly* prevalence prior, the prior distribution over prevalence for a property like *carry malaria* has substantial probability mass at or near 0\%, since most categories do not have the property present at all; however, among categories with at least a few members who carry malaria, it is very unlikely that all or even many carry malaria; the second mode of this prior distribution is near 10\%.  -->

<!-- We test these property-sensitive interpretations in the following experiments.  -->
<!-- Different interpretations for this model come from different prior distributions over prevalence $P(r)$, which -->

In this way, the prevalence prior can be viewed as a distribution over different categories (and their associated prevalence of the feature).
In a more abstract sense, this distribution can reflect causal beliefs about kinds and properties (e.g., there is something internal or external to the entity which causes it to have the property); if such a causal mechanism is believed to exist for some kinds and not others, we would expect the prevalence prior distribution to follow a mixture distribution (e.g., a mixture of Beta distributions as is shown for the *fly*, *lay eggs*, and *carry malaria* cases above). ^[
  This assumption is similar in spirit to that employed by *Hurdle Models* of epidemiological data, where the observed count of zeros is often substantially greater than one would expect from standard models, such as the Poisson [e.g., when modeling adverse reactions to vaccines; @hurdleModels]
]
Such a structured prior distribution could vary by the mixture component (e.g., for how many different kinds does the mechanism exist?) as well as for the parameters of the component(s) that govern the prevalence for the kinds with the mechanism (i.e., given that there is such a mechanism, how strong do we expect that mechanism to be?).
In Experiment 1, we assume this mixture-distribution structure to the prevalence prior in order to measure beliefs about relatively obscure properties.
In Experiment 2, we measure the prevalence prior for more familiar properties in a nonparametric way, and empirically verify that the mixture of Beta distributions fits reasonably well.
Finally, in Experiment 3, we directly manipulate the prevalence prior.


<!-- which can be thought of as levels of prevalence given different categories within a comparison class. -->
<!-- For simplicity, we assume the comparison class relevant for interpreting generics about novel animal categories is *other animals*. -->

<!-- \ndg{i think we should have a little (sub)section here on the structure of the prevalence priors. since one of the main things that changes between the three experiments is the prior elicitation / manipulation, we want to set the stage. so we could talk a bit about how different causal mechanisms would give rise to different mixture components and how a beta-mixture model should be a good approximation to that. then maybe set the stage saying in the first expt we assume this and design elicitation accordingly, in the second expt we measure the prevalence prior in a more direct (non parametric) way and show that a beta-mixture fits reasonably, in the third experiment we directly manipulate the prior.} -->

\ndg{note: i changed "context" to other things (eg "property") in a bunch of places because what we're talking about is differences in target property and it's corresponding background knowledge. this is context in some sense, but i worry it would confuse people with more pragmatic / situated notions of context.}
\mht{wonder if we should make those changes more widespread (e.g., the running-head) or have an explicit statement about the kind of context we are considering here...}

## Alternative models and Bayesian data-analytic strategy

The uncertain threshold generic interpretation model presented here and in @TesslerLangGenUnderReview is the first cognitive model to make quantitative predictions about human interpretations of generic statements.
In order to assess the predictive capabilities of this model, we construct a number of alternatives for comparison.
Foremost, we compare the uncertain threshold model to a model that does not update beliefs and predicts prevalence ratings according to the prior distribution $P(r)$. 
This comparison informs us as to whether or not participants actually *update* their beliefs based on the generic statement.
In addition, we construct two alternatives models by removing the model's uncertainty about the threshold, roughly corresponding to models of quantifier interpretation.^[
  Note that a more accurate model of quantifier interpretation would include their pragmatic interpretations (e.g., that "some" often implies "not all"). Such a model can be implemented in the same probabilistic modeling framework [@Goodman2013] but does not directly address our question of what threshold best corresponds to a model of generic interpretation.
]
The first is a model of the quantifier "some" which rules out the lowest possible prevalence level:

\begin{eqnarray}
L_{some}(r \mid u) &\propto&  P(r \mid r > 0)  \label{eq:someModel}
\end{eqnarray}

The second is analogous to "most", with a threshold at 50% prevalence:

\begin{eqnarray}
L_{most}(r \mid u) &\propto&  P(r \mid r > 0.5)  \label{eq:mostModel}
\end{eqnarray}

A model that assumes a fixed threshold at 50% is a very restricted model; it places zero probability on any response less than 50%. 
In case there are ratings in the experimental data sets that are less than 50%, we must supplement the "most" model with an extrinsic noise process in order for this model to actually generate predictions for those data; that is, with some probability, participants respond at random.
We infer this noise probability parameter for the "most" model from the data.

Our primary analyses ask how well the various interpretation models accomodate the human generic interpretation data given our corresponding measurements of the prevalence priors.
To fit these models, we build Bayesian data analysis (BDA) models to jointly predict the prevalence prior data and the generic interpretation data.
Such a joint-inference model allows us to retain the uncertainty in the measurements of the prevalence prior data when using it in our generics model to predict the generic interpretation results.

<!-- \ndg{see comments below that we should have brief discussions of joint BDA analysis strategy and of alternative models up here, to avoid duplication and make the expt sections smoother.} -->

<!-- Considering different fixed-thresholds in conjunction with structured background knowledge also illuminates the unique behavior of the uncertain threshold model. -->

<!-- The literal interpretation of the quantifier "some" (threshold = 0.01) rules out only the lowest prevalence levels, returning an intuitively compelling interpretation for "Xs carry malaria" (*very few Xs carry malaria*); however, even given strong prior knowledge about the distribution of the property *fly*, "Some Xs fly" leaves open the possibility that very few Xs fly -->

<!-- A threshold that is slightly higher (threshold = 0.33; "more than a third"), when coupled with strong prior knowledge (e.g., for "Xs fly") can give  -->
<!-- The quantifier "most" would correspond to a threshold at 0.5, which like "more than a third", can result in intuitive interpretations for "Xs fly" (the posterior over prevalence suggests *almost all Xs fly*); -->

<!-- Different prevalence priors give rise to different interpretations. -->
<!-- Figure\ \@ref(fig:modelSimulations)B shows different interpretations (posterior distributions over prevalence) given different fixed thresholds (corresponding to different quantifiers) as well as the uncertain threshold, corresponding to the generic. -->

<!-- The interpretation model computes a posterior distribution on prevalence by considering different possible thresholds $\theta$. -->
<!-- Figure\ \@ref(fig:modelSimulations)B (top-row) shows what the model would believe given different thresholds (columns). -->
<!-- If the threshold were to be very high (e.g., $\theta = 0.75$), only the highest prevalence levels would be consistent with the utterance. -->
<!-- As the threshold decreases, more and more prevalence levels would be true. -->
<!-- Roughly speaking, the uncertain-threshold interpretation model averages over these possibilities, resulting in a posterior distribution that favors higher prevalence levels because they are consistent with more thresholds. -->
<!-- The endorsement model inverts the interpretation model and predicts higher rates of endorsement as the speaker's belief about the prevalence (referent-prevalence) increases. -->


```{r modelSimulations, fig.width = 10, fig.asp = 0.6, fig.cap="Model simulations. A: Prevalence priors reflect knowledge about properties. An abstract property could be given a uniform distribution, while familiar properties display more complex structure. B: Posterior distributions over prevalence (interpretations) given different fixed-threshold quantifiers and the uncertain threshold generic."}
load(file = "cached_results/modelSims-priors_fixedT_uncertainT.RData")
get.colors <- function(pal) brewer.pal(brewer.pal.info[pal, "maxcolors"], pal)
spectrum.color.palette <- get.colors("Blues")


fig.sims.priors <- ggplot(sims.combined %>%
         filter(
           PriorShape %in% c("uniform", "biological_rare", "sexed_rare","accidental_rare"),
           src %in% c("priors")
           ) %>%
         mutate(PriorShape = factor(PriorShape, levels = c("uniform", "biological_rare",  "sexed_rare","accidental_rare"),
                                    labels = c("Xs Y (uniform)", "Xs fly (biological)", 
                                               "Xs lay eggs (sexed)", 
                                               "Xs carry malaria (accidental)")),
                src = factor(src, levels = c( "priors"),
                             labels = c(
                               '\n prevalence prior'
                                        ))), 
       aes(x = state))+
    geom_density(aes(y = ..scaled..), fill= 'black', size = 0.6, alpha = 0.7, adjust = 1.1)+
    theme_few() +
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    ylab("Probability density (scaled)") +
    xlab("Prior Prevalence")+
    scale_color_solarized()+
    scale_fill_solarized()+
    facet_grid(PriorShape~src, scales = 'free')+
    theme(strip.text.y = element_blank(),
          legend.position = "none"
          )


fig.sims.distributions <- ggplot(sims.combined %>%
         filter(
           PriorShape %in% c("uniform", "biological_rare","sexed_rare", "accidental_rare"),
           src %in% c("fixed_0.1", "fixed_0.33", "fixed_0.5", "posteriors")
           ) %>%
         mutate(PriorShape = factor(PriorShape, levels = c("uniform", "biological_rare", "sexed_rare", "accidental_rare"),
                                    labels = c("Xs Y\n[uniform]", "Xs fly\n[biological]",
                                               "Xs lay eggs\n[sexed]", "Xs carry malaria \n [accidental]")),
                src = factor(src, levels = c( "fixed_0.1", "fixed_0.33",
                                              "fixed_0.5", "posteriors"),
                             labels = c(
                           #    'prevalence prior',
                               '"some"\n(threshold = 0.01)',
                               '"more than a third"\n(threshold = 0.33)',
                              '"most"\n(threshold = 0.5)',
                               'generic\n(uncertain threshold)'
                                        ))), 
       aes(x = state, fill = src, color = src))+
    geom_density(aes(y = ..scaled..), 
                 color ='black', size = 0.6, alpha = 0.7, adjust = 1.1)+
    theme_few() +
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    ylab("Scaled posterior density") +
    xlab("Implied Prevalence")+
    # scale_fill_brewer(palette=2, type = "seq", direction = -1)+
    # scale_color_brewer(palette=2, type = "seq", direction = -1)+
    scale_color_manual( values =  c(spectrum.color.palette[c(8,5,2)], "#238b45"))+
    scale_fill_manual( values = c(spectrum.color.palette[c(8,5,2)], "#238b45") )+
    facet_grid(PriorShape~src, scales = 'free')+
    theme(strip.text.y = element_text(angle = 0, size = 12),
          legend.position = "none",
          axis.title.y = element_blank())

sims.combined.summary <- sims.combined %>%
         filter(
           PriorShape %in% c("uniform","biological_rare", "accidental_rare"),
           src %in% c("fixed_0.1", "fixed_0.5", "posteriors")
           ) %>%
         mutate(PriorShape = factor(PriorShape, 
                                    levels = c( "accidental_rare", "biological_rare","sexed_rare", "uniform"),
                                    labels = c("uniform", "Xs carry malaria\n[accidental]", 
                                               "Xs lay eggs\n[sexed]",
                                               "Xs fly\n[biological]")),
                src = factor(src, 
                             levels = c( 
                               "fixed_0.1", "fixed_0.5", "posteriors"),
                             labels = c(
                               '"some" (threshold = 0.01)',
                              '"most" (threshold = 0.5)',
                               'generic (uncertain threshold)'
                                        ))) %>%
    group_by(PriorShape, src) %>%
    summarize(expval = mean(state))
  
  
fig.sims.bars <- ggplot(sims.combined.summary %>% mutate(blank = '\n'), 
       aes(x = PriorShape, y = expval, fill = src))+
    geom_col(color = 'black', 
             position = position_dodge(), alpha = 0.8, width = 0.5)+
    theme_few() +
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    ylab("Average\nimplied prevalence")+
    scale_color_manual( values = spectrum.color.palette )+
    scale_fill_manual( values = spectrum.color.palette )+
    #scale_color_solarized()+
    #scale_fill_solarized()+
    facet_wrap(~blank)+
    coord_flip()+
    guides(fill = F)+
    theme(axis.title.y = element_blank(),
          axis.text.y = element_blank())

cowplot::plot_grid(
  fig.sims.priors + theme(plot.margin = unit(c(6, 3, 6, 0), "pt")), 
  fig.sims.distributions + theme(plot.margin = unit(c(6, 0, 6, 0), "pt")),
  #fig.sims.bars+ theme(plot.margin = unit(c(6, 0, 0, 0), "pt")),
  nrow = 1,
  labels = c("A", "B"),
  rel_widths = c(0.25, 1)
)
```

<!-- 
- Figure:
  - 3 schematic priors, different fixed thresholds, generic interpretation 
  - possibly with bar plot summarizing means
  
- Figure:
  - comparison to a fixed threshold ("some") model, fixed threshold ("most") model, and L1 model (?)
-->

# Experiment 1: Replication and extension of Cimpian et al. (2010)

Our model of generic interpretation (Eq. \ref{eq:L0}) predicts that the interpretations of generics in terms of prevalence should vary as a function of the prevalence prior.
@Cimpian2010 found a difference in the implied prevalence between biological properties (e.g., *yellow fur*) and accidental properties (e.g., *fungus-covered claws*).
Classic work in generalization suggests beliefs about the prevalence of properties include relatively fine distinctions among properties that are all biological in nature [@Nisbett1983].
For this reason, we elaborated the stimulus set from @Cimpian2010 to include three types of biological properties: body parts (e.g., *fur*), body parts of a particular color (e.g., *yellow fur*) and body parts described with a vague adjective (e.g., *curly fur*). 
Here, we empirically measure the prevalence priors for these properties using a structured prior elicitation task (Expt. 1a) and use our interpretation model to predict the prevalence implied by a generic statement about a novel category (e.g., "Wugs have yellow fur"; Expt. 1b). 

<!-- %We also coded the accidental properties from Expt.~2a as either ``common'' or ``rare'' using a by-item median split based on \emph{a priori} expected prevalence when present. -->
<!-- %Most of the materials we used were from \citeauthor{Cimpian2010}.  -->
<!-- %The materials used were 30 novel animal categories (e.g. lorches, morseths, blins) each paired with a unique property.  -->
<!-- %Biological properties were made by pairing a color with a body-part (e.g. purple feathers, orange tails).  -->
<!-- %Accidental properties used the same set of body-parts but modified it with an adjective describing an accidental or disease state (e.g. broken legs, wet fur).  -->
<!-- %Each participant saw a random subset of 10 unique animal-property pairs for each type of property (biological and accidental).  -->


## Experiment 1a: Prior elicitation

This experiment measures the prevalence prior $P(r)$ in Eq. \ref{eq:L0} using a structured, prior elicitation procedure.

### Method

#### Participants

We recruited 40 participants over Amazon's crowd-sourcing platform Mechanical Turk (MTurk). We chose this number of participants based on intuition from similar experiments which were designed primarily to test a quantitative model.
Participants were restricted to those with US IP addresses and with at least a 95\% MTurk work approval rating. 
All participants were native English speakers. 
The experiment took about 5-7 minutes and participants were compensated \$0.75.

#### Procedure and materials

We constructed a stimulus set of forty different properties to explore a wide range of *a priori* beliefs about prevalence. 
These items make up four categories of properties: body parts (e.g., *fur*), body parts of a particular color (e.g., *yellow fur*), body parts described with a vague adjective (e.g., *curly fur*), and body parts with in an accidental or disease state (e.g., *wet fur*).
Because pilot testing revealed more variability for items in the accidental category relative to the other types of properties, we used twice as many exemplars of accidental properties, yielding a more thorough test of the quantitative predictive power of the generic interpretation model. 
We used eight exemplars of each of the three non-accidental properties (parts, colored parts, vague parts), and sixteen exemplars of accidental properties, building on a stimulus set from @Cimpian2010.
<!-- \ndg{list properties and other materials in appendix or supplement?} -->
List of properties is shown in Table 1 of the Appendix.

Direct elicitation of background knowledge about the properties used in @Cimpian2010 (e.g., by asking about prevalence in familiar categories) is difficult because many of the properties are fantastical or obscure (e.g., pink teeth, silver legs, fungus-covered fur) leading to a large component of the distribution at zero prevalence.
Therefore, we assume a mixture distribution structure and create an elicitation task to measure two aspects of the prior: (1) the relative contribution of zero-prevalence distribution (e.g., for how many categories is the property expected to be present at all) and (2) the prevalence among kinds where the property is present (*prevalence when present*). 

Participants were first introduced to a "data-collection robot" that was tasked with learning about properties of animals. 
Participants were told the robot randomly selected an animal from its memory to ask the participant about (e.g., The robot says: "We recently discovered animals called feps."). 
To measure the relative contribution of the zero-prevalence distribution, the robot asked how likely it was that there *was a fep with property* (e.g., "How likely is it that there is a fep that has wings?"), to which participants reported on a scale from *unlikely* to *likely*.
To measure *prevalence when present*, the robot then asked the likely prevalence assuming that at least one has the property (e.g., "Suppose there is a fep that has wings. What percentage of feps do you think have wings?"). 
Participants completed a practice trial using the property *are female* to make sure they understood the meanings of these two questions.
For example, it is very likely that there is a fep that is female because almost all animals have female members (high $P(\text{feature is present})$).
Additionally, when present, the property is only expected in about 50\% of the category.


<!-- In previous work, we have found that prevalence priors are well-modeled by a mixture of two Beta distributions. ^[ -->
<!--   The Beta distribution is chosen because the support of this distribution is numerical values between 0 - 1, which is the appropriate support for a distribution over prevalence. -->
<!-- ] -->
<!-- One of these distributions represents kinds of animals who *do not have* a stable causal mechanism that could give rise to the property (e.g., *lions* do not have a stable mechanism by which they could *lay eggs*), which results in prevalence levels close to or equal to 0. -->
<!-- This "null distribution" is potentially present for all features in exactly the same way (i.e., the lack of producing the feature). -->
<!-- The second distribution represents kinds of animals who *do have* such a mechanism; we cannot specify the parameters of this second distribution *a priori* as they are likely different for different properties. -->
<!-- Finally, the relative contribution of these two component distributions can also not be specified *a priori*.  -->
<!-- \ndg{i feel like this part comes off as kind of complex and ad-hoc. how about waiting until next subsection to talk about betas, and here saying direct ellicitation is hard because there is generally a big component near zero, due to categories that lack any causal mechanism, so we to elicitation in two steps....} -->


### Data analysis and results

Question 1 elicits the mixture parameter of a 2-distribution mixture model ($P(\text{feature is present})$). 
Question 2 elicits the prevalence in a kind where the property is present.
These elicited parameters of the priors display a range of possible values Figure\ \@ref(fig:cimpian-prevPrior)A.
<!-- Figure \ref{fig:prior2}a shows a summary of the elicited priors, in terms of the diversity of $d_{potential}$ and $d_{expected}$. -->
Biological properties are likely to be present and when present, are likely to be widespread (top right corner of scatter plot).
More specific properties (either using gradable adjectives or color adjectives) are expected to be slightly less prevalent among the kinds where the property is present, perhaps reflecting the fact that the same kind of animal can come in many different colors or that gradable properties (e.g., *big claws*) might not be ubiquitous in a category.
Finally, accidental properties are as likely to be present in a category as the color or gradable properties (same $P(\text{feature is present})$), but are not expected to be widespread even when present in the category (low *prevalence when present*).

From these two elicitation questions, we can reconstruct what the prevalence priors should look like. 
We assume that kinds for which the property is absent have prevalence levels sampled from a Beta distribution that heavily favors numbers close to 0: $\text{Beta}(\gamma = 0.01; \xi = 100)$.^[
  Note that we use the noncanonical mean $\gamma$ and concentration $\xi$ (or, inverse-variance) parameterization of the Beta distribution rather than the canonical shape (or pseudocount) parameterization for ease of posterior inference. The shape parameterization can be recovered using: $\alpha = \gamma \cdot \xi; \beta = (1 - \gamma) \cdot \xi$.
]
With that assumption, the prevalence distribution is given by:^[
All modeling results hold when this null distribution is assumed to be even more left-skewed $\text{Beta}(\gamma = 0.001; \xi = 1000)$ or just a delta-function at zero $\delta_{p=0}$.
]

\begin{align}
\phi & \sim \text{Beta}(\gamma_1, \xi_1) \nonumber \\ 
r & \sim \begin{cases}
		\text{Beta}(\gamma_2, \xi_2) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{T} \label{eq:priorModel}  \\
		\text{Beta}(\gamma = 0.01; \xi = 100) &\mbox{if } \text{Bernoulli}(\phi) = \textsc{F} \\
		\end{cases}
\end{align}

For data analysis, we assume participants' responses to both questions ($i \in \{\text{Question 1}, \text{Question 2}\}$) are generated from Beta distributions: $d_{i} \sim \text{Beta}(\gamma_i, \xi_i)$, and put uninformative priors over the parameters of each: $\gamma_i \sim \text{Uniform}(0, 1); \xi_i \sim \text{Uniform}(0, 100)$. 
We implemented this Bayesian mixture-model in the probabilistic programming language WebPPL [@dippl].
To learn about the credible values of the parameters of the model, we ran MCMC on each item independently for 100,000 iterations, discarding the first 50,000 for burn-in.

<!-- This mixture model specifies the correct way to combine our two prior-elicitation questions. -->
Figure\ \@ref(fig:cimpian-prevPrior)B shows example reconstructed priors.
Biological properties (*biological*, *vague*, and *color* body parts) have prevalence distributions that are bimodal with peaks at 0\% and near-100\% prevalence, but differ in their variance around the 100\%-mode. 
By contrast, accidental properties do not have a substantial second mode.
This variability in prevalence priors leads the generic interpretation model to predict different prevalence levels implied by the generic.

<!-- predicting weaker and more variable interpretations of novel generics for these properties.  -->
<!-- \mht{will you plot prevalence posteriors as well? probably...} -->
<!-- Interpretations of generics about these properties ($L$ model, Eq. \ref{eq:L0}) update these distributions to concave posteriors peaked at 100\% (Figure \ref{fig:prior2}a; red, blue and green insets); the model predicts these novel generics will be interpreted as implying the property is widespread in the category. -->




<!-- To construct prevalence prior distributions, we built a Bayesian mixture-model for this prior elicitation task. -->


```{r cimpian-prevPrior, fig.width = 9, fig.asp = 0.4, fig.cap="Prevalence priors for items from Cimpian et al. (2010). A: Latent parameters governing prevalence priors are different for different kinds of properties. B: The diversity in parameters gives rise to different underlying distributions over prevalence, which the generic interpretation model uses to make predictions."}
load("cached_results/cimpian-prevPrior-interpretations.Rdata")
# m.rs.priors.reconstructed.subset,
     # df.c.prior.bs.wide, 
     # df.c.int.bs,

fig.prevPriors <- m.rs.priors.reconstructed.subset %>%
  mutate(stim_type = as.character(stim_type),
         stim_type_fixed = ifelse(stim_type == "color adj + part", "gradable adj + part",
                                  ifelse(stim_type == "gradable adj + part", "color adj + part",stim_type)),
         stim_type_fixed = factor(stim_type_fixed,
                                         levels = c("body part",
                                                    "gradable adj + part",
                                                    "color adj + part",
                                                    "accidental"))) %>%  
  ggplot(., 
       aes( x = prevalence,
                                    fill = stim_type_fixed))+
    stat_density ( aes(y = ..scaled.. ), color = 'black')+
    facet_wrap(~property, nrow = 2)+
    scale_x_continuous(limits = c(-0.01,1.01), breaks = c(0, 1)) +
    scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 1)) +
    theme(strip.text.y = element_text(angle = 0))+   guides(fill=guide_legend(title="Property type"))+
  ylab("Probability density (scaled)")+
  xlab("Prevalence")

fig.prevParams <- ggplot(df.c.prior.bs.wide %>%
         mutate("Property type" = factor(stim_type,
                                         levels = c("part",
                                                    "vague",
                                                    "color",
                                                    "accidental"),
                                         labels = c("body part",
                                                    "gradable adj + part",
                                                    "color adj + part",
                                                    "accidental"))), 
       aes( x = mixture_mean, xmin = mixture_lower, xmax = mixture_upper,
            y = pwp_mean, ymin = pwp_lower, ymax = pwp_upper,
            fill = `Property type`))+
  geom_errorbar(alpha = 0.3) + geom_errorbarh(alpha = 0.3) + 
  geom_point(shape = 21, size = 2.6, color = 'black')+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  ylab("Prevalence when present")+
  xlab("P(feature is present)")



cowplot::plot_grid( 
  cowplot::plot_grid(
    fig.prevParams + theme(plot.margin = unit(c(6, 6, 0, 0), "pt"),
                           legend.position = 'none'),
    fig.prevPriors + theme(plot.margin = unit(c(6, 0, 0, 0), "pt"),
                           legend.position = 'none'), 
    nrow = 1,
    labels = c("A", "B"),
    rel_widths = c(0.33, 0.66)
  ), 
  cowplot::get_legend(
    fig.prevPriors + theme(
      legend.position="bottom"
      #legend.text = element_text(size = 16),
      #legend.title = element_text(size = 16)
                           )
    ), ncol = 1, rel_heights = c(1, .2))
```




<!-- In addition to specifying the correct way to combine our two prior-elicitation questions, using this inferred prior resolves two technical difficulties. -->
<!-- First, it smooths effects that are clearly results of the response format.  -->
<!-- For example, a very common rating for certain events is \emph{1 time per year}. -->
<!-- Presumably participants would be just as happy reporting \emph{approximately} 1 time per year (e.g., on average, 1.2 times per year); the raw data does not reflect this due to demands of the dependent measure. -->
<!-- Second, this methodology better captures the tails of the prior distribution (i.e., very frequent or very infrequent rates) which have relatively little data and need to be regularized by the analysis. -->



<!-- We used the same structured, statistical model for the prior data from Expt.~1. -->
<!-- The only difference from Expt.~1a. is that our experimental data comes from inquiring about the parameters of the priors directly, as opposed to asking about particular samples from the prior (i.e. particular kinds) as was done in Expt.~1a.  -->
<!-- <!-- %For Expt.~2a, participants are asked questions directly targeting $\theta$ and $\gamma$ in the above model (see {\it Expt. 2a}). -->
<!-- We assume these two measurements follow Beta distributions ($d_{potential} \sim \text{Beta}(\gamma_{1}, \xi_{1})$; $ -->
<!-- d_{expected} \sim \text{Beta}(\gamma_{2}, \xi_{2})$), and construct single prevalence distributions, $P(x)$, by sampling from the posterior predictive distribution of prevalence as we did before: $P(x) = \int [ \phi\cdot \text{Beta} (x \mid \gamma_{2}, \xi_{2}) + (1 -  \phi) \cdot \delta_{x=0} ] \cdot \text{Beta}(\phi \mid \gamma_{1}, \xi_{1}) d\phi$. -->
<!-- We used the same uninformative priors over parameters $\phi, \gamma_{i}, \xi_{i}$ as in Expt.~1a. -->


<!-- %These convex posteriors show that generics about accidental or temporary properties come with highly uncertain interpretations, plausibly as a consequence of theory-driven considerations \cite{Cimpian2010c}.  -->




## Experiment 1b: Generic interpretation

This experiment measures the prevalence implied by a generic statement about a novel category, which we then compare to the predictions of the generic interpretation model $L(p \mid u)$ (Eq. \ref{eq:L0}).

<!-- %The full cover story is described in {\it SI Section C} and is the same for Expt.~2c. -->

### Method

#### Participants

We recruited 40 participants over MTurk. 
The experimental design is very similar to @Cimpian2010, and we chose to have a sample size at least twice as large as the original study (original n=15). 
This is a quantitative experiment with only quantitative comparisons planned.
All participants were native English speakers. 
The experiment took about 5 minutes and participants were compensated \$0.60.

#### Procedure and materials

In order to get participants motivated to reason about novel kinds, they were told they were the resident zoologist of a team of scientists on a recently discovered island with many unknown animals; their task was to provide their expert opinion on questions about these animals.
Participants were supplied with a generic about a novel category (e.g., "Feps have yellow fur.") and asked to judge prevalence: "What percentage of feps do you think have yellow fur?" 
Participants completed in randomized order 25 trials: 5 for each of the biological properties and 10 for the accidental.
The experiment in full can be viewed at \url{http://stanford.edu/~mtessler/generics/experiments/asymmetry/asymmetry-2.html}. 

### Results

```{r cimpian regression}
load("cached_results/cimpian_interpretation_brms_prevPrior.RData")
brm.c.int.prior_mean.summary <- summary(brm.c.int.prior_mean)
```


<!-- We look at the posterior predictive distribution of the generic interpretation model $L$. -->
Figure\ \@ref(fig:cimpian-modelingResults) shows the prevalence implied by the forty novel generic sentences in the experiment. 
We find a gradient of interpretation, mostly clustered by the type of property. 
We first explore a qualitative trend predicted by the interpretation model, before proceeding to a quantitative model analysis.
Prevalence implied by a generic is predicted to vary according to the prevalence prior, which we can summarize by its mean.
We ran a Bayesian mixed-effects beta regression model with fixed-effects of intercept and slope (scaled prior mean) with random by-participant effects of intercept and slope.
There is a clear positive relationship between the prevalence prior mean and the implied prevalence ($\beta_{\text{prev prior mean}}=$ `r format_regression_effects(brm.c.int.prior_mean.summary, "scaled_prior_mean")`).

## Model-based analysis and results

```{r cimpian-modelingResults, fig.width = 10, fig.asp = 0.57, fig.cap="Implied prevalence data and model predictions for items from Cimpian et al. (2010). A: Mean implied prevalence ratings for forty stimuli. B: Implied prevalence and generics model prections collapsed across property type. C: Posterior predictive model fits for quantitative models based on (i) the mean of the prevalence prior, (ii) a threshold semantics fixed at 0.01 (\"some\"), (iii) a threshold semantics fixed at 0.5 (\"most\"), and (iv) an uncertain threshold semantics (generic). Error bars denote bootstrapped 95% confidence intervals for the behavioral data and 95% highest posterior density intervals for the model predictions."}

load(file = "cached_results/cimpian-modelFits-interpretations.RData")
load(file = "cached_results/cimpian-interpretations-95ci.RData")



fig.cimpian.interpretation.95ci <- df.c.int.bs %>%
  ungroup() %>%
  mutate(stim_property = factor(stim_property, 
                           levels =  with(df.c.int.bs, stim_property[order(-mean)])),
         stim_type = ifelse(stim_type == "disease", "accidental", stim_type),
          "Property type" = factor(stim_type,
                                         levels = c("part",
                                                    "vague",
                                                    "color",
                                                    "accidental"),
                                         labels = c("body part",
                                                    "color adj + part",
                                                    "gradable adj + part",
                                                    "accidental"))) %>%
  ggplot(., aes( x = stim_property, y = mean, ymin = ci_lower, ymax = ci_upper, 
                 fill = `Property type`))+
  geom_col(position = position_dodge(), color = 'black')+
  geom_errorbar(position = position_dodge(), alpha = 0.3)+
  #geom_pirate(bars = F, violins = F, width_points = 0.2)+
  #coord_flip()+
  #scale_color_viridis(discrete = T)+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        axis.title.x = element_blank())+
  ylab("Implied prevalence")


fig.cimpian.interpretation.stimtype <- md.impprev.type %>%
  mutate("Property type" = factor(stim_type,
                                         levels = c("part",
                                                    "vague",
                                                    "color",
                                                    "accidental"),
                                         labels = c("body part",
                                                    "color adj + part",
                                                    "gradable adj + part",
                                                    "accidental")),
         src  = factor(src, levels = c("data","model"),
                       labels = c("data", "generics model"))) %>%
  ggplot(., aes( x = src,
                        y = mean, ymin = ci_lower, ymax = ci_upper,
                 fill = `Property type`))+
  geom_col(position = position_dodge(0.7), width = 0.7, color = 'black')+
  #geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.3)+
  geom_errorbar(alpha = 0.7, position = position_dodge(0.7), width = 0.3)+
  #geom_point(shape = 21, size = 2.6, color = 'black')+
  #facet_wrap(~src, nrow = 1)+
  #scale_x_continuous(limits = c(0,1.01), breaks = c(0, 0.5, 1)) +
  scale_y_continuous(limits = c(0,1.01), breaks = c(0,0.5, 1)) +
  #coord_fixed()+
  #xlab("Model prediction")+
  ylab("Implied prevalence")+
  theme(axis.title.x = element_blank())


md.impprev.plotting <- md.impprev %>% 
  filter((Parameter == "posterior") | (semantics == "uncertain")) %>%
  mutate(src = paste(Parameter, "_", semantics, sep =""),
         src = factor(src, levels = c("prior_uncertain", "posterior_some",
                                      "posterior_most", "posterior_uncertain"),
                      labels = c("Prevalence prior mean",
                                 '"some"\n(threshold = 0.01)',
                                 '"most" + noise\n(threshold = 0.5)',
                                 'generic\n(uncertain threshold)')),
         "Property type" = factor(stim_type,
                                         levels = c("part",
                                                    "vague",
                                                    "color",
                                                    "accidental"),
                                         labels = c("body part",
                                                    "color adj + part",
                                                    "gradable adj + part",
                                                    "accidental")))



fig.cimpian.interpretation.models <- ggplot(md.impprev.plotting, 
       aes( x = model_MAP, xmin = model_lower, xmax = model_upper, 
                        y = mean, ymin = ci_lower, ymax = ci_upper,
                 fill = `Property type`))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.3)+
  geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)+
  geom_point(shape = 21, size = 2.6, color = 'black')+
  facet_wrap(~src, nrow = 1)+
  scale_x_continuous(limits = c(0,1.01), breaks = c(0, 1)) +
  scale_y_continuous(limits = c(0,1.01), breaks = c(0, 1)) +
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Implied prevalence")+
  theme(legend.position = 'right')

cowplot::plot_grid( 
  fig.cimpian.interpretation.95ci + theme(
    plot.margin = unit(c(30, 6, 0, 6), "pt"),
                         legend.position = 'none'),
  cowplot::plot_grid(
    fig.cimpian.interpretation.stimtype + theme(plot.margin = unit(c(20, 6, 12, 6), "pt"),
                           legend.position = 'none'),
    fig.cimpian.interpretation.models + theme(plot.margin = unit(c(0, 6, 0, 6), "pt"),
                           legend.position = 'none'), 
    nrow = 1,
    labels = c("B", "C"),
    rel_widths = c(1, 2.5)
  ), 
  cowplot::get_legend(
    fig.cimpian.interpretation.stimtype + theme(
      legend.position="bottom"
      #legend.text = element_text(size = 16),
      #legend.title = element_text(size = 16)
                           )
    ), ncol = 1, rel_heights = c(1.2, 1.2, 0.2),
  labels = c("A", "", "")
  )

```


We now test the quantitative predictions of the model. 
We use the prevalence priors reconstructed from Expt. 1a's structured elicitation task via Eq. \ref{eq:priorModel} as the prevalence prior $P(r)$ in Eq. \ref{eq:L0} to predict the generic interpretation data.
We built a joint-inference Bayesian data analysis (BDA) model to predict both the prevalence prior data and the generic interpretation data simultaneously.
We ran the model using 3 chains of MCMC for 750,000 iterations, the first 250,000 of which were discarded for burn-in. 
Figure\ \@ref(fig:cimpian-modelingResults)B shows the generics model predictions and the human data for each of the four types of properties (collapsing across items within a property-type).
We see that the model displays the same sensitivity to the kind of property: Generics about body parts are interpreted the strongest, accidental properties the weakest, with the other two types falling in between.

We compare our generic interpretation to two lesioned versions of the model, both of which lack the uncertain threshold (a "some" most and a "most" model, described in the **Alternative models** section above). 
Figure\ \@ref(fig:cimpian-modelingResults)C shows the model predictions in the comparison to the behavioral data for each item independently for the generics model, the two alternative fixed threshold models, and the prevalence prior mean.
The alternative models' defects are apparent visually. 
The prevalence prior, though it is highly correlated with the posterior ($r^2(40)=$ `r compute_r2(md.impprev %>% filter(semantics == "uncertain", Parameter == "prior"), "model_MAP", "mean")`), predicts too low values, resulting in a high mean squared error ($MSE=$ `r compute_mse(md.impprev %>% filter(semantics == "uncertain", Parameter == "prior"), "model_MAP", "mean")`).
The "some" model is similar: It is highly correlated ($r^2(40)=$ `r compute_r2(md.impprev %>% filter(semantics == "some", Parameter == "posterior"), "model_MAP", "mean")`) but underpredicts the data ($MSE=$ `r compute_mse(md.impprev %>% filter(semantics == "some", Parameter == "posterior"), "model_MAP", "mean")`).
The "most" + noise model achieves a pretty good fit to the data ($r^2(40) =$ `r compute_r2(md.impprev %>% filter(semantics == "most", Parameter == "posterior"), "model_MAP", "mean")`; $MSE=$ `r compute_mse(md.impprev %>% filter(semantics == "most", Parameter == "posterior"), "model_MAP", "mean")`), but only does so because it predicts about a third of the data set is noise (proportion noise = $0.37 (0.33, 0.42)$).
Finally, the uncertain threshold generic interpretation model explains practically all of the variance in the data ($r^2(40) =$ `r compute_r2(md.impprev %>% filter(semantics == "uncertain", Parameter == "posterior"), "model_MAP", "mean")`) and achieves an extremely low mean squared error ($MSE =$ `r compute_mse(md.impprev %>% filter(semantics == "uncertain", Parameter == "posterior"), "model_MAP", "mean")`).

## Discussion

We replicated @Cimpian2010's finding of a difference in the implied prevalence between biological properties (e.g., *yellow fur*) and accidental properties (e.g., *fungus-covered claws*).
We extended these findings with a broader stimulus set and discovered even more gradability in interpretations of generic statements. 
We empirically measured the prevalence priors and used our generic interpretation model to predict prevalence implied by a generic statement.

\mht{does this add anything? do we want to speculate a little more about where these differences in parameters might come from?}
The structured elicitation of prevalence knowledge in Expt. 1a provides a more detailed picture of what differs between these kinds of properties. 
Properties differ in both the *a priori* probability of being present in a category as well as how widespread the property would be expected to be, given that it is present (Figure\ \@ref(fig:cimpian-prevPrior)).
It is these differences that give rise to different implied prevalence ratings for generics about different properties.

The items that receive the lowest implied prevalence are those of accidental or diseased states (e.g., *fungus-covered claws*, *broken legs*). 
As @Cimpian2010 noted, "properties of this type do not lend themselves very well to generic predication (Cimpian & Markman, 2008; Gelman, 1988), so generics about broken legs, itchy skin, etc. are infrequent outside the laboratory." (p.1472)
It, thus, remains a possibility that participants treat statements such as "Lorches have broken legs" as an existential claim about the here-and-now, analagous to how "Dogs are on my front lawn" describes a particular state of affairs as opposed to something generalizable about dogs. 
We thus aim to replicate these findings of low prevalence prevalence interpretations in the next experiment, using properties that more naturally lend themselves to generic interpretation.
In addition, we use more naturalistic properties and measure background knowledge using a more direct elicitation technique that does not presuppose a structured model for the prevalence prior.

# Experiment 2

This experiment is designed to measure the prevalence implied by a generic about a diverse set of properties (Expt. 2b). 
In addition, we elicit participants' beliefs about the likely prevalence levels expected for these different properties (Expt. 2a). 
We again use our computational model and alternative models, all using the elicited prevalence priors, to make predictions about the prevalence implied by a generic.

## Experiment 2a: Prevalence prior elicitation

In this experiment, we elicit prevalence knowledge about a diverse set of familiar properties.
Because the properties are relatively familiar, we elicit participants' knowledge without assuming a particular structure (as was done in Expt. 1a). 
This allows us for a non-parametric examination of the priors. 

```{r load expt 2a meta data}
load(file = "cached_results/genint_priors_metaData.RData")
# expt2.prior.n,
#      expt2.prior.nonEnglish,
#      expt2.prior.catchFail,
#      expt2.prior.n.passCatch.English,
#      df.prior.3.filtered.meanTime, 
#     df.prior.3.filtered.n_subj_per_item
```


### Methods

#### Participants

We recruited `r expt2.prior.n` participants from MTurk.
This number was arrived at with the intention of getting approximately 23 independent sets of ratings for each unique item in the experiment.
Participants were restricted to those with U.S. IP addresses and with at least a 95\% MTurk work approval rating (these same criteria apply to all experiments reported).
The experiment took on average `r round(df.prior.3.filtered.meanTime$mean_time, 1)` minutes and participants were compensated \$0.80.

#### Materials

We created a stimulus set composed of seventy-five properties.
Items were generated by the first author by considering eight different classes of properties: physical characteristics (e.g., *have brown spots*, *have four legs*), psychological characteristics (e.g., *experience emotions*), dietary habits (e.g., *eat human food*), habitat (e.g., *live in zoos*), disease (e.g., *get cancer*, *carry malaria*), reproductive behavior (e.g., *have a menstrual cycle*), aggressive behaviors (e.g., *pound their chests to display dominance*, *hunt other animals*), and other miscellaneous behaviors (e.g., *perform in the circus*, *sing beautiful songs*); online sources about strange animal behaviors were consulted in order to find the more obscure properties. Full list of materials can be found in \red{Table X} in Appendix.

#### Procedure and materials

On the first trial, participants were asked to list three kinds of animals for each of five different classes of animals: mammals, fish, birds, insects/bugs, amphibeans/reptiles. 
The five classes of animals were presented in a randomized order on the screen and there were three text boxes for each in which participants could type an animal kind.
On subsequent trials, participants were shown a random subset of five animal kinds and asked what percentage each of these categories they believed had a property (e.g., "Out of all of the cheetas in the world, what percentage do you think attack hikers?").
Pilot results indicated similar responses were generated by a question about frequency (e.g., "Out of 100 cheetahs, how many do you think attack hikers?").
Participants responded using a slider bar with endpoints labeled 0% and 100%, and the exact number corresponding to their slider bar rating was displayed once participants clicked on the slider bar.
Each participant saw a random selection of twelve properties.

\ndg{say something about why elicitation paradigm is different for this expt than last one? partly to give a non-parametric look at priors?}
\mht{i did this in the introductory remarks about the expt.}

As an attention check, at the end of the prior elicitation trials, participants were asked to select, from a list of ten, all of the properties they could remember being tested on. 
The list included five properties that they had been tested on and five distractors. 
The experimental paradigm can be seen here: http://stanford.edu/~mtessler/generic-interpretation/experiments/generics/prior-3.html.

### Results

We used the same exclusion criteria that were preregistered for the subsequent generic interpretation study (Expt. 2b): https://osf.io/bwn4t/register/5771ca429ad5a1020de2872e. 
Participants who did not have at least 4 out of 5 hits and at least 4 out of 5 correct rejections during the memory trial were excluded ($n = `r expt2.prior.catchFail`$).
In addition, we excluded participants who self-reported a native language other than English ($n = `r expt2.prior.nonEnglish`$). 
This left a total of $n = `r expt2.prior.n.passCatch.English`$ participants, with items receiving on average `r round(df.prior.3.filtered.n_subj_per_item$n_subj_per_item)` (range = [`r round(df.prior.3.filtered.n_subj_per_item$lb)`, `r round(df.prior.3.filtered.n_subj_per_item$ub)`]) unique participants responses (each participant provides five ratings).

A response in this task can be thought of as a sample from a property's prevalence prior distribution.
Thus, the distribution of responses for an item are an estimate of the prevalence prior distribution.
Figure\ \@ref(fig:genInt-prevPrior)A shows eight example items' distributions of responses.
For example, the property *have four legs* is most likely either completely present (prevalence = 100%) or completely absent (prevalence = 0%) from categories.
*Eat insects* looks similar, though there is considerable probability mass spread among the non-binary alternatives ($0\% <$ prevalence $< 100\%$). 
*Get in fights with other animals* is similar but has substantially less probability mass at 100% prevalence: It is unlikely that this property is widespread in a category. 
*Live in urban areas* shows a monotonically decreasing probability function; the higher the prevalence, the less likely it is. 
*Live in zoos* is expected to be even less prevalent, and the property *has seizures* is expected to not be widespread at all. 
The property *get erections* is only expected to be present in 50% of the population (presumably, the males) when it is present at all.

Most of the elicited prevalence prior distributions are at least bi-modal. 
To visualize all properties simultaneously, we represent each distribution by its relative probability mass at 0%---$P(\text{feature is present})$, or $P(r > 0)$---and the expected value (mean) of the distribution conditional on the prevalence being greater than 0\%---$\mathbb{E}[P(r \mid r>0)]$ or the its *prevalence when present* (Figure\ \@ref(fig:genInt-prevPrior)B).
Our stimulus set covers a wide range of possible values of both of these parameters; the set of parameters that summarize these priors is also largely non-overlapping with those of Expt. 1 (compare with Figure\ \@ref(fig:cimpian-prevPrior)A).
This suggests we have sampled items with priors that exhibit a lot of quantitative variability.
Given these priors, our model makes quantitative predictions about the prevalence implied by a novel generic sentence (e.g., "Lorches live in zoos").

```{r genInt-prevPrior, fig.width = 12, fig.asp = 0.35, fig.cap="Prevalence priors for a broad set of animal properties.  A: Ten example prevalence priors elicited in Expt. 2a. Different prevalence priors give rise to different model predicted implied prevalence. B: Prevalence priors summarized by their relative probability mass at zero-prevalence P(feature is present), and their expected value among non-zero prevalence levels: Prevalence when present. Error bars denote bootstrapped 95% confidence intervals. "}
#load(file = "cached_results/genInt_priors.RData")
# df.prior.prevalence.2.isZero.conditionalEv,
#      df.prior.prevalence.2,

load(file = "cached_results/genInt_priors3.RData")

# df.prior.prevalence.3.isZero.conditionalEv,
#      df.prior.prevalence.3,
#      df.prior.3.filtered.bs,

fig.prevParams.genInt <- ggplot(df.prior.prevalence.3.isZero.conditionalEv, 
       aes( x = 1-isZero, xmin = 1-zero_low, xmax = 1-zero_high,
            y = pwp_mean, ymin = pwp_low, ymax = pwp_high))+
  geom_errorbar(alpha = 0.3) + geom_errorbarh(alpha = 0.3) + 
  geom_point(shape = 21, size = 2.6, color = 'black', fill = 'black')+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  # ggrepel::geom_label_repel(data = df.prior.prevalence.3.isZero.conditionalEv %>% 
  #                             filter(property %in% c("have four legs", 
  #                      "eat insects", 
  #                      #"feed on the carcasses of dead animals",
  #                      "get in fights with other animals",
  #                      "know when earthquakes are about to happen",
  #                      "live in zoos",
  #                      #"drink alcohol left behind by tourists",
  #                      #"chase their tails",
  #                      "have seizures")), 
  #                           aes(label = property))+
  ylab("Prevalence when present")+
  xlab("P(feature is present)")+
  coord_fixed()

target.properties <- c("have four legs", 
                       "eat insects", 
                       "eat garbage",
                       #"feed on the carcasses of dead animals",
                       "are afraid of loud noises",
                       "get in fights with other animals",
                       "live in urban areas",
                       "know when earthquakes are about to happen",
                       "get erections",
                       "live in zoos",
                       #"drink alcohol left behind by tourists",
                       #"chase their tails",
                       "have seizures")

var_width <- 22

fig.prevPriors.genInt <- df.prior.3.filtered.bs %>% ungroup() %>%
  filter(property %in% target.properties) %>%
  mutate(property = factor(property, levels = target.properties,
                           labels = stringr::str_wrap(target.properties, 
                                                      width = var_width))) %>%
  mutate(state = as.numeric(state)) %>%
  group_by(property, state) %>%
  summarize( lower = quantile(prop, 0.025),
             mean = mean(prop),
             upper = quantile(prop, 0.975)) %>%
  ggplot(., aes( x = state, y = mean, ymin = lower, ymax = upper))+
  geom_col(position= position_dodge(), color = 'black', fill= 'white')+
  geom_errorbar(position = position_dodge(), width= 0.036, alpha = 0.4 )+
  facet_wrap(~property, nrow = 2) +
  scale_x_continuous(limits = c(-0.1, 1.1), breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(-0, 0.8), breaks = c(0, 0.25, 0.5, 0.75))+
  ylab("Proportion of responses")+
  xlab("Prevalence")

cowplot::plot_grid(
  fig.prevPriors.genInt + theme(plot.margin = unit(c(6, 6, 6, 0), "pt"),
                         legend.position = 'none'), 
  fig.prevParams.genInt + theme(plot.margin = unit(c(18, 6, 6, 6), "pt"),
                         legend.position = 'none'),

  nrow = 1,
  labels = c("A", "B"),
  rel_widths = c(2.5, 1)
)

```

## Experiment 2b: Generic interpretation

```{r load expt2b meta data}
load(file = "cached_results/genint_int_metaData.RData")

# expt2.int.n,
#      expt2.int.nonEnglish,
#      expt2.int.catchFail,
#      expt2.int.n.passCatch.English,
#      df.int.6.meanTime, 
#      df.int.6.filtered.n_subj_per_item,
#      df.int.56.filtered.means.r, df.int.56.filtered.means.n,
#   df.int.56.filtered.means.spearman,

```

### Methods

#### Participants

We recruited `r expt2.int.n` participants from MTurk. 
This number was arrived at with the intention of getting approximately 50 ratings for each unique item in the experiment.
The experiment took on average `r round(df.int.6.meanTime$mean_time,1)` minutes and participants were compensated \$0.80.

#### Procedure and materials

The materials were the same as in Expt. 2a.
Participants were told that scientists had recently discovered lots of new animals that we did not know existed.
On each trial, they would be told facts about the new animals and be asked to translate it into the percentage of that animal it applies to.
On each trial, participants read "You are told: *generic sentence*", where the generic sentence was a bare plural statement about a familiar property $F$ applying to a novel animal category $K$ (e.g., "Javs attack hikers").
They were then asked "Out of all of the *K*s on the planet, what percentage do you think *F*?" (e.g., "Out of all of the javs on the planet, what percentage do you think attack hikers?").
Novel animal category names were mostly taken from @Cimpian2010 and similar studies on generic language. 
Participants responded using a slider bar with endpoints labeled 0% and 100%, and the exact number corresponding to their slider bar rating was displayed once participants clicked on the slider bar.
Each participant completed thirty-five trials, corresponding to a random subset of the full stimulus set.

After the generic interpretation trials, participants completed the same memory check trial as was done in the prior elicitation. 
They were shown ten properties and asked to click on those they had seen in the experiment.
Following the memory check trials, participants completed up to five explanation trials, depending on their ratings in the task.
On an explanation trial, participants saw a rating they had given for a property they had rated as applying to less than 50% and asked if they could explain why they gave the response that they gave. 
Participants also had the option of changing their response after providing an explanation. 
These data were only used in exploratory analyses and not for the main analysis reported below.
If participants gave no ratings less than 50%, they did not complete any explanation trials. 

The experimental paradigm can be viewed at http://stanford.edu/~mtessler/generic-interpretation/experiments/generics/interpretations-6.html

### Results

We used preregistered exclusion criteria, which were also used for Expt. 2a. 
Participants who did not have at least 4 out of 5 hits and at least 4 out of 5 correct rejections during the memory trial were excluded ($n = `r expt2.int.catchFail`$).
In addition, we excluded participants who self-reported a native language other than English ($n = `r expt2.int.nonEnglish`$). 
This left a total of $n = `r expt2.int.n.passCatch.English`$ participants, with items receiving on average `r round(df.int.6.filtered.n_subj_per_item$n_subj_per_item)` responses (range = [`r round(df.int.6.filtered.n_subj_per_item$lb)`, `r round(df.int.6.filtered.n_subj_per_item$ub)`]).


```{r load interpretation results, cache=F}
load(file = "cached_results/genInt_interpretation6_prior3_modelData.RData")
#df.int.filtered, df.int.filtered.bs, md.impprev
load(file = "cached_results/genInt_interpretation6_prior3_mostNoise.RData")
format_empirical_ci <- function(
  df, estimate = "mean", low = "ci_lower",
  high = "ci_upper", sigfigs = 2){
  return(paste(
    round(df[[1,estimate]], sigfigs),
    " [",
    round(df[[1,low]], sigfigs),
    ", ",
    round(df[[1,high]], sigfigs),
    "]", sep = ""))
}

md.impprev.stats <- md.impprev %>%
  group_by(parameter, semantics) %>%
  summarize( mse  = mean((model_MAP-mean)^2),
             r2 = cor(model_MAP, mean)^2,
             n = n())
```


```{r}
# md.prevpriors.binned.summarized
load("cached_results/genInt_interpretation6_prior3_modelData_priorsSummarized.RData")

md.prevprior.stats <- md.prevpriors.binned.summarized %>%
  ungroup() %>%
  summarize(mse = mean((model - data)^2),
            r2 = cor(model, data)^2,
            n = n())
```

#### Descriptive results

Interpreting a novel generic sentence "Ks have F" often has the possibility of being understood as a universal or near-universal claim (*all or almost all Ks Fs)*. 
Across our seventy-five items, however, we observe a clear gradient in the implied prevalence ratings (Figure\ \@ref(fig:genint-modelingResults)A).
On one end of the continuum, there is a generic like "Wugs have four legs", which is interpreted as a universal---applying to exactly 100% of wugs---by `r sum(filter(df.int.filtered, property == "have four legs")$response == 1)` out of `r length(filter(df.int.filtered, property == "have four legs")$response)` participants and which received a mean implied prevalence rating of $`r format_empirical_ci(filter(df.int.filtered.bs, property == "have four legs"))`$. 
^[
  Note the novel category term is randomized for each participant and property. 
  We use particular novel category terms in the text for ease of exposition.
]
On the other end is "Glippets perform in the circus", which is interpreted as applying to less than 25% of glippets by `r sum(filter(df.int.filtered, property == "perform in the circus")$response < 0.25)` out of `r length(filter(df.int.filtered, property == "perform in the circus")$response)` participants and which receives a mean rating below 50% ($`r format_empirical_ci(filter(df.int.filtered.bs, property == "perform in the circus"))`$).
<!-- Several items have mean ratings below 50%.  -->
Additionally remarkable is the distribution of responses for individual items: Though "Feps live in zoos" probably means around 25% of feps live in zoos, it is still quite possible that almost 100% live in zoos (e.g., in the real world, 100% of Micronesian Kingfishers live in zoos).

To assess the reliability of these data, we ran a replication ($n=140$) using a slightly different dependent measure.^[
  By experimenter error, only seventy-four of the seventy-five items were collected in the replication data set.
]
Instead of being asked a question about percentages (e.g., "Out of all of the Ks in the world, what percentage F?"), participants were asked a question in terms of frequency: "Out of 100 Ks, how many do you think F?".
The empirical by-item means between these data and the original data are highly correlated ($r(`r df.int.56.filtered.means.n`) = `r round(df.int.56.filtered.means.r, 2)`$, $r_{spearman}(`r df.int.56.filtered.means.n`)= `r round(df.int.56.filtered.means.spearman, 2)`$), indicating very high data reliability.

#### Model-based analysis and results

Our primary analysis concerns how well the uncertain threshold generic interpretation model can accomodate the implied prevalence data in comparison to alternative models. 
To fit these models, we follow the same Bayesian data analytic approach as Expt. 1 to jointly predict the prevalence prior data (Expt. 2a) and the generic interpretation data (Expt. 2b).
We model the prevalence prior data as a mixture of three Beta distributions.
Each prevalence prior, thus, has eight parameters governing its shape: a mean $\gamma$ and variance parameter $\xi$ for each of the three Beta components and two parameters $\phi_1$, $\phi_2$ that describe the relative weighting among the three components.
We put uninformative priors over these parameters $\gamma \sim \text{Uniform}(0, 1)$, $\xi \sim \text{Uniform}(0, 100)$, $\phi \sim \text{Dirichlet}(1,1,1)$.
The inferred prevalence prior distributions are then used as $P(r)$ in Eq. \ref{eq:L0} in order to generate predictions for the generic interpretation data.^[
  In reality, this procedure is done simultaneously, not sequentially.
]
The generic interpretation model is fully specified by Eq. \ref{eq:L0} and has no free parameters.

To learn about the credible values of the parameters governing the prevalence priors as well as generate model predictions for the generic interpretation data, we performed Bayesian inference on the model by running three chains of an incrementalized version of MCMC [@Ritchie2016] for 750,000 iterations, removing the first 250,000 iterations for burn-in.
A qualitative examination showed that the prevalence prior distributions were well-modeled as a mixture of three Beta distributions. 
Often one Beta distribution is devoted to accounting for the very small numbers (0% or near 0% prevalence ratings), while the two other components model the other parts of the distribution, the details of which depend upon the property.
To provide a quantitative examination of the fit to the priors data, we look at the posterior predictive distribution discretized to bins in increments of 10% prevalence (i.e., categorical distributions over the bins of 0%, 10%, ..., 90%, 100% prevalence) and compare the model's inferred priors to the empirical counts that fell into those bins. 
The joint data analysis model accomodates the empirical patterns in the prevalence priors very well: $r^2(`r md.prevprior.stats[["n"]]`) = `r format(md.prevprior.stats[["r2"]], digits = 3)`$, $MSE = `r format(md.prevprior.stats[["mse"]], digits = 2)`$.
\ndg{we should have a brief result reporting the posterior predictive check on the priors data? ie how well does our joint data analysis accommodate the empirical patterns in the prevalence priors.}
\mht{above. okay?}

As a first attempt to understand the implied prevalence data in a quantitative way, we compare the means of the inferred prevalence priors to the empirical means of the implied prevalence data (Figure\ \@ref(fig:genint-modelingResults)B top facet).
The means of the prevalence prior distributions do a rather poor job at predicting the implied prevalence ratings, consistently underpredicting the ratings ($r^2(`r filter(md.impprev.stats, semantics == "uncertain", parameter == "prior")[["n"]]`) = `r filter(md.impprev.stats, semantics == "uncertain", parameter == "prior")[["r2"]]`$, $MSE = `r format(filter(md.impprev.stats, semantics == "uncertain", parameter == "prior")[["mse"]], digits = 2)`$).
The fact that the prevalence prior data underpredicts the generic interpretation data is good evidence that participants are actually *updating* their beliefs about the property in the generic interpretation task, as opposed to simply responding according to their prior beliefs.

As before, we ran alternative interpretation models using the same data analytic approach (i.e., joint cognitive-statistical models) but which had access to only a single fixed-threshold rather the uncertain threshold of the generic interpretation model. 
<!-- \ndg{similarly, a short section on alternative models at the end of the model section would save having to re-explain the alternatives each time, and give a better flow.} -->
<!-- These alternative models correspond to models of the quantifier "some" and "most" and provide strict tests of our generic interpretation model because they too have access to the full prior distribution over prevalence as well as the flexibility endowed by the Bayesian data analysis method. -->
Figure\ \@ref(fig:genint-modelingResults)B shows each of the alternative model's predictions (technically, the BDA models' posterior predictive distributions) for the mean implied prevalence of each of the seventy-five novel generic sentences, in comparison to the empirical means. 
We see that the model based on quantifier "some" (i.e., a fixed threshold at the lowest possible value) consistently *underpredicts* the implied prevalence, consistent with the intuition that assigning the semantics of "some" for generics is too weak.
Though the model explains a lot of the variance $r^2(`r filter(md.impprev.stats, semantics == "some", parameter == "posterior")[["n"]]`) = `r filter(md.impprev.stats, semantics == "some", parameter == "posterior")[["r2"]]`$, it does so with a relatively high mean squared error $MSE = `r format(filter(md.impprev.stats, semantics == "some", parameter == "posterior")[["mse"]], digits = 2)`$.
<!-- It is impossible for the model based on the quantifier "most" to accomodate these data: *Most* has a strict threshold at 0.5 and thus assigns probability 0 to all responses less than 0.5. \ndg{you said this already in expt 1} -->
<!-- In order to alleviate this issue, we endow the BDA model for "most" with a external noise parameter, which allows the model to randomly guess on some proportion of trial (the exact proportion is a parameter to be inferred from the data). -->
The "most" model assigns `r format_empirical_ci(m.samp.most.noise, "MAP", "cred_lower", "cred_upper")` proportion of the data to be noise, because of the high prevalence of minority (i.e., less than 50%) interpretations. 
A model based on the semantics for "most" is also not well-suited for these data $r^2(`r filter(md.impprev.stats, semantics == "most", parameter == "posterior")[["n"]]`) = `r filter(md.impprev.stats, semantics == "most", parameter == "posterior")[["r2"]]`$,  $MSE = `r format(filter(md.impprev.stats, semantics == "most", parameter == "posterior")[["mse"]], digits = 2)`$.

Finally, we examine the uncertain threshold model's predictions for the mean implied prevalence ratings. 
Unlike each of the alternative models, the uncertain threshold is able to perfectly accomodate the highly variable generic interpretation data $r^2(`r filter(md.impprev.stats, semantics == "uncertain", parameter == "posterior")[["n"]]`) = `r filter(md.impprev.stats, semantics == "uncertain", parameter == "posterior")[["r2"]]`$, $MSE = `r format(filter(md.impprev.stats, semantics == "uncertain", parameter == "posterior")[["mse"]], digits = 2)`$.
The generic interpretation model is able to flexibly adjust the threshold depending on the prevalence prior, resulting in context-sensitive generic interpretation that finely tracks human judgments.


```{r genint-modelingResults, fig.width = 11, fig.asp = 0.95, fig.cap="Implied prevalence data and model predictions for a broad set of seventy-four items. A: Mean implied prevalence ratings (points are individual empirical judgments). B: Posterior predictive model fits for quantitative models based on (i) the mean of the prevalence prior, (ii) a threshold semantics fixed at 0.01 (\"some\"), (iii) a threshold semantics fixed at 0.5 (\"most\"), and (iv) an uncertain threshold semantics (generic). The model for \"most\" is outfitted with a noise parameter to accomodate data points that are logically impossible given the fixed semantics. Error bars denote bootstrapped 95% confidence intervals for the behavioral data and 95% highest posterior density intervals for the model predictions.", cache = F}
fig.genint.interpretation.ci <- df.int.filtered %>%
  mutate(property = factor(property, 
                           levels =  with(df.int.filtered.bs, property[order(mean)]))) %>%
  ggplot(., aes( x = property, y = response, fill = property))+
  #geom_point()+
  #geom_pirate()+
  geom_pirate(violins = F, bars = F)+
  coord_flip()+
  #scale_color_viridis(discrete = T)+
  scale_y_continuous(limits= c(0, 1), breaks = c(0, 0.5, 1))+
  theme(axis.title.y = element_blank())+
  ylab("Implied prevalence rating")


fig.genint.interpretation.modelss <- md.impprev %>% 
  filter((parameter == "posterior") | (semantics == "uncertain")) %>%
  mutate(src = paste(parameter, "_", semantics, sep =""),
         src = factor(src, levels = c("prior_uncertain", "posterior_some",
                                      "posterior_most", "posterior_uncertain"),
                      labels = c("Prevalence prior mean",
                                 '"some"\n(threshold = 0.01)',
                                 '"most" + noise\n(threshold = 0.5)',
                                 'generic\n(uncertain threshold)'))) %>%
  ggplot(., aes( x = model_MAP, xmin = model_lower, xmax = model_upper, 
                        y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.3)+
  geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)+
  geom_point(alpha = 1)+
  facet_wrap(~src, ncol = 1)+
  scale_x_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
  scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human implied prevalence")


cowplot::plot_grid(
  fig.genint.interpretation.ci + theme(plot.margin = unit(c(12, 6, 6, 6), "pt"),
                         legend.position = 'none'),
  fig.genint.interpretation.modelss + theme(plot.margin = unit(c(0, 6, 6, 6), "pt"),
                         legend.position = 'none'), 
  nrow = 1,
  labels = c("A", "B"),
  rel_widths = c(3.5, 1)
)
```


## Discussion

In Expt. 2, we extended the findings of Expt. 1 to a larger and more diverse set of stimuli. 
We uncovered a continuum of interpretations of novel generic statements, and were able to predict the gradience in interpretation using the uncertain threshold generics model. 
Graded interpretations of generic statements result from diverse prior beliefs about properties operated over using an underspecified threshold criterion.
In our final experiment, we experimentally manipulate these prior beliefs to test their causal role in governing generic interpretations.


# Experiment 3: Prior Manipulation

In the previous experiments, we saw how participants' prior beliefs about the prevalence of the property, either measured by asking about alternative categories (Expt. 2) or abstract questions about the distribution of the property (Expt. 1), related to the prevalence implied by a novel generic via a model that reasons about an uncertain threshold on prevalence (Eq. \ref{eq:L0}).
In both of the previous experiments, we measured both generic interpretation and the prevalence prior and related the two via the uncertain threshold model. 
Though our model is able to finely track interpretations in a way that alternative models cannot, the evidence so far for the influence of the prevalence prior on interpretation is merely correlational. 
We have shown that the two are related but not that intervening on the prevalence prior can change interpretations.

In this final experiment, we test the causal role of the prevalence prior in generic interpretation. 
We do this by manipulating the prevalence prior and measuring the resulting influence on interpretation (*generic interpretation* condition).
To serve as a manipulation check, we first elicit predictions about prevalences following our prior manipulation procedure; these predictions also serve as the measurements of the (manipulated) prevalence priors used in our model.

## Experiment 3a: Prior elicitation (manipulation check)

### Methods

#### Participants

We recruited 200 participants from MTurk. 
This number was arrived at with the intention of getting approximately 30 ratings for each unique item in the experiment.
The experiment took on average 3 minutes and participants were compensated \$0.30.

#### Materials 

The goal of this experiment was to manipulate the prevalence prior. 
To focus on the influence of our prior manipulation cover story (described below), we chose to use a single property (*know when earthquakes are about to happen*) whose prevalence prior elicited in Expt. 2a suggested participants had a lot of uncertainty as to what prevalence levels to expect for this property, and thus could be particularly amenable to manipulation.^[
  Pilot testing using a completely novel property (e.g., *daxing*) appeared to make the task too artificial. Participants seemed to treat the task as a number game. 
]

Participants were familiarized with one of ten prevalence prior distributions, shown in Figure\ \@ref(fig:priorManipulationExpt)E). 
Nine of the ten distributions are bimodal with modes either at 0%, 25%, 50%, 75%, or 100%; the tenth distribution is uniform over all prevalence levels between 0% and 100%.
The mixture between the two modes was always 50% (half of samples were from one mode and half from the other, as shown in Figure\ \@ref(fig:priorManipulationExpt)B).

#### Procedure

```{r priorManipulationExpt, fig.cap="Overview of Experiment 3. A: Prevalences of feature in animals are shown one at a time, described in text and displayed in a table. B: Participants are asked to review previous results once all displayed. C: Prior elicitation task: Participants predict the results of the next five animals. D: Generic interpretation task: Participants rate prevalence after reading generic sentence. E: Experimentally manipulated prevalence prior distributions. The distribution shown in B is the \\emph{weak or deterministic} distribution.", fig.width = 11,fig.asp = 0.6}
zero.samples <- rbeta(n = 5000, shape1 = 1, shape2 = 100)
weak.samples <- rnorm(n = 5000, mean = 0.25, sd = 0.06)
half.samples <- rnorm(n = 5000, mean = 0.50, sd = 0.06)
strong.samples <- rnorm(n = 5000, mean = 0.75, sd = 0.06)
deterministic.samples <-rbeta(n = 5000, shape1 = 50, shape2 = 1)

sample.dists <- bind_rows(
  data.frame( dist = "0/25", x = c(zero.samples, weak.samples) ),
  data.frame( dist = "0/50", x = c(zero.samples, half.samples) ),
  data.frame( dist = "0/75", x = c(zero.samples, strong.samples) ),
  data.frame( dist = "0/100", x = c(zero.samples, deterministic.samples) ),
  
  data.frame( dist = "25/50", x = c(weak.samples, half.samples) ),
  data.frame( dist = "25/75", x = c(weak.samples, strong.samples) ),
  data.frame( dist = "25/100", x = c(weak.samples, deterministic.samples) ),

  data.frame( dist = "50/100", x = c(half.samples, deterministic.samples) ),
  data.frame( dist = "75/100", x = c(strong.samples, deterministic.samples) ),
  
  data.frame( dist = "uniform", x = rbeta(n = 50000, shape1 = 1, shape2 = 1))
)



distribution.order.levels <- c("rare_weak",
                                        "rare_half",
                                        "weak_or_half",
                                        "rare_strong",
                                        "weak_or_strong",
                                        "rare_deterministic", 
                                        "weak_or_deterministic",
                                        "half_or_deterministic",
                                        "strong_or_deterministic",
                                        "uniform")

# distribution.order.labels <- c("rare weak",
#                                         "rare half",
#                                         "weak or half",
#                                         "rare strong",
#                                         "weak or strong",
#                                         "rare deterministic", 
#                                         "weak or deterministic",
#                                         "half or deterministic",
#                                         "strong or deterministic",
#                                         "uniform")

distribution.order.labels <- c("0/25","0/50","25/50","0/75","25/75","0/100", "25/100",
                                        "50/100",
                                        "75/100",
                                        "uniform")
                                        
fig.manipulatedPriors <- sample.dists %>%
  mutate(dist = factor(dist, levels = distribution.order.labels)) %>%
  ggplot(., aes(x = x))+ 
  geom_density(aes( y = ..scaled..))+ #
  # geom_histogram(bins = 20,
  #   aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
  #   color = 'black', fill= 'grey')+
  scale_x_continuous(limits = c(-0, 1), breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
  #scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
  #scale_fill_solarized()+scale_color_solarized()+
  #scale_color_manual(values = c("#636363", "#d7191c"))+
  ylab("Scaled Prior Probability")+
  xlab("Prevalence")+
  facet_wrap(~dist, scales = 'free', nrow = 2)+
  guides(fill = F, color = F)+
  theme(legend.position = 'bottom', legend.direction = 'horizontal')


prior.manip.exp.1 <- ggdraw() + draw_image("figs/prior-manip-paradigm-1.jpeg", scale = 0.9) +
  theme(plot.margin = unit(c(2,0,0,0), "pt"),
        panel.background = element_rect(colour = "black", size=1)) 
prior.manip.exp.2 <- ggdraw() + draw_image("figs/prior-manip-paradigm-2.jpeg", scale = 0.9)+
  theme(plot.margin = unit(c(2,0,0,0), "pt"),
        panel.background = element_rect(colour = "black", size=1)) 
prior.manip.exp.3 <- ggdraw() + draw_image("figs/prior-manip-paradigm-priorMeasure.jpeg", scale = 0.95)+
  theme(plot.margin = unit(c(2,0,0,0), "pt"),
        panel.background = element_rect(colour = "black", size=1))
prior.manip.exp.4 <- ggdraw() + draw_image("figs/prior-manip-paradigm-intMeasure.jpeg", scale = 0.95)+
  theme(plot.margin = unit(c(2,0,0,0), "pt"),
        panel.background = element_rect(colour = "black", size=1))




prior.manip.toprow <- plot_grid(prior.manip.exp.1, 
                             prior.manip.exp.2, labels = c("A", "B"), nrow = 1, align = 'vh')

title <- ggdraw() + draw_label("Prevalence prior manipulation")
plot_grid(
  plot_grid(title, prior.manip.toprow, ncol=1, rel_heights=c(0.15, 1)),
  plot_grid(
    plot_grid(ggdraw() + draw_label("Manipulation check"), 
              prior.manip.exp.3, ncol=1, rel_heights=c(0.15, 1) ), 
    plot_grid(ggdraw() + draw_label("Generic interpretation"), 
              prior.manip.exp.4, ncol=1, rel_heights=c(0.15, 1) ),
              labels = c("C", "D"), nrow = 1),
  # plot_grid(add_sub(prior.manip.exp.3, "Manipulation check"), 
  #           add_sub(prior.manip.exp.4,"Generic interpretation"), labels = c("C", "D"), nrow = 1),
  fig.manipulatedPriors, labels = c("","", "E"),
  rel_heights = c(1,1,1.5),
  nrow = 3)
```

In order to avoid participants learning the structure of the task, participants completed only a single trial: Each participant saw only one prevalence distribution.
Participants were given a cover story in which they were asked to imagine they were an astronaut-scientist exploring a distant planet with lots of new animals on it.
They were studying these animals with another scientist to understand the animals' ability to "know when earthquakes are about to happen".
Participants were then shown data that they and their fellow scientist had collected about the prevalence of the property among different novel animals.
In order to minimize distraction, novel animals were simply labeled by a letter (e.g., "Animal C" or just "Cs").
Information about the animal appeared in an *evidence statement* (e.g., "After studying the animal, you and your partner determine that 98\% of Cs *know when earthquakes are about to happen*.") and were displayed in a table showing the corresponding numerical data (Figure\ \@ref(fig:priorManipulationExpt)A). 
Participants proceed in a self-paced way by clicking a button to reveal information about the next animals.
After participants viewed the data for ten categories, they are told to review the information about the animals before continuing (Figure\ \@ref(fig:priorManipulationExpt)B).
Then, the data table is removed and participants are provided the following prompt:

> Tomorrow, you and your partner will study 5 other new species of animals. What percentage of each do you think will know when earthquakes are about to happen?

Participants were given five slider bars ranging from 0% - 100%, and asked to predict the prevalence for the next five categories (Animals K - P; Figure\ \@ref(fig:priorManipulationExpt)C).
After rating the slider bars, participants were asked if they could explain why they gave the responses that they did. 
Then, they completed an attention check survey where they were asked what property was being investigated (choosing a response from a list of 10 options) and to input one of the prevalence levels they saw on the familiarization screen.

### Results

Participants who failed to either select the correct property or list a correct number from the familiarization period were excluded.

Similar to the data from Expt. 2a, a response in this task can be thought of as a sample from a prevalence prior distribution and the distribution of responses as estimates for the whole distribution.
We visualize the distributions by discretizing the responses so that each response goes into one of twenty equally spaced bins (effectively turning the 101-pt scale into a 20-pt scale).
Figure\ \@ref(fig:priorManipulationResults)A (top row) shows the empirically elicited predicted prevalence  distributions.
These distributions clearly reflect the familiarization distributions supplied to participants in the experiment, with some idiosyncractic features.
The distribution that is most different from the familiarization distribution is the uniform distribution; the empirical predicted distribution is more unimodal with a peak at 50%. 
Many distributions exhibit a regression to the mean in some participants' predictions: In the *rare or deterministic* distribution (which featured prevalence levels either around 0% or 100%), some participants guess that the next animal will have 50% prevalence; a similar phenomenon can be observed in the *weak or strong* distribution (25% or 75%) and to a lesser extent in the other bimodal distributions. 

Because our generic interpretation model has no free parameters, we use these empirically measured prevalence distributions to generate *a priori* model predictions using the generic interpretation data.
To account for our uncertainty in the measurement of the prevalence priors, we bootstrap the priors by resampling subjects (with replacement), calculating the empirical prevalence distributions (by binning, as above), and generating model predictions. 
We repeated this procedure 10,000 times to generate distributions of predictions.
The boostrapped mean and 95% quantiles for each prevalence bin in each distribution are shown in Figure\ \@ref(fig:priorManipulationResults)A (middle row).
We see that context-sensitive interpretations are predicted, with idiosyncracies that reflect empirically measured distributions.
We then tested these predictions against interpretations in the same empirical paradigm.

```{r priorManipulationResults, fig.cap="Experiment 3 results. A: Empirical distribution of responses for the prior elicitation task (Expt. 3a), generics model predictions based on those empirical distributions, and empirical distributions of responses for the generic interpretation task (Expt. 3b). B: Model predicted means for several alternative models and empirical means. C: Same as B shown in scatterplot.", fig.width = 13.5,fig.asp = 0.6}
load(file = "cached_results/gentInt_manipPriors_dists_expvals.RData")
# md.pm.int.3.filtered.expvals.bs.summary, md.pm.int.3.filtered.dists.bs.summary,
#      md.pm.int.3.filtered.dists.bs.summary.wide, md.pm.int.3.filtered.expvals.bs.summary.wide


md.pm.int.3.filtered.expvals.bs.summary.wide.summarized <- left_join(
      md.pm.int.3.filtered.expvals.bs.summary.wide %>%
      group_by(model) %>%
      summarize(ev_r2 = format(cor(model_prediction, mean)^2, digits = 2),
                ev_n = n(),
                ev_mse = format(mean((model_prediction - mean)^2), digits = 3)),
    md.pm.int.3.filtered.dists.bs.summary.wide %>%
      group_by(model) %>%
      summarize(fd_r2 = format(cor(model_mean, data_mean)^2, digits = 2),
                fd_n = n(),
                fd_mse = format(mean((model_mean - data_mean)^2), digits = 3))
    )




distribution.order.levels <- with(md.pm.int.3.filtered.expvals.bs.summary %>%
                         filter(model == "uncertain"), distribution[order(mean)])
distribution.order.labels <- gsub("_", " ", distribution.order.levels)

distribution.order.labels <- gsub(" ", "/", gsub(" or", "", gsub("deterministic", "100", gsub("strong", "75", gsub("half", "50", gsub("weak", "25", gsub("rare","0", distribution.order.labels)))))))



fig.int.dists.bs <- md.pm.int.3.filtered.dists.bs.summary %>%
  filter(model %in% c("prior", "uncertain", "data")) %>%
  mutate(distribution = factor(distribution,  levels = distribution.order.levels, labels = distribution.order.labels),
         model = factor(model, levels = c("prior", "uncertain", "data"),
                        labels = c("prevalence prior", "generics model", "data"))) %>%
  ggplot(., aes( x = state, y = mean, ymin = lower, ymax = upper, fill = distribution))+
  geom_col(position= position_dodge(), alpha = 0.8, color = 'black')+
  geom_errorbar(position = position_dodge(),  alpha = 0.3)+
  geom_text(data = data.frame(model = c("prevalence prior", "generics model", "data"),
    x = c(0.5, 0.5, 0.5),
    y = c(0.4, 0.5, 0.6),
    distribution = c("0/100","0/100","0/100")), 
    aes( x= x ,y =y, label = model), inherit.aes = F)+
  facet_grid(model~distribution, scales = 'free')+
  scale_x_continuous(breaks = c(0, 1))+
  scale_fill_viridis(discrete = T)+
  ylab("predicted / empirical probability")+
  xlab("prevalence")+
  theme(strip.text.y = element_blank())+
  guides(fill = F)


fig.int.expval.bs <- md.pm.int.3.filtered.expvals.bs.summary %>%
  ungroup() %>%
  filter(!(model %in% c("fixed_0.625", "fixed_0.875"))) %>%
  mutate(distribution = factor(distribution,  levels = distribution.order.levels, labels = distribution.order.labels),
         model = factor(model,
                        levels = c("prior", "uncertain", "data",
                                   "fixed_0.0175", "fixed_0.125",
                                   "fixed_0.375"),
                        labels = c("prevalence prior", "generics model", "data",
                                   '"some" (threshold = 0.01)', '"not rare" (threshold = 0.10)', 
                                   '"more than third" (threshold= 0.33)'))) %>%
  ggplot(., aes( x = distribution, y = mean, ymin = ci_lower, ymax = ci_upper, fill = distribution))+
  geom_col(position= position_dodge(), color  = 'black', alpha = 0.8)+
  geom_errorbar(position = position_dodge())+
  scale_fill_viridis(discrete = T)+
  ylab("Mean implied prevalence")+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+
  facet_wrap(~model, nrow = 2)+ guides(fill = guide_legend(reverse=T))



fig.int.expval.bs.scatters <- md.pm.int.3.filtered.expvals.bs.summary.wide %>%
  filter(!(model %in% c("fixed_0.625", "fixed_0.875","fixed_0.375"))) %>%
  mutate(distribution = factor(distribution, levels = distribution.order.levels),
         model = factor(model, levels = c("prior", "fixed_0.0175", "fixed_0.125", "uncertain"),
                        labels = c("prevalence prior", '"some"\n(fixed threshold = 0.01)', '"not rare" (fixed threshold = 0.10)',
                                   "generics model \n (uncertain threshold)"))) %>%
  ggplot(., aes(x = model_prediction, xmin = model_lower, xmax = model_upper, ymin = ci_lower, y = mean, ymax = ci_upper, fill = distribution))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.3)+
  geom_errorbar(position = position_dodge(), alpha = 0.8)+
  geom_errorbarh(position = position_dodge(), alpha = 0.4)+
  geom_point(shape = 21, color = 'black')+
  scale_fill_viridis(discrete = T)+
  ylab("Empirical mean implied prevalence")+
  xlab("Model prediction")+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
  coord_fixed()+
  facet_wrap(~model, nrow = 2)+
  guides(fill = F)




cowplot::plot_grid(
  fig.int.dists.bs + theme(plot.margin = unit(c(6, 6, 6, 0), "pt"),
                         legend.position = 'none'), 
  cowplot::plot_grid(
    fig.int.expval.bs + theme(plot.margin = unit(c(6, 6, 6, 6), "pt"),
                         legend.position = 'none'),
    fig.int.expval.bs.scatters + theme(plot.margin = unit(c(6, 0, 0, 0), "pt"),
                           legend.position = 'none'),
    get_legend(fig.int.expval.bs), rel_widths = c(1, 0.65,0.3),
    nrow = 1,  labels = c("B", "C", "")
  ),
  nrow = 2,
  labels = c("A", "B"),
  rel_widths = c(3.5, 1, 1)
)
```




## Experiment 3b: Generic interpretation

### Methods

```{r load prior manip meta data}
load(file = "cached_results/priorManip_int_metaData.RData")
# expt3.int.catchFail,
#      expt3.int.nonEnglish,
#      expt3.int.n,
#      expt3.int.n.passCatch.English,
#      expt3.int.meanTime,
#df.prior_manip.int.filtered.n_subj_per_item
```

The sample size, exclusion criteria, and planned statistical contrasts were all preregistered: https://osf.io/n342q/register/5771ca429ad5a1020de2872e. 

#### Participants

We recruited `r expt3.int.n` participants from MTurk.
This number was arrived at with the intention of getting approximately 50 ratings for each unique item in the experiment.
The experiment took on average `r round(expt3.int.meanTime$mean_time, 1)` minutes and participants were compensated \$0.30.

#### Materials and procedure

The materials and procedure were identical to those of Expt. 3a with the following exception. 
After the familiarization period, the data table is removed and participants are provided the following prompt:

> The next day, you are busy and your partner studies a new animal on their own: Animal K.
> Your partner tells you: "Ks know when earthquakes are about to happen."

In order to encourage participants to pay attention to the language, this text is on the screen for five seconds before participants are asked: "What percentage of Ks do you think know when earthquakes are about to happen?" and provided with a slider bar ranging from 0%-100% (Figure\ \@ref(fig:priorManipulationExpt)D). 
As in Expt. 3a, participants then completed an attention check survey where they were asked what property was being investigated and to input one of the prevalence levels they saw on the familiarization screen.
The experiment can be viewed at http://stanford.edu/~mtessler/generic-interpretation/experiments/generics/prior-manipulation-2.html. 
<!-- Participants see the data from eleven different categories, though they are told the data for one kind were lost and a "?" was placed in the table (\red{Figure}).^[ -->
<!--   These lost results would be found in the *generic interpretation* task, Expt. 3b. -->
<!--   We chose to present a "lost data" category to imply that the sampling procedure for the referent-category was random. The alternative would be to present data from ten categories and have participants rate the eleventh, which could imply that the scientists are collecting data until they find one for which the property applied generically. \red{[clean up]} -->
<!-- ] -->


<!-- scientists had recently discovered lots of new animals that we did not know existed, and that scientists were trying to understand the properties of these new animals.  -->

<!-- From the stimulus set of 74 properties used in Expt. 2, we selected a subset of 24 items that received intermediate interpretation judgments (Expt. 2b: implied prevalence between: 40 - 65\%), which we believed would make them most susceptible to our prior manipulation. -->

### Results

```{r load prior manip regression}
load(file = "cached_results/gentInt_manipPriors_lm.RData")
# rs.lm.priorManip
# rs.lm.priorManip.contrast1,
# rs.lm.priorManip.contrast2,
# rs.lm.priorManip.contrast3,
# rs.lm.priorManip.contrast4,
# rs.lm.priorManip.contrast5,
# rs.lm.priorManip.contrast6,

rs.lm.priorManip.contrast1.summ <- summary(rs.lm.priorManip.contrast1)
rs.lm.priorManip.contrast2.summ <- summary(rs.lm.priorManip.contrast2)
rs.lm.priorManip.contrast3.summ <- summary(rs.lm.priorManip.contrast3)
rs.lm.priorManip.contrast4.summ <- summary(rs.lm.priorManip.contrast4)
rs.lm.priorManip.contrast5.summ <- summary(rs.lm.priorManip.contrast5)
rs.lm.priorManip.contrast6.summ <- summary(rs.lm.priorManip.contrast6)
rs.lm.priorManip.summ <- summary(rs.lm.priorManip)

```

We used preregistered exclusion criteria, which were also used for Expt. 3a.
Participants who failed to either select the correct property or list a correct number from the familiarization period were excluded ($n = `r expt3.int.catchFail`$).
In addition, we excluded participants who self-reported a native language other than English ($n = `r expt3.int.nonEnglish`$). 
This left a total of $n = `r expt3.int.n.passCatch.English`$ participants, with items receiving on average `r round(df.prior_manip.int.filtered.n_subj_per_item$n_subj_per_item)` responses (range = [`r round(df.prior_manip.int.filtered.n_subj_per_item$lb)`, `r round(df.prior_manip.int.filtered.n_subj_per_item$ub)`]).

Our main qualitative hypothesis is that there would be a difference across conditions in interpretations of the same generic sentence ("Ks know when earthquakes are about to happen").
The differences in interpretations are evident in the empirical distributions of responses (Figure \@ref(fig:priorManipulationResults)A, bottom row).
More specifically, we predict that the prevalence implied by the generic sentence will, to a first approximation, track the mean of the prevalence prior distribution.
To test this, we ran a linear model predicting responses with a fixed effect of the prior mean (as estimated by the data from Expt. 3a).
There was a significant main effect of prior mean, with a coefficient close to 1 ($\beta_1 = `r rs.lm.priorManip.summ[["coefficients"]][["prior_mean", "Estimate"]]`$, $SE=`r rs.lm.priorManip.summ[["coefficients"]][["prior_mean", "Std. Error"]]`$, $t = `r rs.lm.priorManip.summ[["coefficients"]][["prior_mean", "t value"]]`$), indicating a strong linear relationship between the mean of the learned prevalence prior and the resulting interpretations.
Furthermore, there was a significant main effect of intercept, indicating that participants' responses were significantly greater than the mean of the corresponding prevalence priors ($\beta_0 = `r rs.lm.priorManip.summ[["coefficients"]][["(Intercept)", "Estimate"]]`$, $SE=`r rs.lm.priorManip.summ[["coefficients"]][["(Intercept)", "Std. Error"]]`$, $t = `r rs.lm.priorManip.summ[["coefficients"]][["(Intercept)", "t value"]]`$).
These results show that participants interpret the novel generic sentence in a manner sensitive to the background distribution and that the generic utterance updates participants' beliefs to indicate a prevalence significantly higher than the prior.
There is a lot more to be learned from these data, however; this simple linear model explains less than a quarter of the variance in the data $r^2 = `r rs.lm.priorManip.summ[["r.squared"]]`$.

From the generics model, we are able to make a number of *a priori* predictions about quantitative differences in mean implied prevalence ratings across the ten conditions. 
These predictions were derived by examining pairs of conditions with small quantitative differences but for which the bootstrapped 95% confidence interval around the generics model predictions did not overlap (Figure\ \@ref(fig:priorManipulationResults)B, "generics model" panel).
<!-- For example, Figure\ \@ref(fig:priorManipulationResults)B ("generics model" panel) -->
With those criteria in mind, we preregistered the following contrast predictions among mean implied prevalences (\{\}s indicate no predicted difference): 0/25 $<$ \{25/50, 0/50\} $<$ \{25/75, *uniform*\} $<$ 25/75 $<$ \{25/100, 50/100\}  $<$ \{75/100, 0/100\}.
To evaluate these predictions, we built a Bayesian regression model with the relevant contrasts using a "zero and one inflated beta" linking function to appropriately model the responses of exactly 0% and 100%, which are undefined under the beta distribution.
The maximum a-posteriori estimates and 95% credible intervals of the coefficients of the regression model, as well as the model predicted qualitative differences, are shown in Table 1.
Each of the five predicted positive differences were estimated to be greater than zero, and each of the four predicted null differences were not different from zero.
Overall, the uncertain threshold model predicts much of the variance in the means of these empirical distributions: $r^2(`r filter(md.pm.int.3.filtered.expvals.bs.summary.wide.summarized, model == "uncertain")[["ev_n"]]`) = `r filter(md.pm.int.3.filtered.expvals.bs.summary.wide.summarized, model == "uncertain")[["ev_r2"]]`; MSE = `r filter(md.pm.int.3.filtered.expvals.bs.summary.wide.summarized, model == "uncertain")[["ev_mse"]]`$

<!-- We compare these predictions to those made by three fixed threshold models: a literal "some" model (fixed threshold at 0.01), and fixed threshold models with thresholds at 0.1 and 0.35. -->
<!-- The fixed thresholds of 0.1 and 0.35 were chosen to lie in between the 0% and 25% distributions, and the 25% and 50% distributions, respectively. -->
<!-- Predictions of these models, as well as a model based on the prevalence prior, for the average implied prevalence given the ten distributions are shown in Figure\ \@ref(fig:priorManipulationResults)B. -->


```{r brmTable, results="asis"}

load(file = "cached_results/gentInt_manipPriors_brms_contrasts.RData") #rs.brm.priorManip.sdif

df.rs.brm.priorManip.sdif.summ <- data.frame(summary(rs.brm.priorManip.sdif)$fixed)
df.rs.brm.priorManip.sdif.summ$term <- row.names(df.rs.brm.priorManip.sdif.summ)

brm.table1 <- xtable::xtable(df.rs.brm.priorManip.sdif.summ %>%
  mutate(coefficient = factor(term, 
                              levels = c("Intercept", paste("dc", seq(1,9), sep ="")),
                              labels = c("Intercept", 
                                         "0/25 vs. {25/50, 0/50}",
                                         "25/50 vs. 0/50",
                                         "{0/25, 25/50, 0/50} vs. {25/75, uniform}",
                                         "25/75 vs. uniform",
                                         "{25/75, uniform} vs. 0/75",
                                         "0/75 vs. {25/100, 50/100}",
                                         "25/50 vs. 50/100",
                                         "{25/100, 50/100} vs. {75/100, 0/100}",
                                         "75/100 vs. 0/100")),
         prediction = c("", ">", "=", ">", "=", ">", ">", "=", ">", "=")) %>%
      mutate(credible_interval = paste(
      "[", format(l.95..CI, digits = 2), ", ",
      format(u.95..CI, digits = 2), "]", sep =""
    )) %>%
    select(coefficient, prediction, Estimate, credible_interval),
  caption = "Regression model fits for planned comparisons. Predictions are based on whether the 95\\% credible intervals for the generics model prediction overlap.")



print(brm.table1, type="latex", comment = F, table.placement = "H", size="\\fontsize{9pt}{10pt}\\selectfont", include.rownames=FALSE)
```


<!-- The generics model predicts that the *weak or half* and the *rare half* distributions will receive a higher implied prevalence than the *rare weak* distribution. This prediction is also made by the "not rare" model, though that model also predicts that the  *rare half* distribution receives a stronger interpretation that the *weak or half* distribution. As predicted by the generics model, the *weak or half* distribution received significantly stronger interpretations than the *rare weak* distribution ($\beta = `r rs.lm.priorManip.contrast1.summ[["coefficients"]][["distributionweak_or_half", "Estimate"]]`$, $SE=`r rs.lm.priorManip.contrast1.summ[["coefficients"]][["distributionweak_or_half", "Std. Error"]]`$, $t = `r rs.lm.priorManip.contrast1.summ[["coefficients"]][["distributionweak_or_half", "t value"]]`$, $p = `r rs.lm.priorManip.contrast1.summ[["coefficients"]][["distributionweak_or_half", "Pr(>|t|)"]]`$) as did the rare or half distribution ($\beta = `r rs.lm.priorManip.contrast1.summ[["coefficients"]][["distributionrare_half", "Estimate"]]`$, $SE=`r rs.lm.priorManip.contrast1.summ[["coefficients"]][["distributionrare_half", "Std. Error"]]`$, $t = `r rs.lm.priorManip.contrast1.summ[["coefficients"]][["distributionrare_half", "t value"]]`$, $p = `r rs.lm.priorManip.contrast1.summ[["coefficients"]][["distributionrare_half", "Pr(>|t|)"]]`$). -->
<!-- The *rare half* distribution was not significantly different from the *weak or half* distribution ($\beta = `r rs.lm.priorManip.contrast2.summ[["coefficients"]][["distributionrare_half", "Estimate"]]`$, $SE=`r rs.lm.priorManip.contrast2.summ[["coefficients"]][["distributionrare_half", "Std. Error"]]`$, $t = `r rs.lm.priorManip.contrast2.summ[["coefficients"]][["distributionrare_half", "t value"]]`$, $p = `r rs.lm.priorManip.contrast2.summ[["coefficients"]][["distributionrare_half", "Pr(>|t|)"]]`$). -->
 
<!-- All models predict that the *uniform* distribution will receive higher ratings than both the *weak or half* and the *rare half* distributions.  -->
<!-- The *weak or strong* distribution is also predicted to be greater than *weak or half* or the *rare half*, by all models except the "not absent" model, which predicts no difference for this comparison.  -->
<!-- In fact, both the *uniform* ($\beta = `r rs.lm.priorManip.contrast3.summ[["coefficients"]][["distributionuniform", "Estimate"]]`$, $SE=`r rs.lm.priorManip.contrast3.summ[["coefficients"]][["distributionuniform", "Std. Error"]]`$, $t = `r rs.lm.priorManip.contrast3.summ[["coefficients"]][["distributionuniform", "t value"]]`$, $p = `r rs.lm.priorManip.contrast3.summ[["coefficients"]][["distributionuniform", "Pr(>|t|)"]]`$) and the *weak or strong* ($\beta = `r rs.lm.priorManip.contrast3.summ[["coefficients"]][["distributionweak_or_strong", "Estimate"]]`$, $SE=`r rs.lm.priorManip.contrast3.summ[["coefficients"]][["distributionweak_or_strong", "Std. Error"]]`$, $t = `r rs.lm.priorManip.contrast3.summ[["coefficients"]][["distributionweak_or_strong", "t value"]]`$, $p = `r rs.lm.priorManip.contrast3.summ[["coefficients"]][["distributionweak_or_strong", "Pr(>|t|)"]]`$) distributions received significantly greater implied prevalence than the *weak or half* distributions, providing some evidence against the "not absent" model.  -->

 <!-- [n.s.] -- [weak_or_strong, uniform] vs.  rare_strong -->
<!-- The *rare or strong* distribution was predicted (by most models) to receive stronger interpretations than either the *weak or strong* and/or the *uniform*.  -->
<!-- Contra these predictions, such a difference was not observed in the empirical data -->


<!-- - Some sort of regression tests to see the test the following infleunces: -->
  <!-- - The type of the weaker distribution and the type of the stronger distribution? -->

The computational models we articulate do more than just predict the *mean* implied prevalence; they predict the full distribution of responses.
The model fits in terms of variance-explained and mean squared errors for the full distribution of responses in shown in Table 2.
Unlike in Expts. 1 and 2, it is not obvious which of these models accounts best for the data. 
To quantitatively compare the models in their ability to predict the empirical distributions of responses for these ten different conditions, we computed the likelihood of the data under each model by discretizing the empirical distributions and model predictions into ten equally spaced bins.
<!-- \ndg{also report correlation and MSE as before, or say why we don't do so. for that matter, we should say why we didn't do BFs for earlier expts?} -->
As is evident from Figure\ \@ref(fig:priorManipulationResults)A (bottom row, "data"), however, a number of participants responded that 0% of Ks had the property. 
Examining these participants' explanations revealed that the majority of these respondents believed they were answering a question more akin to the prior elicitation / manipulation check task: Predict the next animal. 
This is a source of noise in the data and one that affects all models (execept the prior only model) to an equal degree. 
All of the models we articulate (the uncertain threshold and the fixed threshold models) have no way to account for 0% responses, which is literally impossible given the utterance of the form "Ks F". 
To compute the likelihood of the complete data set under these models, we make the further assumption that the true generative process of the data is a mixture of responding according to the model and responding according to the prior. 
We calculate Bayes Factors assuming a uniform distribution of noise between 0-20% (approximated using the following discretization $= \{0.001, 0.01, 0.05, 0.1, 0.15, 0.20\}$). 
To account for uncertainty in the measurement of the prior, we again bootstrap the model predictions by resampling the prior.
As if shown in Table 2, the uncertain threshold model is by far the best model at predicting these data.

<!-- Since the models have no free parameters, the ratio of these likelihood values corresponds to the *Bayes Factor* (BF), which quantifies the evidence in favor of one model over another.  -->



<!-- For all noise probabilities, the uncertain threshold model is preferred over each of the fixed threshold models (Table 2 shows the BFs assuming a noise parameter of 0.05).  -->
<!-- In comparison to the prior only model, however, the uncertain threshold is equally as good at predicting the data with a noise parameter of 0.01, and the prior is the preferred model with noise parameters smaller than 0.01.  -->
<!-- This is unsurprising given that the uncertain threshold model cannot predict responses of exactly 0% prevalence, and decreasing the amount of assumed noise further penalizes the model for all the 0% responses. -->
<!-- The important result is that given even a little bit of noise (between 1-5% of responses), the uncertain threshold model is quantitatively the better model. -->

<!-- \ndg{shouldn't we be treating this noise as a param for BDA and integrating it out? (that should be easy if you just treat the noise vals you ran as a discrete approx.) it would simplify the explanation, since no need to talk about different noise levels...} -->

<!-- For all noise probabilities greater than 0.01, the uncertain threshold model is the preferred model by  -->
<!-- The conclusions derived from the Bayes Factors are unchanged under different noise probabilities.    -->

```{r bayes factors, results="asis"}
load("cached_results/genint_manipPriors_bf.RData") # model.likelihoodRatios.summarized




tab1 <- xtable::xtable(
  left_join(
     left_join(
      md.pm.int.3.filtered.expvals.bs.summary.wide %>%
      group_by(model) %>%
      summarize(`expected value statistics` = paste(
        "r\\textsuperscript{2}","(", n(), ") = ", format(cor(model_prediction, mean)^2, digits = 2),
        "; MSE = ", format(mean((model_prediction - mean)^2), digits = 3), sep = "")
    ),
    md.pm.int.3.filtered.dists.bs.summary.wide %>%
      group_by(model) %>%
      summarize(`full distribution statistics` = paste(
        "r\\textsuperscript{2}","(", n(), ") = ", format(cor(model_mean, data_mean)^2, digits = 2),
        "; MSE = ", format(mean((model_mean - data_mean)^2), digits = 3), sep = "")
    )) %>% ungroup() %>%
    mutate(model = ifelse(model == "fixed_0.0175", "fixed_0.05", model)), 
  model.likelihoodRatios.summarized %>%
      group_by(alternative_model) %>%
      summarize(expected_log_bf = log(mean(exp(expected_log_bf))),
            lower_log_bf =  log(mean(exp(lower_log_bf))),
            upper_log_bf =  log(mean(exp(upper_log_bf)))) %>% 
      ungroup() %>% rename(model = alternative_model)) %>%
      filter(model %in% c("uncertain", "prior", "fixed_0.05", "fixed_0.125", "fixed_0.375")) %>%
    mutate(`Model` = factor(model, levels = c("prior", "fixed_0.05",
                                              "fixed_0.125", "fixed_0.375", "uncertain"),
                                    labels = c("Prior", 
                                               "Threshold = 0.01",
                                               "Threshold = 0.1",
                                               "Threshold = 0.35",
                                               "Uncertain threshold")),
    `log Bayes Factor` = paste(
    round(-expected_log_bf, 1), " (", round(-lower_log_bf,1), ", ", round(-upper_log_bf,1), ")", sep=""
  )) %>% 
    mutate(`log Bayes Factor` = ifelse(Model == "Uncertain threshold", "0", `log Bayes Factor`)) %>%
    
    select(`Model`, `log Bayes Factor`, `expected value statistics`, `full distribution statistics`),
  caption = "Summary statistics for alternative generic interpretations. (Log) Bayes Factors quantify evidence in favor of each model in comparison to the uncertain threshold generics model. Numbers less than 0 indicate evidence in favor of the uncertain threshold model. Summary statistics disaplyed for the model fits for the expected values (means) of the distributions and the full (discretized) distributions.")

print(tab1, type="latex", comment = F, table.placement = "H", size="\\fontsize{9pt}{10pt}\\selectfont",
      sanitize.text.function = identity, include.rownames=FALSE)
```


<!-- In addition to the qualitative analyses afforded by the regression analysis, we examine the generic interpretation model's *a priori* quantitative predictions and compare those to a set of alternative models.  -->
<!-- The first alternative model we consider is prevalence prior; we have already seen via the regression analyses that this will not be sufficient.  -->
<!-- We also consider three fixed threshold models which have increasing sophisticating as to their knowledge of the prior distributions: a literal "some" model (fixed threshold at the lowest possible value), a "not absent" model where the fixed threshold is placed in between the "absent" distribution and the "weak distribution" (threshold $\sim 10\%$), and a "highest mode" model where the fixed threshold is placed, in a context-sensitive manner, in between the two component distributions thus always signalling the higher of the two.  -->
<!-- Finally, we have our uncertain threshold model, which integrates the prevalence prior with the pressure from the literal semantics that favors higher prevalences. -->
<!-- Predictions of these models for the ten distributions of interest are shown in \red{Figure X}. -->




# General Discussion

<!-- - is there a way to connect to the claims of Cimpian2009 about generics influencing feature-as-cause vs. feature-as-effect explanations? -->
  <!-- - perhaps not due to the generic vs. specific distiction, but to prior beliefs about the property? -->
  
<!-- Further, the existence of property-sensitive interpretations has been used as evidence against a quantitative account of generic language *per se* and it has been suggested that the normal tools of formal semantics are inappropriate for studying generics [@Leslie2008]. -->
<!-- \mht{not sure if we want to take up the previous point to add to the contributions of this paper} -->

<!-- Much of what we come to learn about the world comes from other people, often expressed in language. -->

Generic language is the foremost case study of how abstract, generalizable knowledge is transmitted in language, and it is often thought that generics carry strong interpretations (analogous to the quantifier "most" or "all").
Despite its ubiquity and relative morphosyntactic simplicity, there have been few quantitative studies of generics and no quantitative models that make predictions about how generic language updates beliefs.
Here, we tested a quantitative model of generic interpretations of a broad set of stimuli, including a replication data set from @Cimpian2010, and show that the generic interpretations can be predicted with high-quantitative accuracy as a function of background knowledge about the property. 
The model could accurately predict which generic statements would carry the weakest interpretations.
<!-- Because generic interpretations are heavily sensitive to background knowledge, generics can carry weak interpretations. -->
<!-- We also find that generics can carry weak interpretations, when background knowledge would make a strong interpretation implausible. -->
<!-- We find reliable fine-grained differences in interpretations across properties, which only our uncertain threshold model can account for. -->
This work, thus, provides the computational formalism necessary to describe how beliefs are updated from generic language.

Other theories of generic language make use of a mechanism by which the domain over which the prevalence of the feature in the category is calculated is contextually restricted [e.g., @Cohen1999; @Declerck1991].
In such a theory, the statement "Lorches have a menstrual cycle" gets evaluated as "Female lorches have a menstrual cycle"; under such an account, the prevalence of the feature would be 100% (or near 100%) because 100% of the *relevant lorches* (i.e., the females) have a menstrual cycle.
Interestingly, domain restricted interpretations are present in the empirical data.
Several properties about the reproductive behavior of animals (Expt. 2b) have interpretation distributions that are bimodal. 
For example, "Morseths have a menstrual cycle" is interpreted primarily as applying to 50% of morseths (`r sum(with(filter(df.int.filtered, property == "have a menstrual cycle"), ((response < 0.55) & (response > 0.45))))` out of `r length(with(filter(df.int.filtered, property == "have a menstrual cycle"), response))` give a response between 45% and 55%); however, some participants (`r sum(with(filter(df.int.filtered, property == "have a menstrual cycle"), response ==1 ))` of `r length(with(filter(df.int.filtered, property == "have a menstrual cycle"), response))`) rate this as applying to 100% of morseths.
<!-- \ndg{move this to a discussion section:} -->
This behavior could result from a participant interpreting the question as pragmatically restricting the domain to only the members of that category that *could* have the property (e.g., 100% of female morseths have a menstrual cycle).
The domain restricted interpretation is not limited to the generic interpretation data, however.
We notice this bimodal interpretation in our prevalence elicitation task (Expt. 2a) as well: The distribution over several of the reproductive properties is tri-modal, with peaks at 0% (the animals that don't have a menstrual cycle), 50% ("only females") and 100% (perhaps, "all females").
The fact that this multi-modality appears in the prior elicitation task means that the generic interpretation model predicts bi-modal interpretation distributions for the implied prevalence data, which is what we observe.

In what follows, we defuse a concern for circularity in our modeling framework, describe how conceptual knowledge can guide prevalence-based interpretations, discuss how our answer to the problem of generic interpretation can inform an answer to the parallel problem of *generic identification*, and speculate about the implications for communicating weak generics.

\ndg{i'm not so sure about including these following discussion sections. they seem like interesting but only thematically related, as apposed to being crucial to our story or responses to probably objections. i didn't comment / edit them yet -- let's first decide if they stay.}


## The relationship between prevalence priors and generic interpretations

Across our three experiments, we measured participants' background knowledge about the property using knowledge elicitation tasks.
These background knowledge elicitation tasks involve reasoning about alternative categories of animals.
Conveying the instructions and questions of such prior elictation tasks require using language. 
Thus, there is the potential for circularity in our argument: We are predicting beliefs updated from language via beliefs measured using language.

Consider first the nonparametric elicitation task of Expt. 2a. 
Here, we asked participants to generate different animal categories and later rate prevalence for different properties for those animal categories.
It is possible that participants answer the prevalence question by first asking themselves a generic question (e.g., "Do dogs develop phobias?") and then rating their personal generic interpretation prevalence if the answer to the generic question is yes and rating 0% prevalence if the answer to the generic question is no.
If this were so, however, the predictions of the "some" model (fixed-threshold at 0% prevalence) would predict the generic interpretation data well, by ruling out the 0% component of the distribution.
The fact that the "some" model consistently underpredicts the generic interpretation data argues against the circularity in our measurements of the prevalence prior and generic interpretations.

A similar argument can be made for the structured elicitation task in Expt. 1a.
In Expt. 1, we assumed a particular model of the prevalence prior (i.e., a mixture of Betas) and elicited participants' knowledge about the property using questions that we assumed tapped into this structure. 
One question concerned the probability that a kind would have 0% prevalence of the feature (or, equivalently, the proportion of categories for whom the property is expected to be present at some non-zero level of prevalence) by asking "How likely is it that *there is a K with F*?"
Intuitively, the response to this question should be very high for properties that exist in many categories (e.g., *is female*) and low for properties that only exist in a few categories (e.g., *has purple feathers*).
The second question concerned the shape of the conditional, non-zero distribution of prevalence; this was measured by asking "*Suppose there is a K with F*, how many Ks do you think have F?".
This question measures the projectibility of the property given a single, positive exemplar.
Thus, the predictions of the alternative, fixed-threhsold "some" model (which rules out 0% prevalence) for this experiment correspond to the inferences upon learning that *at least one member of the category has the property*.
In Expt. 1, we again find the generic interpretation data are distinct from those of the conditional, non-zero distributioun of prevalence, as evidenced by the "some" model comparisons.
<!-- Learning from a generic carries stronger interpretations than just learning the existential information that a property exists in the category. -->
<!-- are derived from the background knowledge in the correct way: They  -->

The patterns of data we observe in our three generic interpretation experiments are additionally unlikely to be the same as if participants heard "Some Ks have F" rather than "Ks have F".
Though we did not empirically measure judgments given the existentially quantified statements, the alternative model that assumes a fixed-threshold at 0%-prevalence provides insight into what should be expected for those data.^[
  Recall the fixed-threshold models are "literal interpretation" models and do not compute scalar implicatures.
]
Across our three experiments, we found that the "some" model provided too weak of interpretations, consistent with the intuition that generic statements convey stronger prevalence implications that the existential statement.

\ndg{people may worry about circularity of argument, given rich background knowledge elicitation that also uses language (similar to ellen's point). i think we should discuss this directly. relatedly we should discuss the implications of our structured background knowledge (elicitation and results).}
\mht{does that address it?}

<!-- - Finer points about the data? Discussion of explanation data? Have relationship to DR theories come here? -->

## Conceptual generic interpretations

In this paper, we tested a particular model of generic interpretation that uses a prior distribution over the prevalence of a feature across relevant categories and assumes the truth-functional meaning of the generic is an uncertain threshold on the prevalence. 
The prevalence prior distributions, which we elicit from participants, are likely influenced by the conceptual knowledge of our participants.
For example, the prevalence priors over properties that have to do with reproduction (e.g., *have menstrual cycles*, *get erections*) are multi-modal with one mode around 50%, clearly reflecting participants' knowledge that these properties are specific to one sex of the animal.
The uncertain threshold model predicts that generics about these properites should be imply roughly 50% have the feature (Figure\ \@ref(fig:modelSimulations)).
Thus, though we do not explicitly model conceptual knowledge *per se*, this behavior is consistent with a richer, conceptual-informed interpretation (e.g., *female morseths have menstrual cycles*).^[
  The scientifically correct term for this is actually an "estrous cycle". We are grateful to one of our MTurk participants for pointing this out to us. 
]

Indeed participants describe conceptually-informed interpretations in their explanations for low-prevalence ratings, revealing aspects of their intuitive theories which guide their judgments.
One participant wrote: "About half are females and females have menstrual cycles."
Another: "I assumed that only a percentage of Moxes were female and young enough to have a menstrual cycle."
A typical explanation of a participant's response to *Dobles live in zoos* was "I thought that there would be many more Dobles in the wild than in zoos. This is true of most animals in zoos today".
Here, it is clear that the participant is using their knowledge of the property, derived from other animals, to learn about the category.
Participants often wrote about the lack of an enabling causal situation when describing their weak interpretations: "Most frams don't have access to nicotine."
Explicitly modeling the intuitive theories that give rise to the intuitions about prevalence is an obvious future direction of this work.

<!-- Our model restricts the domain by reasoning about a threshold that would make sense for that particular property, given its background distribution on prevalence.  -->
<!-- Reasoning about an uncertain threshold via background knowledge is one mechanism by which the domain can be restricted. -->


<!-- Indeed, this kind of conceptual knowledge is present in our participants, as evidence by their explanations. -->






<!-- From a purely theoretical perspective, domain restriction is an attractive mechanism because it would allow the semantic theory to be a context-invariant fixed threhsold [e.g., at 50%; @Cohen1999]. -->
<!-- However, such a theory still needs to explain why and formalize how the domain gets restricted; without such a formal account to accompany the domain restriction hypothesis, the hypothesis explains but does not predict the data. -->
<!-- The uncertain threshold model that we present here can be seen as a particular instantiation of a domain restriction theory.  -->
<!-- In our model, the statement "Lorches have a menstrual cycle" is resolved by a literal interpretation model to mean mean "50% of lorches have a menstrual cycle". -->
<!-- Were a listener to have the background theory that the reason why half of a category would have such a property is for reproductive purposes, the listener's interpretation would most naturally be expressed as "Female lorches have a menstrual cycle". -->


## Generic identification

Though often interpreted as generics, bare plural sentences (e.g., "Dogs bark") can also manifest as *non-generics* (e.g., "Dogs are on my front lawn").
Figuring out when a sentence expresses a generic meaning vs. a non-generic meaning is called the problem of generic identification and is a parallel challenge to the problem of generic meaning [@Carlson1995].
Our answer to the question "what do generics mean?" involves vagueness concerning the prevalence, which recruits beliefs about the property in question.
The properties themselves may involve vagueness in terms of genericity (or its event counterpart: habituality) such as *barks*: How often does an individual dog need to bark in order to qualify as a thing that barks?
@TesslerLangGenUnderReview found that the same uncertain threshold mechanism explains graded endorsements of habitual statements like "John's dog barks".

The habituality of the predicate may actually be the source of the perceived generic/non-generic distinction. 
For instance, "Dogs are on my front lawn" exhibits only a single generalization (e.g., over *dogs*); it is not a habitual predicate like *barks*.
The habituality of the verb may influence the expected prevalence in the head noun category: A more vague, habitual predicate may apply to more instances of the category (e.g., it's comparatively easy to tell whether or not a dog is on your front lawn, but harder to tell whether or not an animal barks *habitually*).
For non-habitual predicates, the expected prevalence would be substantially more restricted. 
Thus, we may find continuity in interpretations of underspecified noun phrases, including so-called "non-generics": "Tigers have stripes" has higher implied prevalence than "Tigers are in the savanna" which is higher than "Tigers are in zoos", "Tigers are in my local zoo", and "Tigers are on my front lawn".
An uncertain threshold mechanism of the kind we have posited here may be such a way as to pragmatically infer a continuum of interpretations, from generics that are interpreted as universals ("Tigers are mammals") to those that are interpreted existentially but habitually ("Tigers are in zoos") to those that are interpreted existentially and non-habitually ("Tigers are on my front lawn").
Deriving such a prediction would necessarily involve a model of compositional generic interpretation, in which a habitual predicate meaning can be resolved jointly with a generic subject.

<!-- Interpreting the uncertain threshold as a kind of domain restriction might be sufficient to extend the model to interpreting "non-generic" bare plurals (e.g., "Dogs are on my front lawn"). -->

<!-- First, let us note that many generics actually expressed two or more generalizations.  -->
<!-- For example, "Lorches eat insects" says that $[gen \text{ lorches}] [hab \text{ eat}] [gen \text{ insects}]$. -->
<!-- <!-- In this paper, we have looked at the first aspect of generic understanding, the generalization over the head noun category (e.g., lorches) though in previous work we have shown that the same uncertain threshold model can explain habitual language as well [e.g., "John smokes"; @TesslerLangGenUnderReview]. --> -->
<!-- In this paper, we have looked at the first aspect of generic understanding, the generalization over the head noun category (e.g., lorches) though in the next chapter we will see that the same uncertain threshold model can explain habitual language as well (e.g., "John smokes"). -->

<!-- An old intuition with generics is that at least some express properties that are especially timeless and enduring [@Lyons1977; @Gelman2003; @Gelman2007], though it is not clear what generalization this should be attributed to.  -->



## Implications for stereotype propogation

The experimental data we present provides strong evidence for the existence of "weak generics", which we operationalize here as generic statements that imply a prevalence less than 50%. 
Statements like "Lorches live in zoos", "Feps perform in the circus", and "Wugs have seizures" all received average implied prevalence ratings below 50%, with many individual participants providing ratings of 10% or less (Expt. 2b).
When manipulating the prevalence prior distributions to suggest only prevalence levels of around 0% or aroud 25%, participants interpret the statement "Ks know when earthquakes are about to happen" to mean about 25% (Expt. 3b). 
This is an aspect of generic language understanding often swept under the rug: Generics are believed to (in a generic sense) carry strong implications.
Here, we show that generics also carry weak implications.

Adults readily use their causal knowledge of the world to restrict the interpretation of a generic statement to a reasonable population, as evidenced by their explanations (e.g., "I thought that there would be many more Dobles in the wild than in zoos").
At the same time, the uncertain threshold mechanisms encodes a pressure for higher prevalence interpretations (e.g., without strong prior knowledge, generics imply high prevalence).
Thus, listeners who do not have the substantial prior knowledge to restrict an interpretation of generics to a weak interpretation (e.g., young children) might derive a high-prevalence interpretation and furthermore posit abstract relations that would make a high-prevalence interpretation more likely.
For example, upon learning "Dobles live in zoos", a naive learner might infer that there is something about Dobles that causes them to live in zoos [cf., @Prasada2013]. 
This is potentially problematic for language about social categories (e.g., "Tall people are good at basketball") for which an adult speaker might wish to convey a relatively low prevalence interpretation (e.g., *some tall people...* because most people are not good at basketball) but which a naive listener might derive a higher prevalence interpretation.
This points to an aspect of generic meaning that might differ between adults and children: Whether or not children understand weak generics.

<!-- It is often argued that children have adult-like understanding of generics from a very young age . -->
<!-- These studies often look at a small range of properties that do not exhibit much context-sensitivity.  -->
<!-- It is an open-question whether or not children understand "weak generics". -->

<!-- There are theoretical reasons to think that the understanding of weak generics may be later developing.  -->
<!-- Prevalence priors are naturally modeled as Beta distributions, which are probability distributions over numbers ranging from 0 - 1: In other words, Beta distributions are probability distributions over probabilities.  -->
<!-- These probabilities can be thought of as the weight of a biased coin, and a common interpretation of the parameters of the Beta distribution are as *pseudo-counts*, imaginary outcomes of a previous experiment of flipping the coin. -->
<!-- For example, a Beta(1, 9) distribution describes beliefs about the weight of the coin upon observing 1+9 = 10 flips of that coin, 1 of which landed on heads and 9 of which landed on tails.  -->
<!-- This probability distribution heavily favors numbers around 0.1, as a coin of that weight is most likely to have generated the observed 1 out of 10 heads.  -->

<!-- If we take the pseudo-counts as indices of worldly experience, it is interesting to note what happens as the pseudo-counts approach 0.  -->
<!-- As the parameters approach zero, the Beta probability distribution increasi -->
<!-- ngly prefers extreme values: 0 or 1.  -->
<!-- If our knowledge about predictive probabilities are represented by Beta distributions, then early on, our belief distributions would favor categorical thinking.  -->
<!-- However, once we start to learn about different kinds of categories and properties, probably via labeling, we may begin to represent multiple distributions in our prevalence priors.  -->
<!-- Such a development would predict that children start out interpreting all generics as strong generics, and that the understanding of weak generics is later developing ability. -->





<!-- ## Implications for social categories -->


<!--   - since properties tend to be rare of objects (e.g., Oaksford & Chater wason), false-positives are not as bad as false-negatives (from a purely informational standpoint, because false-negatives are less likely? because most things are going to be correct rejections?) -->
<!--   - howver, for social categories this can be bad, as social categories are socially-constructed, reflecting what the speaker believes is a relevant categorization to make (Foster-Hansen, maybe Steve Roberts?) -->
<!-- - does this *strong interpretations before weak interpretations* relate at all to Gelman & Bloom's developmental changes? -->

## Conclusion

Abstract knowledge is transmitted via generic statements but heretofore no quantitative models have accounted for this belief updating processs.
The uncertain threshold model is able to predict the large variability in generic interpretations, even predicting the existence of "weak generics", or generics that only apply to a minority of the category.

\newpage

# References 

<!-- \setlength{\parindent}{-0.1in}  -->
<!-- \setlength{\leftskip}{0.125in} -->
<!-- \noindent -->

<div id = 'refs'></div>

\newpage

```{r child = 'appendix_items.Rmd'}
```
