---
title: "CBG replication and extension"
output: html_notebook
---



```{r}
library(rwebppl)
library(tidyverse)
library(tidyboot)
library(knitr)
library(ggpirate)
library(viridis)
```

## Load data

```{r}
df.c.prior <- read_csv("../data/asymmetry/asymmetry-prior-4-trials.csv")

df.c.int <- read_csv("../data/asymmetry/implied-prevalence-2-trials.csv") %>%
  group_by(workerid) %>%
  mutate(normalizedResponse = (response - mean(response)) / sd(response))
```

## Interpretation data

```{r fig.height = 5}
df.c.int.bs <- df.c.int %>%
  group_by(stim_property) %>%
  tidyboot_mean(column = response)

df.c.int %>%
  mutate(stim_property = factor(stim_property, 
                           levels =  with(df.c.int.bs, stim_property[order(mean)]))) %>%
  ggplot(., aes( x = stim_property, y = response, color = stim_property))+
  geom_pirate(bars = F, violins = F, width_points = 0.2)+
  coord_flip()+
  scale_color_viridis(discrete = T)+
  ylim(0, 1)
```
```{r}
df.c.int.bs %>%
  ggplot(., aes(x = mean))+
  geom_histogram( binwidth = 0.075)
```

## Linear model: Interpretation ~ two prior questions

Summarized prevalence prior questions

```{r}
df.c.prior.bs <- df.c.prior %>%
  gather(key, val, response0, response1) %>%
  mutate(key = factor(key, levels = c("response0", "response1"),
                labels = c("mixtureParam","prevalenceWhenPresent")),
         stim_type = ifelse(stim_type == "disease", "accidental", stim_type)) %>%
  group_by(stim_type, stim_property, key)  %>%
  tidyboot_mean(column = val)


df.c.prior.bs.wide <- left_join(
  df.c.prior.bs %>%
    filter(key == "mixtureParam") %>%
    rename(mixture_lower = ci_lower,
           mixture_mean = mean,
           mixture_upper = ci_upper) %>%
    select(-empirical_stat, -key),
  df.c.prior.bs %>%
    filter(key == "prevalenceWhenPresent") %>%
    rename(pwp_lower = ci_lower,
           pwp_mean = mean,
           pwp_upper = ci_upper) %>%
    select(-empirical_stat, -key)
)
```

Scatterplot of two prevalence questions

```{r}
ggplot(df.c.prior.bs.wide %>%
         mutate("Property type" = factor(stim_type,
                                         levels = c("part",
                                                    "vague",
                                                    "color",
                                                    "accidental"),
                                         labels = c("body part",
                                                    "color adj + part",
                                                    "gradable adj + part",
                                                    "accidental"))), 
       aes( x = mixture_mean, xmin = mixture_lower, xmax = mixture_upper,
            y = pwp_mean, ymin = pwp_lower, ymax = pwp_upper,
            fill = `Property type`))+
  geom_errorbar(alpha = 0.3) + geom_errorbarh(alpha = 0.3) + 
  geom_point(shape = 21, size = 2.6, color = 'black')+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  ylab("Prevalence when present")+
  xlab("P(feature is present)")

```



## Load model results

```{r}
model.path <- "../models/results/"

model.prefix <- "pilot-results-cimpian-L0-structuredPrior_uncertain-semantics_25000_burn12500_lag2_chain1"
m.samp <- read_csv(paste(model.path,model.prefix,".csv", sep = ""))

# model.files <- list.files(
#   path = model.path, 
#   pattern = paste(model.prefix, n_samples, "_burn", n_burn, 
#                   "_lag", lg, "_chain", sep = "")
#   )
# m.samp <- data.frame()
# for (modfile in model.files){
#   m.item <- read_csv(paste(model.path , modfile, sep = ""))
#   
#   m.samp <- bind_rows(
#     m.samp,
#     m.item %>% mutate(chain = match(modfile, model.files))
#   )
#     
# }
```

### Null distribution parameters

```{r}
m.samp %>%
  filter(param == "nullParams") %>%
  ggplot(., aes( x = val))+
  geom_histogram()+
  facet_wrap(~category, scales = 'free')

ggsave(paste("figs/", model.prefix, "nullDistParams.pdf", sep = ""),
       width = 4, height = 4)
```


#### Forward sample prevalence priors

Add iteration number back in.

```{r}
m.samp.iter <-   m.samp %>% 
  filter(param %in% c("mixtureParam", "prevWhenPresent")) %>%
  mutate(parameter = paste(type, param, property, category, sep = "_")) %>%
  select(-type, -param, -property, -category) %>%
  group_by(parameter) %>%
  mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
  ungroup() %>%
  separate(parameter, into = c("parameter", "componentID", "property", "componentParam"), sep= "_")

m.rs.prior.parameters <- m.samp.iter %>% 
  mutate(componentParam = paste(componentParam, "_", componentID, sep = "")) %>% select(-componentID) %>%
  spread(componentParam, val) %>%
  rowwise() %>%
  mutate(
    prevWhenPresent = rbeta(shape1 = alpha_prevWhenPresent,
                            shape2 = beta_prevWhenPresent, 
                            n = 1),
    mixtureParam = rbeta(shape1 = alpha_mixtureParam,
                            shape2 = beta_mixtureParam, 
                            n = 1),
    isPresent = rbinom(n = 1, prob = mixtureParam, size = 1),
    prevalence = ifelse(isPresent == 1, prevWhenPresent, 
                        rbeta( shape1 = 1, shape2 = 200, n = 1) )
    )
```


### Prevalence prior parameters

```{r gen-prevpriorParams-cdf, fig.width = 8, fig.height = 5}
md.prevPriorParams <- bind_rows(
  df.c.prior %>% 
    gather(param, val, response0, response1) %>%
    mutate(param = factor(param, levels = c("response0", "response1"),
                          labels = c("mixtureParam", "prevWhenPresent"))) %>%
    select(stim_property,param,  val) %>%
    mutate(src = 'data'),
  m.rs.prior.parameters %>% 
    gather(param, val, mixtureParam, prevWhenPresent) %>%
    select(property, param, val) %>%
    rename(stim_property = property) %>%
    mutate(src = 'model') 
  )


ggplot(m.rs.prior.parameters, 
       aes( x = val, color = src))+
    stat_ecdf()+
    facet_wrap(~stim_property + param)+
    scale_color_solarized()+
    scale_x_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
    scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
    theme(strip.text.y = element_text(angle = 0))
ggsave(paste("figs/", model.prefix, "prevPriorParamsCDFs.pdf", sep = ""),
       width = 14, height = 8)
```


### Reconstructed prevalence priors

```{r gen-prevalencepriors, fig.width = 8, fig.height = 5}
m.rs.prior.parameters2 <- left_join(
  m.rs.prior.parameters,
  df.c.prior.bs.wide %>%
    distinct(stim_property, stim_type) %>%
    rename(property = stim_property)
)  %>% mutate(stim_type= 
                factor(stim_type,
                       levels = c("part",
                                                    "vague",
                                                    "color",
                                                    "accidental"),
                                         labels = c("body part",
                                                    "color adj + part",
                                                    "gradable adj + part",
                                                    "accidental")))

example.properties.priors <- c(
  "claws",  "big claws",   "blue claws",   "worn-out claws", 
  "feathers","smooth feathers","purple feathers","torn feathers"
)

m.rs.priors.reconstructed.subset <- m.rs.prior.parameters2 %>%
         filter(property %in% example.properties.priors) %>% 
       mutate(property = factor(property,
                                levels = example.properties.priors))

ggplot(m.rs.priors.reconstructed.subset, 
       aes( x = prevalence,
                                    fill = stim_type))+
    stat_density ( aes(y = ..scaled.. ), color = 'black')+
    facet_wrap(~property, nrow = 2)+
    scale_x_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
    scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
    theme(strip.text.y = element_text(angle = 0))+
  guides(fill = F)

save(m.rs.priors.reconstructed.subset,
     df.c.prior.bs.wide, 
     df.c.int.bs,
     file = "../paper/cached_results/cimpian-prevPrior-interpretations")

# ggsave(paste("figs/", model.prefix, "prevPriorParamsCDFs.pdf", sep = ""),
#        width = 14, height = 8)
```

### Implied prevalence

```{r}

md.impprev <- left_join(
   m.samp %>%
    filter(type == "prediction") %>%
    rename(Parameter = category) %>%
    group_by(property, Parameter) %>%
    summarize(model_MAP = estimate_mode(val),
            model_upper = hdi_upper(val),
            model_lower = hdi_lower(val)),
  df.c.int.bs %>%
    ungroup() %>%
    rename(property = stim_property)
)
```

```{r}
ggplot(md.impprev, aes( x = model_MAP, xmin = model_lower, xmax = model_upper, 
                        y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_abline(intercept = 0, slope = 1, lty = 2)+
  geom_point()+
  geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)+
  facet_wrap(~Parameter)+
  scale_x_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
  scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
  coord_fixed()

ggsave(paste("figs/", model.prefix, "interpretationScatters.pdf", sep = ""),
       width = 6, height = 4)
```

```{r}
md.impprev %>%
  filter(!is.na(mean)) %>%
  group_by(Parameter) %>%
  summarize( mse  = mean((model_MAP-mean)^2),
             r2 = cor(model_MAP, mean)^2) %>% 
  kable()
```



