---
title: "Generics BDA"
output: html_notebook
---


```{r}
library(rwebppl)
library(tidyverse)
library(knitr)
```

```{r}
readData = function(folder, proj){
  read_csv(
    paste("../data/",folder, proj,"/",
          proj,"-trials.csv", sep = "")
    )
}

readCatchInfo = function(folder, proj){
  read_csv(
    paste("../data/",folder, proj,"/",
          proj,"-catch_trials.csv", sep = "")
    )
}

priorDataLabel = "prior-2"
interpretationDataLabel = "interpretation-4"
```

## Load data
Prior data

```{r}
df.prior <- readData("prior/", priorDataLabel)
df.prior.catch <- readCatchInfo("prior/", priorDataLabel)

df.prior.catch.summary <- df.prior.catch %>%
  group_by(workerid, tested_on) %>%
  summarize(totalCorrect = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, totalCorrect) %>%
  rename(correct_rejection = `0`, 
         hit = `1`) %>%
  mutate(pass = ifelse(hit >= 4 & correct_rejection >= 4, 1, 0),
         totalCorrect = correct_rejection + hit)

df.prior <- left_join(df.prior, df.prior.catch.summary %>%
                         select(workerid, totalCorrect, pass))

df.prior.filtered <- df.prior %>% 
  filter(pass == 1, trial_type == "prevalence_elicitation") %>%
  mutate(response = as.numeric(response))

```

Interpretation (posterior) data

```{r}
df.int.catch <- readCatchInfo("interpretation/", interpretationDataLabel)

df.int.catch.summary <- df.int.catch %>%
  group_by(workerid, tested_on) %>%
  summarize(totalCorrect = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, totalCorrect) %>%
  rename(correct_rejection = `0`, 
         hit = `1`) %>%
  mutate(pass = ifelse(hit >= 4 & correct_rejection >= 4, 1, 0),
         totalCorrect = correct_rejection + hit)

df.int <- readData("interpretation/", interpretationDataLabel) %>%
  group_by(workerid) %>%
  mutate(normalizedResponse = (response - mean(response)) / sd(response))

df.int <- left_join(df.int, df.int.catch.summary %>%
                         select(workerid, totalCorrect, pass))

df.int.filtered <- df.int %>% filter(pass == 1) %>%
  mutate(response = as.numeric(response))
```

## RSA/BDA Model

### RWebPPL model (not working)

rwebppl doesn't like returning supports with variable elements (this is because I'm inferring the number of components)

```{r}
rsa.bda.model <- '
var priorData = map(avoidEnds, data.prior)
var interpretationData = map(
  function(d){ return utils.closest( midBins.slice(1), d) }, 
  data.interpretation
)

// display(priorData)
// display(interpretationData)
var meaning = function(utt,state, theta) {
  return utt=="generic"? state > theta :
         true
}

var model = function(){

  var numberOfComponents = 3// poisson(1) + 1;

  var weights = normalize(repeat(numberOfComponents,
    function(){ return uniformDrift({a: 0, b: 1, width:0.2}) }
  ))

  var componentParameters = repeat(numberOfComponents,
   function(){
    return betaShape({
        g: uniformDrift({a: 0, b: 1, width: 0.2}),
        d: uniformDrift({a: 0, b: 100, width: 5})
      })
  })

	mapData({data: priorData}, function(d){
    var componentLogLikelihood = map2(function(w, params){
      Math.log(w) + Beta(params).score(d)
    }, weights, componentParameters)
    var scr = util.logsumexp(componentLogLikelihood)
    // console.log(scr)
		factor(scr)
	})

	var statePrior = Infer({model: function(){
    sample(DiscretizedBeta(componentParameters[discrete(weights)]))
	}});

	/// RSA model
	var listener0 = cache(function(utterance) {
	  Infer({model: function(){
	    var state = sample(statePrior), theta = sample(thetaPrior);
	    var m = meaning(utterance, state, theta)
	    condition(m)
	    return state
	 }})}, 10000)

   var interpretationPrediction = listener0("generic")

   mapData({data:interpretationData}, function(d){
     // display(d)
      var scr = interpretationPrediction.score(d)
      scr == -Infinity ? displayObj(d) : null
     // display(scr)
     // observe(interpretationPrediction, d)
   })

   // RECORD PARAMETERS AND PREDICTIVES
   // query.add(["numberOfComponents", -99, -99, -99], numberOfComponents)

   // foreach(_.range(numberOfComponents), function(i){
  //    query.add(["componentParameters", i, weights[i], componentParameters[i]["a"]], componentParameters[i]["b"]
     //)
   // })

  // query.add(["prediction", -99, -99, expectation(statePrior)], expectation(interpretationPrediction))

   var componentParams_obj = _.fromPairs(_.flatten(map(function(i){
   return [
      ["weight_"+ i, weights[i]],
      ["a_"+ i, componentParameters[i]["a"]],
      ["b_"+ i, componentParameters[i]["b"]]
    ]
   },_.range(numberOfComponents))))
  
  return extend({
    priorMean: expectation(statePrior), 
    posteriorMean: expectation(interpretationPrediction),
  }, componentParams_obj)

}
'
```

```{r}
all.properties <- unique(df.int.filtered$property)
n_samples <- 5000
n_burn <- n_samples / 2
wp.rs.predictives <- data.frame()
wp.rs.prior.parameters <- data.frame()

for (p in all.properties[1:10]){
  
  priorData <- filter(df.prior.filtered, property == p)$response
  interpretationData <- filter(df.int.filtered, property == p)$response

  dataToPass = list(prior = priorData, interpretation = interpretationData)
  
  wp.rs <- webppl(program_code = rsa.bda.model,
                packages = c("node_modules/utils"),
                data_var = "data", data = dataToPass,
                model_var = "model", 
                inference_opts = list(method = "MCMC",
                                      samples = n_samples,
                                      burn = n_burn,
                                      verbose = TRUE))
  

  wp.rs.predictives <- bind_rows(
    wp.rs.predictives,
    wp.rs %>% filter(Parameter %in% c("priorMean", "posteriorMean"))  %>%
      mutate(property = p)
  )
  
  wp.rs.prior.parameters <- bind_rows(
    wp.rs.prior.parameters,
    wp.rs %>% filter(!(Parameter %in% c("priorMean", "posteriorMean"))) %>%
      #separate(Parameter, sep = "_", into = c("parameter", "component")) %>%
      mutate(property = p) 
  )

  print(p)
}
```

#### Forward sample prevalence priors

```{r}
wp.rs.prior.parameters <- wp.rs.prior.parameters %>% 
  spread(Parameter, value) %>%
  rowwise() %>%
  mutate(component = LaplacesDemon::rcat(1, c(`weight_0`, `weight_1`, `weight_2`)) - 1,
         shape1_param = ifelse(component == 0, a_0, ifelse(component == 1, a_1, a_2)),
         shape2_param = ifelse(component == 0, b_0, ifelse(component == 1, b_1, b_2)),
         prev = rbeta(shape1 = shape1_param, shape2 = shape2_param, n = 1))
```

##### Marginal distributions on prevalence

```{r gen-prevprior-marginals, fig.width = 8, fig.height = 5}
md.prevpriors <- bind_rows(
  df.prior.filtered %>% 
    filter(property %in% levels(factor(wp.rs.prior.parameters$property))) %>%
    select(property, response) %>%
    rename(prev = response) %>% 
    mutate(src = 'data'),
  wp.rs.prior.parameters %>% 
    select(property, prev) %>%
    mutate(src = 'model') 
  )


ggplot(md.prevpriors , aes( x = prev, color = src))+
  geom_density(size = 1, aes( y = ..scaled.. ), adjust = 0.5)+
  facet_wrap( ~ property)+
  scale_color_solarized()+
  scale_x_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
  theme(strip.text.y = element_text(angle = 0))
```

##### Cumulative Density Functions

```{r gen-prevprior-cdf, fig.width = 8, fig.height = 5}
ggplot(md.prevpriors, aes( x = prev, color = src))+
    stat_ecdf()+
    facet_wrap(~property, nrow = 3)+
    scale_color_solarized()+
    scale_x_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
    scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
    theme(strip.text.y = element_text(angle = 0))
```

#### Implied prevalence

```{r}

md.impprev <- left_join(
  wp.rs.predictives %>%
    group_by(property, Parameter) %>%
    summarize(model_MAP = estimate_mode(value),
            model_upper = hdi_upper(value),
            model_lower = hdi_lower(value)),
  df.int.filtered %>%
    filter(property %in% levels(factor(wp.rs.predictives$property))) %>%
    group_by(property) %>%
    tidyboot::tidyboot_mean(column = response)
)

```

```{r}
ggplot(md.impprev, aes( x = model_MAP, xmin = model_lower, xmax = model_upper, 
                        y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_point()+
  geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)+
  facet_wrap(~Parameter)+
  scale_x_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
  scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
  coord_fixed()
```






## Load model results

```{r}
model.path <- "../models/results/"
#model.prefix <- "pilot-results-genint-L1-3Components_"
#model.prefix <- "pilot-results-genint-L0-3Components_fixed-semantics_"
#model.prefix <- "pilot-results-genint-L1-3Components_fixed-semantics_"
#model.prefix <- "pilot-predict-results-genint-L0-3Components_uncertain-semantics_"
n_samples <- 250000
n_burn <- n_samples / 2
lg <- 75
chain <- 1

model.files <- list.files(
  path = model.path, 
  pattern = paste(model.prefix, n_samples, "_burn", n_burn, 
                  "_lag", lg, "_chain", sep = "")
  )
m.samp <- data.frame()
for (modfile in model.files){
  m.item <- read_csv(paste(model.path , modfile, sep = ""))
  
  m.samp <- bind_rows(
    m.samp,
    m.item %>% mutate(chain = match(modfile, model.files))
  )
    
}
```

```{r}
m.samp <- read_csv(paste(model.path,
                         "hmc/pilot-results-genint-L1-3Components_hmc1000_burn500_stepSize0.000025_steps5_chain10.csv", sep = ""))

m.samp <- get_samples(m.samp, 1000)
```



### Speaker optimality parameter

```{r}
m.samp %>%
  #filter(type == "parameter") %>%
  filter(parameter == "speakerOptimality") %>%
  ggplot(., aes( x = val ))+
  geom_histogram()#+
  #facet_wrap(~chain, scales = 'free')

# ggsave(paste("figs/", model.prefix, "speakerOptimality.pdf", sep = ""),
#        width = 4, height = 4)
```


### Prevalence prior parameters

#### Forward sample prevalence priors

Add iteration number back in.

```{r}
m.samp.iter <- m.samp %>%
  #filter(type %in% c("componentParameters")) %>%
  filter(parameter %in% c("weight", "alpha", "beta")) %>%
  # mutate(parameter = paste(type, param, property, category, sep = "_")) %>%
  # select(-type, -param, -property, -category) %>%
  mutate(parameter = paste(parameter, property, component, sep = "_")) %>%
  select(-property, -component) %>%
  group_by(parameter) %>%
  mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
  ungroup() %>%
#  separate(parameter, into = c("parameter", "property", "componentID", "componentParam"), sep= "_")
  separate(parameter, into = c("parameter", "property", "componentID"), 
           sep= "_")

m.rs.prior.parameters <- m.samp.iter %>% 
  #mutate(componentParam = paste(componentParam, "_", componentID, sep = "")) %>% select(-componentID) %>%
  mutate(componentParam = paste(parameter, "_", componentID, sep = "")) %>% select(-componentID, -parameter) %>%
  spread(componentParam, val) %>%
  rowwise() %>%
  mutate(component = LaplacesDemon::rcat(1, c(`weight_0`, `weight_1`, `weight_2`)) - 1,
         shape1_param = ifelse(component == 0, alpha_0, ifelse(component == 1, alpha_1, alpha_2)),
         shape2_param = ifelse(component == 0, beta_0, ifelse(component == 1, beta_1, beta_2)),
         prev = rbeta(shape1 = shape1_param, shape2 = shape2_param, n = 1))

```

##### Marginal distributions on prevalence

```{r gen-prevprior2-marginals, fig.width = 8, fig.height = 5}
md.prevpriors <- bind_rows(
  df.prior.filtered %>% 
    filter(property %in% levels(factor(m.rs.prior.parameters$property))) %>%
    select(property, response) %>%
    rename(prev = response) %>% 
    mutate(src = 'data'),
  m.rs.prior.parameters %>% 
    select(property, prev) %>%
    mutate(src = 'model') 
  )

ggplot(md.prevpriors , aes( x = prev, color = src))+
  geom_density(size = 1, aes( y = ..scaled.. ), adjust = 0.5)+
  facet_wrap( ~ property)+
  scale_color_solarized()+
  scale_x_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
  theme(strip.text.y = element_text(angle = 0))

# ggsave(paste("figs/", model.prefix, "prevPriorsPDFs.pdf", sep = ""),
#        width = 14, height = 8)
```

##### Cumulative Density Functions

```{r gen-prevprior2-cdf, fig.width = 8, fig.height = 5}
ggplot(md.prevpriors, aes( x = prev, color = src))+
    stat_ecdf()+
    facet_wrap(~property)+
    scale_color_solarized()+
    scale_x_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
    scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
    theme(strip.text.y = element_text(angle = 0))

ggsave(paste("figs/", model.prefix, "prevPriorsCDFs.pdf", sep = ""),
       width = 14, height = 8)
```

### Implied prevalence

```{r}

md.impprev <- left_join(
   m.samp %>%
    filter(parameter %in% c("prior", "posterior")) %>%
    #filter(type == "prediction") %>%
    #rename(component = property, property = param, parameter = category) %>%
    group_by(property, parameter) %>%
    summarize(model_MAP = estimate_mode(val),
            model_upper = hdi_upper(val),
            model_lower = hdi_lower(val)),
  df.int.filtered %>%
    #filter(property %in% levels(factor(m.samp$param))) %>%
    group_by(property) %>%
    tidyboot::tidyboot_mean(column = response)
)

```

```{r}
ggplot(md.impprev, aes( x = model_MAP, xmin = model_lower, xmax = model_upper, 
                        y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_abline(intercept = 0, slope = 1, lty = 2)+
  geom_point()+
  geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)+
  facet_wrap(~parameter)+
  scale_x_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
  scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
  coord_fixed()

# ggsave(paste("figs/", model.prefix, "interpretationScatters.pdf", sep = ""),
#        width = 6, height = 4)
```

```{r}
md.impprev %>%
  filter(!is.na(mean)) %>%
  group_by(Parameter) %>%
  summarize( mse  = mean((model_MAP-mean)^2),
             r2 = cor(model_MAP, mean)^2) %>% 
  kable()
```




```{r wip}
m.samp.iter.weight <- m.samp.iter %>%
  filter((componentParam == "weight") | (parameter == "numberOfComponents")) %>%
  mutate(componentID = paste("component", componentID, sep = "")) %>%
  spread(componentID, val)

m.samp.iter.param <- m.samp.iter %>%
  filter(componentParam %in% c("alpha", "beta")) %>%
  spread(componentParam, val)

# for (p in levels(factor(m.samp.iter$property))){
#   for (i in seq(1, n_samples){
#     
#   }
# }
# 
# m.samp.iter.weight.i <- m.samp.iter.weight %>% 
  filter(iteration == 10, property == 'develop phobias')

indices <- paste("component", 
                 seq(0, 
                     filter(m.samp.iter.weight.i, 
                            parameter == 'numberOfComponents')[[1, "component-99"]]), 
                 sep ="")

ps <- as.numeric(as.vector(
  filter(m.samp.iter.weight.i, 
         componentParam == 'weight')[1,indices]
  ))

componentId <- LaplacesDemon::rcat(1, ps)

m.samp.iter.param %>%
  filter(property == p, iteration == i, componentID == componentId) %>%
  mutate(prev = rbeta(shape1 = alpha, shape2 = beta, n = 1))

```




