---
title: "Single model simulations"
output: html_notebook
---


```{r libraries}
library(tidyverse)
library(forcats)
library(rwebppl)
library(jsonlite)
library(ggthemes)
theme_set(theme_few())

```

```{r}
expectation <- function(dist){
  return(sum(dist$probs*dist$support))
}
```



```{r}
params <- expand.grid(
  speakerOptimality = seq(0.5, 30, 2),
  cost = c(0, 0.5, 1, 3, 5, 10),
  modelName = c("literal", "pragmatic_unlifted", "pragmatic"),
  prior = c("uniform", "biological_rare", "biological_common",
            "accidental_common", "accidental_rare",
            "gendered_rare")
  ) 
```

Notes...

```{r}
wp.rs <- webppl(program_file = "genint.wppl",
       packages = c("./node_modules/utils"),
       data = params)
```



```{r}
ggplot(wp.rs, aes( x = speakerOptimality, y = expectation_prediction,
                   color = factor(cost), group = factor(cost)))+
  geom_line()+
  facet_grid(priorName~modelName)+
  scale_x_continuous(breaks = c(0, 15, 30))+
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  ylab("listener expectation of prevalence")+
  theme(legend.position = 'bottom',
        strip.text.y = element_text(angle = 0))
```

*1/2/18*

- Cost and speakerOptimality contribute differently (at least, assuming cost=0 and varying speakerOptimality doesn't seem to get you enough dynamic range)
- speakerOptimality above 10 doesn't seem to matter: as speakerOptimality increases, interpretation strengthens and then weakens after about speakerOptimality of 5
- unlifted model usually can get stronger interpretation than lifted pragmatic, though as cost > 5, lifted pragmatic gets stronger interpretation
- priors have (desired) effect: interpretations are not arbitrarily strong



```{r}
ggplot(wp.rs, aes( x = expectation_prediction, fill = modelName))+
  geom_histogram(position = position_dodge(), bins = 20)+
  facet_grid(.~priorName, scales = 'free')+
  #scale_x_continuous(breaks = c(0, 15, 30))+
  #scale_y_continuous(breaks = c(0, 5, 10))+
  theme(legend.position = 'bottom',
        strip.text.y = element_text(angle = 0))
```


it appears that the pragmatic_unlifted is just a more flexible model..